### 2020-08-21 coverletter/Coverletter-Gonzalez-Bustamante.tex
Create Coverletter-Gonzalez-Bustamante.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{../bgonzalezbustamante-style}
\geometry{left=2.5cm, top=2.0cm, right=2.5cm, bottom=2.0cm, footskip=.5cm}
\fontdir[fonts/]
\colorlet{awesome}{awesome-concrete}

\setbool{acvSectionColorHighlight}{true}

\renewcommand{\acvHeaderSocialSep}{$\;$$\;$$\;$$\;$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% PERSONAL INFORMATION

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Available options: circle|rectangle,edge/noedge,left/right
%% \photo{}
\name{Bastián}{González-Bustamante}
\position{PRS DPhil in Politics{\enskip\cdotp\enskip}University of Oxford}
\address{St Hilda's College, Cowley Place, Oxford OX4 1DY, UK}

%% \mobile{}
\email{bastian.gonzalezbustamante@politics.ox.ac.uk}
\homepage{users.ox.ac.uk/~shil5311}
\landingpage{bgonzalezbustamante.com}
\github{bgonzalezbustamante}
%% \twitter{@bastiangb}
%% \skype{}
%% \extrainfo{}

%% \quote{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% LETTER INFORMATION

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\recipient
  {Recruitment Committee}
  {St Hilda's College \\ St Hilda's College, Cowley Place \\ Oxford OX4 1DY, UK}
\letterdate{\today}
\lettertitle{Application}
\letteropening{Dear Members of the Committee,}
\letterclosing{Yours faithfully,}
\letterenclosure[Attached]{{\small \faFilePdfO} $\,$ Curriculum Vitae \\ {\small \faFilePdfO} $\,$ Sample of Written Work}

\usepackage{lastpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\makecvheader[L]

\makecvfooter
  {\today}
  {Bastián González-Bustamante~~~·~~~Cover Letter}
  {\thepage\ of \pageref*{LastPage}}

\makelettertitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CONTENT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{cvletter}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

\end{cvletter}

\makeletterclosing

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-08-21 sections/languages.tex
Create languages.tex

--- 2020-08-21 coverletter/Coverletter-Gonzalez-Bustamante.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%!TEX TS-program = xelatex
-%!TEX encoding = UTF-8 Unicode
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\documentclass[11pt, a4paper]{../bgonzalezbustamante-style}
-\geometry{left=2.5cm, top=2.0cm, right=2.5cm, bottom=2.0cm, footskip=.5cm}
-\fontdir[fonts/]
-\colorlet{awesome}{awesome-concrete}
+\cvsection{Languages \& Softwares}
 
-\setbool{acvSectionColorHighlight}{true}
+\begin{cvskills}
 
-\renewcommand{\acvHeaderSocialSep}{$\;$$\;$$\;$$\;$}
+\cvskill
+{Languages} 
+{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\cvskill
+{} 
+{reading skills)} \\
 
-%% PERSONAL INFORMATION
+\cvskill
+{Programming} 
+{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\cvskill
+{} 
+{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}
 
-%% Available options: circle|rectangle,edge/noedge,left/right
-%% \photo{}
-\name{Bastián}{González-Bustamante}
-\position{PRS DPhil in Politics{\enskip\cdotp\enskip}University of Oxford}
-\address{St Hilda's College, Cowley Place, Oxford OX4 1DY, UK}
+\cvskill
+{} 
+{{\scshape xhtml}, Notepad{\footnotesize ++}} \\
 
-%% \mobile{}
-\email{bastian.gonzalezbustamante@politics.ox.ac.uk}
-\homepage{users.ox.ac.uk/~shil5311}
-\landingpage{bgonzalezbustamante.com}
-\github{bgonzalezbustamante}
-%% \twitter{@bastiangb}
-%% \skype{}
-%% \extrainfo{}
-
-%% \quote{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% LETTER INFORMATION
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\recipient
-  {Recruitment Committee}
-  {St Hilda's College \\ St Hilda's College, Cowley Place \\ Oxford OX4 1DY, UK}
-\letterdate{\today}
-\lettertitle{Application}
-\letteropening{Dear Members of the Committee,}
-\letterclosing{Yours faithfully,}
-\letterenclosure[Attached]{{\small \faFilePdfO} $\,$ Curriculum Vitae \\ {\small \faFilePdfO} $\,$ Sample of Written Work}
-
-\usepackage{lastpage}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\makecvheader[L]
-
-\makecvfooter
-  {\today}
-  {Bastián González-Bustamante~~~·~~~Cover Letter}
-  {\thepage\ of \pageref*{LastPage}}
-
-\makelettertitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% CONTENT
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{cvletter}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis.
-Vivamus at neque arcu, sed tempor quam.
-Curabitur pharetra tincidunt tincidunt.
-Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat.
-Duis tristique justo vel massa fermentum accumsan.
-Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum.
-Donec scelerisque lobortis ipsum eu vestibulum.
-Pellentesque vel massa at felis accumsan rhoncus.
-
-\end{cvletter}
-
-\makeletterclosing
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{cvskills}

### 2020-08-21 sections/expertise.tex
Create expertise.tex

--- 2020-08-21 sections/languages.tex
@@
 
-\cvsection{Languages \& Softwares}
+\cvsection{Expertise}
 
@@
 \cvskill
-{Languages} 
-{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}
+{Interests}
+{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}
 
@@
 {}
-{reading skills)} \\
+{systems, political participation, digital media, electronic government}\\
 
 \cvskill
-{Programming} 
-{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}
+{Techniques} 
+{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}
 
@@
 {} 
-{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}
-
-\cvskill
-{} 
-{{\scshape xhtml}, Notepad{\footnotesize ++}} \\
+{network analysis, qualitative comparative analysis, topic modelling} \\
 

### 2020-08-21 sections/experience.tex
Create experience.tex

--- 2020-08-21 sections/expertise.tex
@@
 
-\cvsection{Expertise}
+\cvsection{Relevant Employment}
 
-\begin{cvskills}
+\begin{cventries}
+\cventry
+{Instructor} 
+{Universidad de Santiago} 
+{Santiago, Chile} 
+{2018 - on leave}
+{Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}
 
-\cvskill
-{Interests}
-{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}
+\cventry
+{Consultant} 
+{United Nations Development Programme} 
+{Santiago, Chile} 
+{2016 - 2017}
+{Democratic Governance Programme} \vspace{1.5mm}
 
-\cvskill
-{}
-{systems, political participation, digital media, electronic government}\\
+\cventry
+{Adjunct Professor} 
+{Universidad de Santiago} 
+{Santiago, Chile} 
+{2014 - 2017}
+{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}
 
-\cvskill
-{Techniques} 
-{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}
-
-\cvskill
-{} 
-{network analysis, qualitative comparative analysis, topic modelling} \\
-
-\end{cvskills}
+\end{cventries}

### 2020-08-21 sections/book-chapters.tex
Create book-chapters.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Peer-Reviewed Book Chapters}

\begin{cventries}

\begin{benumerate}{12}
\item{\small Gonz\'alez-Bustamante, B. (2018). Civil Service Models in Latin America. In A. Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}. Cham: Springer. {\scshape doi}: \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2018). Internet, Digital Social Networks Usage, and Participation in the Southern Cone. In P. Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras Posibilidades de Comprensi\'on e Investigaci\'on}. Santiago: Social-Ediciones. {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2018). Governmental Political Elite in Chile: Ministers Survival (1990-2014). In A. Codato \& F. Espinoza (eds.), {\itshape Las \'Elites en las Am\'ericas: Diferentes Perspectivas}. Curitiba: Editora UFPR. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Barr\'ia, D. (2018). Expansion of the Public Sphere in Chile: Social Networks, Electoral Campaigns, and Digital Participation. In N. Del Valle (ed.), {\itshape Transformaciones de la Esfera P\'ublica en Chile. Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}. Santiago: RIL. {\footnotesize \scshape [in Spanish]}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}

\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Araya, J. E. (2017). Electronic Democracy and Digital Participation: Advances and Challenges. In J. R. Gil-Garc\'ia, J. I. Criado \&  J. C. T\'ellez (eds.), {\itshape Tecnolog\'ias de Informaci\'on y Comunicaci\'on en la Administraci\'on P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}. Mexico City: INFOTEC. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2016). Twitter Usage in Political Communication. In I. Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}. Madrid: CEPC. {\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D. (2016). Viral Campaign. In I. Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}. Madrid: CEPC. {\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D. (2016). Political Branding. In I. Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}. Madrid: CEPC. {\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2014). New Media and Digital Politics: The Case of Chilean Primary Presidential Elections 2013. In G. Sibaja (ed.), {\itshape Nuevos medios y comunicaci\'on pol\'itica digital}. San Jose: FESJD. {\footnotesize \scshape [in Spanish]}.} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2014). Digital Activism, Social Networks, and Brokerage. In S. Millaleo \& P. C\'arcamo (eds.), {\itshape Mediaciones del sistema pol\'itico frente al activismo digital}. Santiago: FDD. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

\item{\small Gonz\'alez--Bustamante, B. (2014). Redes sociales como herramienta para la pr\'actica pol\'itica: Twitter y el concepto de opini\'on p\'ublica. In O. Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica pol\'itica y medios digitales}. Santiago: Instituto Igualdad. {\footnotesize \scshape [in Spanish]}.} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G. (2013). Chile: The Digital Campaign 2009-2010. In I. Crespo \& J. del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}. Buenos Aires: Biblos. {\footnotesize \scshape [in Spanish].}} \vspace{1mm}
\end{benumerate}

\end{cventries}

### 2020-08-21 sections/awards.tex
Create awards.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Honours \& Awards}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{St Hilda's College at the University of Oxford Book and Travel Grants} 
{Allowances for books and conference participation (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
{Oxford, UK}
{2019}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{LASA Travel Grant} 
{Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
{New York, USA}
{2016}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{CESS Summer School Scholarship}
{Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
{Santiago, Chile}
{2016}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{ALACIP Methodological School Prize}
{Best methodological work at the Latin American Political Association School (ALACIP)}
{Lima, Peru}
{2015}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{ACCP Winter School Scholarship}
{Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
{Montevideo, Uruguay}
{ 2015}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{PUC Summer School Scholarship}
{Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
{Santiago, Chile}
{2014} 
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Comunicracia Prize}
{Best paper of the political communication area at the XI Argentinian Congress of Political Science (double-blind peer-review), {\pounds} 170}
{Parana, Argentina}
{2013}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Highest Rating MA Dissertation}
{The highest rating and the congratulations from the jury at the Universidad de Chile}
{Santiago, Chile}
{2013}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA field work (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
{Santiago, Chile}
{2012}
\end{cvhonors}

\vspace{1mm}

### 2020-08-21 sections/references.tex
Create references.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{References}

\begin{cvparagraph}

\begin{itemize}
\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:alfredo.joignant@mail.udp.cl}{\textcolor{blue}{alfredo.joignant@mail.udp.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Jaime Baeza}, Assistant Professor, Universidad de Chile, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:jbaezaf@u.uchile.cl}{\textcolor{blue}{jbaezaf@u.uchile.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Marcel Thez\'a}, Associate Professor, Universidad de Los Lagos, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:marcel.theza@ulagos.cl}{\textcolor{blue}{marcel.theza@ulagos.cl}}}} \vspace{1.5mm}
\end{itemize}

\end{cvparagraph}

### 2020-08-21 sections/teaching.tex
Create teaching.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Relevant Teaching Experience}

\begin{cventries}

\begin{itemize}
\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
\begin{itemize}
\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Faculty of Economics and Management, {\bfseries Universidad de Santiago}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Political Science I (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
\item[$\circ$]{\small Political Science II (undergraduate lecture), Spring 2015-2018}
\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), Fall 2018}
\item[$\circ$]{\small Workshop for Research Design (graduate seminar), Spring 2017-2018}
\item[$\circ$]{\small Research Methodology (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), Fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), Fall 2016}
\item[$\circ$]{\small Political Analysis (undergraduate lecture), Fall 2014}
\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
\end{itemize}
\end{itemize}

\vspace{1mm}
\end{cventries}

### 2020-08-21 sections/working-papers.tex
Create working-papers.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Working Papers}

\begin{cventries}

\begin{benumerate}{4}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. ({\itshape forthcoming}).  Applying ForceAtlas2, a Continuous Graph LayoutAlgorithm, to the Elites Study. Tufte Working Papers, (1), 1--13. {\footnotesize \scshape [in Spanish]}.} \vspace{1mm}

\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A. (2016). Revolving Door. Analysis of Public-Private Circulation in Chile (2000-2014). {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, (7), 1--40. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2016). Undersecretaries Rotation in the Chilean Cabinets (1990-2014). {\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil. NUSP/UFPR, 3}(5), 1--19. {\footnotesize \scshape [in Portuguese]}. {\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Soto, D. (2016). Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases. {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, (2), 1--26. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}
\end{benumerate}

\end{cventries}

### 2020-08-21 sections/summary.tex
Create summary.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{3mm}
\cvsection{Summary}

\begin{cvparagraph}

I am a PRS in the DPhil in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Furthermore, I am an Instructor in the Department of Public Administration and Policy at the Faculty of Economics and Management at the Universidad de Santiago, where I have been working since 2014.

Before starting the DPhil, I earned a BA (2:1) in Government and an MA (1st) in Political Science, both from the Universidad de Chile. Moreover, I worked as a lecturer at the Universidad de Santiago and the Universidad de Chile, as well as a consultant for the United Nations Development Programme.

My doctoral research is supervised by Professor Petra Schleiter at St Hilda’s College and focuses on the stability of cabinets in Latin American presidential democracies. My research is supported by the Chilean National Agency for Research and Development. Additionally, I am interested in the political elite’s socialisation, civil services, political participation, digital media, as well as electronic and open government.
\vspace{1mm}
\end{cvparagraph}

### 2020-08-21 sections/reviewer.tex
Create reviewer.tex

--- 2020-08-21 sections/references.tex
@@
 
-\cvsection{References}
+\cvsection{Peer Reviewer \& Expert}
 
@@
 \begin{itemize}
-\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:alfredo.joignant@mail.udp.cl}{\textcolor{blue}{alfredo.joignant@mail.udp.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Jaime Baeza}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:jbaezaf@u.uchile.cl}{\textcolor{blue}{jbaezaf@u.uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Marcel Thez\'a}, Associate Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:marcel.theza@ulagos.cl}{\textcolor{blue}{marcel.theza@ulagos.cl}}}} \vspace{1.5mm}
+\item{\small Varieties of Democracy Project, University of Gothenburg, Sweden, 2014, 2018-2020}
+\item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
+\item{\small Sectoral Commission for Research, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
+\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, 
+Netherlands, 2018-2019}
+\item{\small Reviewer in {\scshape WoS} \& {\scshape Scopus} journals, since 2013}
+\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, since 2013}
 \end{itemize}
 
+\vspace{1mm}
 \end{cvparagraph}

### 2020-08-21 sections/papers-isi.tex
Create papers-isi.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Peer-Reviewed Articles}

\cvsubsection{Social Sciences Citation Index}

\begin{cventries}

\begin{benumerate}{5}
\item{\small Gonz\'alez-Bustamante, B. ({\itshape forthcoming}). Evolution and Early Government Responses to COVID-19 in South America. {\itshape World Development}. {\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A. (2020). Determinants of E-Government in the Municipalities: Evidence from the Chilean Case. {\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129. {\footnotesize \scshape [in Spanish, {\bfseries 0.222} 2019-JIF, {\bfseries Q4} Public Administration]}. {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2019). The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition. {\itshape Bulletin of Latin American Research}. Early View. {\footnotesize \scshape [{\bfseries 0.586} 2019-JIF, {\bfseries Q3} Area Studies]}. {\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2019). Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, (80), 1--27. {\footnotesize \scshape [in Spanish, {\bfseries 0.704} 2019-JIF, {\bfseries Q4} Sociology]}. \\ {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010. {\itshape Pol\'itica y Gobierno, XXV}(1), 31--64. {\footnotesize \scshape [in Spanish, {\bfseries 0.714} 2019-JIF, {\bfseries Q4} Political Science]}. {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
\end{benumerate}

\end{cventries}

### 2020-08-21 sections/papers-scopus.tex
Create papers-scopus.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Peer-Reviewed Articles}

\cvsubsection{Scopus \& Emerging Sources Citation Index}

\begin{cventries}

\begin{benumerate}{7}
\item{\small Olivares, A. {\itshape et al.} (2020). New Challenges, Approaches, and Perspectives in the Study of Political Elites. {\itshape Iberoamericana, XX}(74), 229--259. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}. \\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}

\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A. (2019). Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014). {\itshape Latin American Business Review, 20}(4), 367--387. {\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}

\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Cisternas, C. (2019). The Literature on Open Government in Spanish. Analysis of the Dynamics of Production and Citation. {\itshape N\'oesis. Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}

\item{\small Del Valle, N., \& Gonz\'alez-Bustamante, B. (2018). Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism. {\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{http://revistas.ufro.cl}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2016). Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010). {\itshape Colombia Internacional}, (87), 81--108. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. {\itshape et al.} (2016). Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13). {\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59--79. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2015). Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014. {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
\end{benumerate}

\end{cventries}

### 2020-08-21 sections/papers-scielo.tex
Create papers-scielo.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Peer-Reviewed Articles}

\cvsubsection{ SciELO \& Latindex}

\begin{cventries}

\begin{benumerate}{9}
\item{\small Gonz\'alez-Bustamante, B. (2016). Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2016). Political Elites in the Chilean Legislative Branch: The Chamber of Deputies (1990-2014). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 19--52. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2015). Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013. {\itshape Revista SAAP, 9}(1), 119--141. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2015). Electoral Success and Campaign Spending in Elections of Senators and Deputies in Chile 2013. {\itshape Pol\'iticas P\'ublicas, 8}(1), 21--35. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2014). Popular Election of Regional Councillors 2013. Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}

\item{\small Olivares, A. {\itshape et al.} (2014). Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014). {\itshape Revista de Sociolog\'ia,} (29), 37--54. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2013). Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2013). The Study of the Elites in Chile: Theoretical and Methodological Approaches. {\itshape Intersticios Sociales,} (6), 1--20. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G. (2012). Digital Campaigns: Branding or Political Participation? {\itshape M\'as Poder Local,} (12), 32--39. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
\end{benumerate}

\end{cventries}

### 2020-08-21 sections/projects.tex
Create projects.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% DEPRECATED

\cvsection{Funding \& Research Projects}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Chilean Political Science Impact Ranking} 
{This research have not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
{Coordinator}
{2020}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{COVID-19 Pandemic in South America}
{This research have not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
{Coordinator}
{2020}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Gender Turnout and Elected Representatives in Iceland Municipal Elections}
{Prof. Petra Schleiter, Department of Politics and International Relations and St Hilda's College, University of Oxford}
{Research Assistant}
{2020}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Survival of the Senior Civil Servants in the Chilean Executive Branch}
{Funded by the Universidad de Santiago de Chile (Academic Performance Agreement). {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/WBF6M}{10.17605/OSF.IO/WBF6M}}
{Researcher}
{2018}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Political System and Visibility of Actors in the Public Debate Articulated by the Elite Press, 1990-2018}
{Funded by the Universidad Alberto Hurtado (XVI Promotion of Research Fund, Ximena Orchard, Principal Investigator)}
{Researcher}
{2019}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Transparency and Publication Dynamics on the Latin American Public Administration}
{Funded by the Universidad de Santiago (USA1498.57, Diego Barría, Principal Investigator)}
{Researcher}
{2017}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Public Service Motivation, Open Government and Preferences on Public Services}
{Funded by the Universidad de Santiago (USA1498.37, Diego Barría, Principal Investigator)}
{Researcher}
{2016}
\end{cvhonors}

\vspace{1mm}

%% PENDING PROJECTS

### 2020-08-21 sections/book-chapters.tex
Update book-chapters.tex

@@
 
-\begin{cventries}
+\begin{publications}
 
@@
 Espinoza (eds.), {\itshape Las \'Elites en las Am\'ericas: Diferentes Perspectivas}.
-Curitiba: Editora UFPR.
+Curitiba: Editora da Universidade Federal do Paraná.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \\ %% \vspace{1mm}
 
@@
 Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}.
-Santiago: RIL.
+Santiago: RIL Editores.
 {\footnotesize \scshape [in Spanish]}.
@@
 Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
-Madrid: CEPC.
+Madrid: Centro de Estudios Políticos y Constitucionales.
 {\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}
@@
 Sibaja (ed.), {\itshape Nuevos medios y comunicaci\'on pol\'itica digital}.
-San Jose: FESJD.
+San Jose: Fundación Educativa San Judas Tadeo.
 {\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
@@
 C\'arcamo (eds.), {\itshape Mediaciones del sistema pol\'itico frente al activismo digital}.
-Santiago: FDD.
+Santiago: Fundación Democracia y Desarrollo.
 {\footnotesize \scshape [in Spanish]}.
@@
 del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}.
-Buenos Aires: Biblos.
+Buenos Aires: Editorial Biblos.
 {\footnotesize \scshape [in Spanish].}} \vspace{1mm}
@@
 
-\end{cventries}
+\end{publications}

### 2020-08-21 sections/languages.tex
Update languages.tex

@@
 {Languages} 
-{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}
+{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills),}
 
@@
 {} 
-{reading skills)} \\
+{French (elemental reading skills)} \\
 
@@
 {} 
-{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}
+{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}
 
@@
 {} 
-{{\scshape xhtml}, Notepad{\footnotesize ++}} \\
+{{\scshape css}, {\scshape xhtml}, Notepad{\footnotesize ++}} \\
 

### 2020-08-21 sections/references.tex
Update references.tex

@@
 
-\begin{cvparagraph}
+\begin{publications}
 
@@
 \item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \vspace{1.5mm}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \pagebreak %% \vspace{1.5mm}
 \item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
@@
 
-\end{cvparagraph}
+\end{publications}

### 2020-08-21 spanish/sections/editor.tex
Create editor.tex

--- 2020-08-21 sections/papers-scopus.tex
@@
 
-%% CV-XeLaTeX in English
+%% CV-XeLaTeX in Spanish
 %% Bastián González-Bustamante
@@
 
-\cvsection{Peer-Reviewed Articles}
+\cvsection{Números especiales editados}
 
-\cvsubsection{Scopus \& Emerging Sources Citation Index}
+\begin{publications}
 
-\begin{cventries}
-
-\begin{benumerate}{7}
-\item{\small Olivares, A.
-{\itshape et al.} (2020).
-New Challenges, Approaches, and Perspectives in the Study of Political Elites.
-{\itshape Iberoamericana, XX}(74), 229--259.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}.
-\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
-
-\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A.
-(2019).
-Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014).
-{\itshape Latin American Business Review, 20}(4), 367--387.
-{\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}
-
-\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Cisternas, C.
-(2019).
-The Literature on Open Government in Spanish.
-Analysis of the Dynamics of Production and Citation.
-{\itshape N\'oesis.
-Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}
-
-\item{\small Del Valle, N., \& Gonz\'alez-Bustamante, B.
-(2018).
-Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism.
-{\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{http://revistas.ufro.cl}}}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
-(2016).
-Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010).
-{\itshape Colombia Internacional}, (87), 81--108.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
+\begin{benumerate}{2}
+\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. {\itshape Pleyade}.}\vspace{1mm}
 
 \item{\small Gonz\'alez-Bustamante, B.
-{\itshape et al.} (2016).
-Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13).
-{\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59--79.
+(2016).
+Political, Economic, and Intellectual Elites.
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1).
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
-(2015).
-Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014.
-{\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 \end{benumerate}
 
-\end{cventries}
+\end{publications}

### 2020-08-21 spanish/sections/summary.tex
Create summary.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in Spanish
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{3mm}
\cvsection{Reseña}

\begin{cvparagraph}

Soy doctorante en el programa de Ciencia Política en el Departamento de Política y Relaciones Internacionales en St Hilda's College en la Universidad de Oxford, Reino Unido. Además, soy Profesor Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago, donde he trabajado desde el 2014.

Antes de comenzar mis estudios doctorales, obtuve una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública con distinción y un Magíster en Ciencia Política con máxima distinción, ambos grados en la Universidad de Chile. Además, trabajé como profesor en la Universidad de Santiago y de Chile, como también consultor para el Programa de las Naciones Unidas para el Desarrollo.

Mi investigación doctoral es supervisada por la Profesora Petra Schleiter en St Hilda's College y se enfoca en la estabilidad de los gabinetes en las democracias presidenciales latinoamericanas. Mi investigación es apoyada por la Agencia Nacional de Investigación y Desarrollo. Adicionalmente, estoy interesado en temas como los procesos de socialización de la élite política, servicios civiles, participación política, medios digitales, como también gobierno electrónico y abierto.
\vspace{1mm}
\end{cvparagraph}

### 2020-08-21 spanish/sections/references.tex
Create references.tex

--- 2020-08-21 sections/references.tex
@@
 
-\cvsection{References}
+\cvsection{Referencias}
 
@@
 \begin{itemize}
-\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
+\item[]{\small {\bfseries Petra Schleiter}, Profesora en Política Comparada, Universidad de Oxford, RU}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
+\item[]{\small {\bfseries Gonzalo Delamaza}, Profesor Titular, Universidad de Los Lagos, Chile}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
+\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Profesor Asistente, Universidad de Chile, Chile}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \pagebreak %% \vspace{1.5mm}
-\item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
+\item[]{\small {\bfseries Alfredo Joignant}, Profesor Titular, Universidad Diego Portales, Chile}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:alfredo.joignant@mail.udp.cl}{\textcolor{blue}{alfredo.joignant@mail.udp.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Jaime Baeza}, Assistant Professor, Universidad de Chile, Chile}
+\item[]{\small {\bfseries Jaime Baeza}, Profesor Asistente, Universidad de Chile, Chile}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:jbaezaf@u.uchile.cl}{\textcolor{blue}{jbaezaf@u.uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Marcel Thez\'a}, Associate Professor, Universidad de Los Lagos, Chile}
+\item[]{\small {\bfseries Marcel Thez\'a}, Profesor Asociado, Universidad de Los Lagos, Chile}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:marcel.theza@ulagos.cl}{\textcolor{blue}{marcel.theza@ulagos.cl}}}} \vspace{1.5mm}

### 2020-08-21 spanish/sections/training.tex
Create training.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Certification \& Training}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{DPhil Traning Programme Trinity Term at the University of Oxford} 
{Training in geospatial modelling} 
{Oxford, UK}
{2020}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{DPhil Traning Programme Hilary Term at the University of Oxford} 
{Training in formal analysis and game theory, randomised trials, regression and matching, instrumental variables, regression discontinuity, differences-in-differences, and placebo tests} 
{Oxford, UK}
{2020}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Research Data Workshop IT Centre at the University of Oxford} 
{Training in managing research data} 
{Oxford, UK}
{2019}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{DPhil Traning Programme Michaelmas Term at the University of Oxford}
{Training in research design, logit and OLS models, multinomial models, ordinal logistic regressions,  OLS regularisation and cross-validation procedures, shrinkage methods, regression tree, random forest algorithm, principal component analysis based on unsupervised learning, and count models}
{Oxford, UK}
{2019}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Longitudinal Networks with RSiena Workshop at the Pontifica Universidad Cat\'olica}
{Training in stochastic actor oriented models in R}
{Santiago, Chile}
{2018}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Universidad de Santiago Winter School for Academics}
{Training in evaluation techniques and teaching strategies for academic writing}
{Santiago, Chile}
{2016}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Nuffield-USACH CEES Experimental Summer School}
{Training in experiments in social sciences}
{Santiago, Chile}
{2016}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Universidad de Santiago Winter School for Academics}
{Training in qualitative data analysis in {\scshape atlas}.ti}
{Santiago, Chile}
{2015}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Latin American Political Science Association Methodological School}
{Training in programming in Python, social network analysis in R and Python, and qualitative comparative analysis in R}
{Lima, Peru}
{2015}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
{Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
{Montevideo, Uruguay}
{2015}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
{Training in set theory and logic, case studies and multi-methods, process tracing, and experiments in social sciences}
{Santiago, Chile}
{2014}
\end{cvhonors}

\vspace{1mm}

### 2020-08-21 spanish/sections/awards.tex
Create awards.tex

--- 2020-08-21 sections/awards.tex
@@
 
-\cvsection{Honours \& Awards}
+\cvsection{Honores y premios}
 
@@
 \cvhonor
-{St Hilda's College at the University of Oxford Book and Travel Grants} 
-{Allowances for books and conference participation (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
-{Oxford, UK}
+{Becas de Libros y Viaje St Hilda's College en la Universidad de Oxford} 
+{Asignaciones para libros y participación en conferencias (la subvención para viajes se rechazó debido a la pandemia de coronavirus), USD{\$} 970} 
+{Oxford, RU}
 {2020}
@@
 \cvhonor
-{Becas Chile Doctoral Scholarship Abroad} 
-{Tuition fees, transport and living expenses for pursuing a DPhil at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
-{Oxford, UK}
+{Becas Chile, Beca Doctorado en el Extranjero } 
+{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), USD{\$} 210.000}
+{Oxford, RU}
 {2019}
@@
 \cvhonor
-{LASA Travel Grant} 
+{Beca de Viaje LASA} 
 {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
-{New York, USA}
+{Nueva York, EUA}
 {2016}
@@
 \cvhonor
-{CESS Summer School Scholarship}
+{Beca CESS Escuela de Verano}
 {Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}

### 2020-08-21 spanish/sections/experience.tex
Create experience.tex

--- 2020-08-21 sections/papers-scielo.tex
@@
 
-\cvsection{Peer-Reviewed Articles}
-
-\cvsubsection{ SciELO \& Latindex}
+\cvsection{Experiencia profesional relevante}
 
 \begin{cventries}
+\cventry
+{Profesor Instructor} 
+{Universidad de Santiago} 
+{Santiago, Chile} 
+{2018 - en comisión}
+{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
 
-\begin{benumerate}{9}
-\item{\small Gonz\'alez-Bustamante, B.
-(2016).
-Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+\cventry
+{Consultor} 
+{Programa de las Naciones Unidas para el Desarrollo} 
+{Santiago, Chile} 
+{2016 - 2017}
+{Programa de Gobernabilidad Democrática} \vspace{1.5mm}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
-(2016).
-Political Elites in the Chilean Legislative Branch: The Chamber of Deputies (1990-2014).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 19--52.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2015).
-Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013.
-{\itshape Revista SAAP, 9}(1), 119--141.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2015).
-Electoral Success and Campaign Spending in Elections of Senators and Deputies in Chile 2013.
-{\itshape Pol\'iticas P\'ublicas, 8}(1), 21--35.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2014).
-Popular Election of Regional Councillors 2013.
-Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
-
-\item{\small Olivares, A.
-{\itshape et al.} (2014).
-Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014).
-{\itshape Revista de Sociolog\'ia,} (29), 37--54.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2013).
-Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2013).
-The Study of the Elites in Chile: Theoretical and Methodological Approaches.
-{\itshape Intersticios Sociales,} (6), 1--20.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G.
-(2012).
-Digital Campaigns: Branding or Political Participation?
-{\itshape M\'as Poder Local,} (12), 32--39.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
-\end{benumerate}
+\cventry
+{Profesor Adjunto} 
+{Universidad de Santiago} 
+{Santiago, Chile} 
+{2014 - 2017}
+{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
 

### 2020-08-21 spanish/sections/expertise.tex
Create expertise.tex
Update expertise.tex

--- 2020-08-21 sections/expertise.tex
@@
 
-\cvsection{Expertise}
+\cvsection{Especialidades}
 
@@
 {Interests}
-{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}
+{Composición y nombramiento de gabinetes, rotación ministerial, socialización de élites políticas,}
 
@@
 {}
-{systems, political participation, digital media, electronic government}\\
+{sistemas de servicio civil, participación política, medios digitales, gobierno electrónico}\\
 

### 2020-08-21 spanish/sections/isi-papers.tex
Create isi-papers.tex
Update isi-papers.tex

--- 2020-08-21 sections/papers-isi.tex
@@
 
-\cvsection{Peer-Reviewed Articles}
+\cvsection{Publicaciones revisadas por pares}
 
-\cvsubsection{Social Sciences Citation Index}
+\cvsubsection{Social Sciences Citation Index (SCCI/WoS-ISI)}
 
-\begin{cventries}
+\begin{publications}
 
 \begin{benumerate}{5}
-\item{\small Gonz\'alez-Bustamante, B.
-({\itshape forthcoming}).
-Evolution and Early Government Responses to COVID-19 in South America.
-{\itshape World Development}.
-{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.}\vspace{1mm}
+\item{\small Gonz\'alez-Bustamante, B. ({\itshape forthcoming}). Evolution and Early Government Responses to COVID-19 in South America. {\itshape World Development}.}\vspace{1mm}
 
@@
 (2020).
-Determinants of E-Government in the Municipalities: Evidence from the Chilean Case.
+Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno.
 {\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.222} 2019-JIF, {\bfseries Q4} Public Administration]}.
-{\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+\\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
 {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
@@
 Early View.
-{\footnotesize \scshape [{\bfseries 0.586} 2019-JIF, {\bfseries Q3} Area Studies]}.
-{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+\\ {\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
 
@@
 (2019).
-Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay.
+Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
 {\itshape Convergencia.
 Revista de Ciencias Sociales}, (80), 1--27.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.704} 2019-JIF, {\bfseries Q4} Sociology]}.
-\\ {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
 
@@
 (2018).
-Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
+Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010.
 {\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.714} 2019-JIF, {\bfseries Q4} Political Science]}.
 {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}

### 2020-08-21 spanish/sections/scopus-papers.tex
Create scopus-papers.tex
Update scopus-papers.tex

--- 2020-08-21 sections/papers-scopus.tex
@@
 
-\cvsection{Peer-Reviewed Articles}
+\cvsection{Publicaciones revisadas por pares}
 
-\cvsubsection{Scopus \& Emerging Sources Citation Index}
+\cvsubsection{Scopus y Emerging Sources Citation Index (ESCI)}
 
-\begin{cventries}
+\begin{publications}
 
@@
 {\itshape et al.} (2020).
-New Challenges, Approaches, and Perspectives in the Study of Political Elites.
+Nuevos desafíos, enfoques y perspectivas para estudiar élites políticas.
 {\itshape Iberoamericana, XX}(74), 229--259.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}.
-\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
+{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
 

### 2020-08-22 spanish/sections/scopus-papers.tex
Update scopus-papers.tex

@@
 
-\cvsubsection{Scopus y Emerging Sources Citation Index (ESCI)}
+\cvsubsection{Scopus y Emerging Sources Citation Index (ISI-WoS/ESCI)}
 
@@
 {\itshape Latin American Business Review, 20}(4), 367--387.
-{\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}
+\\ {\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}
 
@@
 (2019).
-The Literature on Open Government in Spanish.
-Analysis of the Dynamics of Production and Citation.
+La literatura sobre gobierno abierto en español.
+Análisis sobre las dinámicas de producción y citación.
 {\itshape N\'oesis.
-Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
-{\footnotesize \scshape [in Spanish]}.
+Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42..
 {\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}
@@
 (2018).
-Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism.
+Agenda política, periodismo y medios digitales en Chile.
+Notas de investigación sobre pluralismo informativo.
 {\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{http://revistas.ufro.cl}}}\vspace{1mm}
@@
 (2016).
-Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010).
+Cambios de gabinete y supervivencia de los ministros en Chile durante los gobiernos de la Concertación (1990-2010).
 {\itshape Colombia Internacional}, (87), 81--108.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
@@
 {\itshape et al.} (2016).
-Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13).
+Servicio civil en Chile, análisis de los directivos de primer nivel jerárquico (2003-13).
 {\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59--79.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}} \vspace{1mm}
@@
 (2015).
-Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014.
+Rotación de subsecretarios en Chile: Una exploración de la segunda línea gubernamental, 1990-2014.
 {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
-{\footnotesize \scshape [in Spanish]}.
 \\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

### 2020-08-23 spanish/sections/scielo-papers.tex
Create scielo-papers.tex
Update scielo-papers.tex

--- 2020-08-21 sections/papers-scielo.tex
@@
 
-\cvsection{Peer-Reviewed Articles}
+\cvsection{Publicaciones revisadas por pares}
 
@@
 (2016).
-Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science.
+Élites políticas, económicas e intelectuales: Una agenda de investigación creciente para la ciencia política.
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
-{\footnotesize \scshape [in Spanish]}.
 \\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
@@
 (2016).
-Political Elites in the Chilean Legislative Branch: The Chamber of Deputies (1990-2014).
+Élites políticas en el poder legislativo chileno: La Cámara de Diputados (1990-2014).
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 19--52.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
 
@@
 (2015).
-Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013.
+Evaluando Twitter como indicador de opinión pública: Una mirada al arribo de Bachelet a la presidencial chilena 2013.
 {\itshape Revista SAAP, 9}(1), 119--141.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+{\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
 
@@
 (2015).
-Electoral Success and Campaign Spending in Elections of Senators and Deputies in Chile 2013.
+Éxito electoral y gasto en campaña en las elecciones de senadores y diputados en Chile 2013.
 {\itshape Pol\'iticas P\'ublicas, 8}(1), 21--35.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}} \vspace{1mm}
@@
 (2014).
-Popular Election of Regional Councillors 2013.
-Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile.
+Elección directa de consejeros regionales 2013.
+Rendimiento del capital político, familiar y económico en una nueva arena electoral en Chile.
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
@@
 {\itshape et al.} (2014).
-Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014).
+Los think tanks en el gabinete: Una exploración del caso chileno (2006-2014).
 {\itshape Revista de Sociolog\'ia,} (29), 37--54.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
@@
 (2013).
-Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
+Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 (2013).
-The Study of the Elites in Chile: Theoretical and Methodological Approaches.
+El estudio de las élites en Chile: Aproximaciones conceptuales y metodológicas.
 {\itshape Intersticios Sociales,} (6), 1--20.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
@@
 (2012).
-Digital Campaigns: Branding or Political Participation?
+Campañas digitales: ¿Branding o participación política?
 {\itshape M\'as Poder Local,} (12), 32--39.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

### 2020-08-23 spanish/sections/summary.tex
Update summary.tex

@@
 Antes de comenzar mis estudios doctorales, obtuve una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública con distinción y un Magíster en Ciencia Política con máxima distinción, ambos grados en la Universidad de Chile.
-Además, trabajé como profesor en la Universidad de Santiago y de Chile, como también consultor para el Programa de las Naciones Unidas para el Desarrollo.
+Además, trabajé como profesor en la Universidad de Santiago y de Chile y como consultor para el Programa de las Naciones Unidas para el Desarrollo.
 
 Mi investigación doctoral es supervisada por la Profesora Petra Schleiter en St Hilda's College y se enfoca en la estabilidad de los gabinetes en las democracias presidenciales latinoamericanas.
-Mi investigación es apoyada por la Agencia Nacional de Investigación y Desarrollo.
-Adicionalmente, estoy interesado en temas como los procesos de socialización de la élite política, servicios civiles, participación política, medios digitales, como también gobierno electrónico y abierto.
+Mi investigación es apoyada por la Agencia Nacional de Investigación y Desarrollo de Chile.
+Adicionalmente, estoy interesado la socialización de la élite política, servicios civiles, participación política, medios digitales y gobierno electrónico y abierto.
 \vspace{1mm}

### 2020-08-23 sections/papers.tex
Create papers.tex

--- 2020-08-21 sections/papers-scielo.tex
@@
 
+\cvsubsection{Social Sciences Citation Index (WoS-ISI/SCCI)}
+
+\begin{publications}
+
+\begin{benumerate}{5}
+\item{\small Gonz\'alez-Bustamante, B.
+({\itshape forthcoming}).
+Evolution and Early Government Responses to COVID-19 in South America.
+{\itshape World Development}.
+{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
+(2020).
+Determinants of E-Government in the Municipalities: Evidence from the Chilean Case.
+{\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129.
+{\footnotesize \scshape [in Spanish, {\bfseries 0.222} 2019-JIF, {\bfseries Q4} Public Administration]}.
+{\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2019).
+The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
+{\itshape Bulletin of Latin American Research}.
+Early View.
+{\footnotesize \scshape [{\bfseries 0.586} 2019-JIF, {\bfseries Q3} Area Studies]}.
+{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2019).
+Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, (80), 1--27.
+{\footnotesize \scshape [in Spanish, {\bfseries 0.704} 2019-JIF, {\bfseries Q4} Sociology]}.
+\\ {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
+{\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
+{\footnotesize \scshape [in Spanish, {\bfseries 0.714} 2019-JIF, {\bfseries Q4} Political Science]}.
+{\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
+\end{benumerate}
+
+\end{publications}
+
+\cvsubsection{Scopus \& Emerging Sources Citation Index (WoS-ISI/ESCI)}
+
+\begin{publications}
+
+\begin{benumerate}{7}
+\item{\small Olivares, A.
+{\itshape et al.} (2020).
+New Challenges, Approaches, and Perspectives in the Study of Political Elites.
+{\itshape Iberoamericana, XX}(74), 229--259.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}.
+\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
+
+\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2019).
+Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014).
+{\itshape Latin American Business Review, 20}(4), 367--387.
+{\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}
+
+\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Cisternas, C.
+(2019).
+The Literature on Open Government in Spanish.
+Analysis of the Dynamics of Production and Citation.
+{\itshape N\'oesis.
+Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}
+
+\item{\small Del Valle, N., \& Gonz\'alez-Bustamante, B.
+(2018).
+Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism.
+{\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{http://revistas.ufro.cl}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2016).
+Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010).
+{\itshape Colombia Internacional}, (87), 81--108.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+{\itshape et al.} (2016).
+Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13).
+{\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59--79.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}} \vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2015).
+Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014.
+{\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
+{\footnotesize \scshape [in Spanish]}.
+\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \pagebreak %% \vspace{1mm}
+\end{benumerate}
+
+\end{publications}
+
 \cvsubsection{ SciELO \& Latindex}
 
-\begin{cventries}
+\begin{publications}
 

### 2020-08-23 spanish/sections/papers.tex
Create papers.tex

--- 2020-08-23 sections/papers.tex
@@
 \begin{benumerate}{5}
-\item{\small Gonz\'alez-Bustamante, B.
-({\itshape forthcoming}).
-Evolution and Early Government Responses to COVID-19 in South America.
-{\itshape World Development}.
-{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.}\vspace{1mm}
+\item{\small Gonz\'alez-Bustamante, B. ({\itshape próximamente}). Evolution and Early Government Responses to COVID-19 in South America. {\itshape World Development}.}\vspace{1mm}
 
@@
 
-\cvsubsection{Scopus \& Emerging Sources Citation Index (WoS-ISI/ESCI)}
+\cvsubsection{Scopus y Emerging Sources Citation Index (WoS-ISI/ESCI)}
 
@@
 (2015).
-Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014.
+Rotación de subsecretarios en Chile: Una exploración de la segunda línea gubernamental, 1990-2014.
 {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \pagebreak %% \vspace{1mm}
+\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
 \end{benumerate}
@@
 
-\cvsubsection{ SciELO \& Latindex}
+\cvsubsection{ SciELO y Latindex}
 

### 2020-08-23 sections/book-chapters.tex
Update book-chapters.tex

--- 2020-08-21 sections/book-chapters.tex
@@
 Espinoza (eds.), {\itshape Las \'Elites en las Am\'ericas: Diferentes Perspectivas}.
-Curitiba: Editora UFPR.
+Curitiba: Editora da Universidade Federal do Paraná.
 {\footnotesize \scshape [in Spanish]}.
@@
 Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}.
-Santiago: RIL.
+Santiago: RIL Editores.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
+{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}} \pagebreak %% \vspace{1mm}
 

### 2020-08-23 spanish/sections/book-chapters.tex
Create book-chapters.tex
Update book-chapters.tex

--- 2020-08-21 sections/book-chapters.tex
@@
 
-\cvsection{Peer-Reviewed Book Chapters}
+\cvsection{Capítulos en libros editados}
 
@@
 Civil Service Models in Latin America.
-In A.
+En A.
 Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}.
@@
 (2018).
-Internet, Digital Social Networks Usage, and Participation in the Southern Cone.
-In P.
-Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras Posibilidades de Comprensi\'on e Investigaci\'on}.
-Santiago: Social-Ediciones.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+Internet, uso de redes sociales digitales y participación en el Cono Sur.
+En P.
+Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras posibilidades de Comprensi\'on e Investigaci\'on}.
+Santiago: Social-Ediciones.}\vspace{1mm}
 
@@
 (2018).
-Governmental Political Elite in Chile: Ministers Survival (1990-2014).
-In A.
+La élite política gubernamental en Chile: Supervivencia de ministros.
+En A.
 Codato \& F.
@@
 Curitiba: Editora da Universidade Federal do Paraná.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \\ %% \vspace{1mm}
@@
 (2018).
-Expansion of the Public Sphere in Chile: Social Networks, Electoral Campaigns, and Digital Participation.
-In N.
-Del Valle (ed.), {\itshape Transformaciones de la Esfera P\'ublica en Chile.
+Expansión de la esfera pública en Chile: Redes sociales, campañas electorales y participación digital.
+En N.
+Del Valle (ed.), {\itshape Transformaciones de la Esfera p\'ublica en Chile.
 Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}.
 Santiago: RIL Editores.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
@@
 (2017).
-Electronic Democracy and Digital Participation: Advances and Challenges.
-In J.
+Democracia electrónica y participación digital.
+Avances y desafíos.
+En J.
 R.
@@
 Mexico City: INFOTEC.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
@@
 (2016).
-Twitter Usage in Political Communication.
-In I.
+Twitter (su uso en la comunicación política).
+En I.
 Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
 Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}
+{\footnotesize \scshape [2da edición]}.} \vspace{1mm}
 
@@
 (2016).
-Viral Campaign.
-In I.
+Campaña viral.
+En I.
 Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
 Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}
+{\footnotesize \scshape [2da edición]}.} \vspace{1mm}
 
@@
 (2016).
-Political Branding.
-In I.
+Imagen de marca para un candidato o gobierno (branding político).
+En I.
 Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
 Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}
+{\footnotesize \scshape [2da edición]}.} \vspace{1mm}
 

### 2020-08-23 sections/book-chapters.tex
Update book-chapters.tex

@@
 Digital Activism, Social Networks, and Brokerage.
-In S.
+En S.
 Millaleo \& P.
-C\'arcamo (eds.), {\itshape Mediaciones del sistema pol\'itico frente al activismo digital}.
+C\'arcamo (eds.), {\itshape Mediaciones del Sistema Pol\'itico frente al Activismo Digital}.
 Santiago: Fundación Democracia y Desarrollo.
@@
 
-\item{\small Gonz\'alez--Bustamante, B.
+\item{\small Gonz\'alez-Bustamante, B.
 (2014).
-Redes sociales como herramienta para la pr\'actica pol\'itica: Twitter y el concepto de opini\'on p\'ublica.
+Social Networks as a Tool for Political Engage: Twitter and the Public Opinion Concept.
 In O.
-Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica pol\'itica y medios digitales}.
+Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica Pol\'itica y Medios Digitales}.
 Santiago: Instituto Igualdad.

### 2020-08-23 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 Curitiba: Editora da Universidade Federal do Paraná.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \\ %% \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
 

### 2020-08-23 spanish/sections/awards.tex
Update awards.tex

@@
 
-\cvsection{Honores y premios}
+\cvsection{Honores \& premios}
 
@@
 \cvhonor
-{Becas Chile, Beca Doctorado en el Extranjero } 
+{Beca Doctorado en el Extranjero Becas Chile} 
 {Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), USD{\$} 210.000}
@@
 {Beca de Viaje LASA} 
-{Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
+{Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), USD{\$} 520}
 {Nueva York, EUA}
@@
 \cvhonor
-{Beca CESS Escuela de Verano}
-{Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
+{Beca Escuela de Verano CESS}
+{Apoyo financiero para participar en la Escuela de Verano Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), USD{\$} 260}
 {Santiago, Chile}
@@
 \cvhonor
-{ALACIP Methodological School Prize}
-{Best methodological work at the Latin American Political Association School (ALACIP)}
-{Lima, Peru}
+{Premio Escuela Metodológica ALACIP}
+{Mejor trabajo metodológico en la Escuela de la Asociación Latinoamericana de Ciencia Política (ALACIP)}
+{Lima, Perú}
 {2015}
@@
 \cvhonor
-{ACCP Winter School Scholarship}
-{Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
+{Beca Escuela de Invierno ACCP}
+{Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgado por la Asociación Chilena de Ciencia Política (ACCP), USD{\$} 400}
 {Montevideo, Uruguay}
@@
 \cvhonor
-{PUC Summer School Scholarship}
-{Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
+{Beca Escuela de Verano PUC}
+{Apoyo financiero para participar en la Escuela de Verano en Métodos Mixtos en la Pontifica Universidad Cat\'olica de Chile (PUC), USD{\$} 230}
 {Santiago, Chile}
@@
 \cvhonor
-{Comunicracia Prize}
-{Best paper of the political communication area at the XI Argentinian Congress of Political Science (double-blind peer-review), {\pounds} 170}
-{Parana, Argentina}
+{Premio Comunicracia}
+{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares), USD{\$} 230}
+{Paraná, Argentina}
 {2013}
@@
 \cvhonor
-{Highest Rating MA Dissertation}
-{The highest rating and the congratulations from the jury at the Universidad de Chile}
+{Mejor calificación en la tesis de Magíster}
+{La más alta calificación y las felicitaciones del jurado en la Universidad de Chile}
 {Santiago, Chile}
@@
 \cvhonor
-{FONDECYT Thesis Writing Grant}
-{Financial support for MA field work (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
+{Beca para investigación de Mag\'ister FONDECYT}
+{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), USD{\$} 1,500}
 {Santiago, Chile}

### 2020-08-23 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 Santiago: RIL Editores.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
+\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
 
@@
 T\'ellez (eds.), {\itshape Tecnolog\'ias de Informaci\'on y Comunicaci\'on en la Administraci\'on P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}.
-Mexico City: INFOTEC.
+Ciudad de México: INFOTEC.
 {\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
@@
 (2014).
-New Media and Digital Politics: The Case of Chilean Primary Presidential Elections 2013.
-In G.
-Sibaja (ed.), {\itshape Nuevos medios y comunicaci\'on pol\'itica digital}.
-San Jose: Fundación Educativa San Judas Tadeo.
-{\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
+Nuevos medios y política digital: El caso de las primarias presidenciales chilenas de 2013.
+En G.
+Sibaja (ed.), {\itshape Nuevos Medios y Comunicaci\'on Pol\'itica Digital}.
+San José: Fundación Educativa San Judas Tadeo.} \vspace{1mm}
 
@@
 (2014).
-Digital Activism, Social Networks, and Brokerage.
-In S.
+Activismo digital, redes sociales e intermediación.
+En S.
 Millaleo \& P.
-C\'arcamo (eds.), {\itshape Mediaciones del sistema pol\'itico frente al activismo digital}.
+C\'arcamo (eds.), {\itshape Mediaciones del Sistema Pol\'itico frente al Activismo Digital}.
 Santiago: Fundación Democracia y Desarrollo.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
@@
 (2014).
-Social Networks as a Tool for Political Engage: Twitter and the Public Opinion Concept.
-In O.
+Redes sociales como herramienta para la pr\'actica pol\'itica: Twitter y el concepto de opini\'on p\'ublica.
+En O.
 Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica Pol\'itica y Medios Digitales}.
-Santiago: Instituto Igualdad.
-{\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
+Santiago: Instituto Igualdad.} \vspace{1mm}
 
@@
 (2013).
-Chile: The Digital Campaign 2009-2010.
-In I.
+Chile: La campaña digital 2009-2010.
+En I.
 Crespo \& J.
 del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}.
-Buenos Aires: Editorial Biblos.
-{\footnotesize \scshape [in Spanish].}} \vspace{1mm}
+Buenos Aires: Editorial Biblos.} \vspace{1mm}
 \end{benumerate}

### 2020-08-23 spanish/sections/papers.tex
Update papers.tex

@@
 
-\cvsubsection{Scopus y Emerging Sources Citation Index (WoS-ISI/ESCI)}
+\cvsubsection{Scopus \& Emerging Sources Citation Index (WoS-ISI/ESCI)}
 
@@
 {\itshape Colombia Internacional}, (87), 81--108.
-{\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
+\\ {\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
 
@@
 
-\cvsubsection{ SciELO y Latindex}
+\cvsubsection{ SciELO \& Latindex}
 

### 2020-08-23 spanish/sections/reviewer.tex
Create reviewer.tex
Update reviewer.tex

--- 2020-08-21 sections/reviewer.tex
@@
 
-\cvsection{Peer Reviewer \& Expert}
+\cvsection{Revisiones de pares y como experto}
 
-\begin{cvparagraph}
+\begin{publications}
 
 \begin{itemize}
-\item{\small Varieties of Democracy Project, University of Gothenburg, Sweden, 2014, 2018-2020}
-\item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
-\item{\small Sectoral Commission for Research, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
-\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, 
-Netherlands, 2018-2019}
-\item{\small Reviewer in {\scshape WoS} \& {\scshape Scopus} journals, since 2013}
-\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, since 2013}
+\item{\small Proyecto V-Dem, Universidad de Gotemburgo, Suecia, 2014, 2018-2020}
+\item{\small Encuesta de Reputación Académica Global, Clarivate Analytics, EUA, 2020}
+\item{\small Comisión Sectorial de Investigación, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
+\item{\small Times Higher Education Ranking, {\scshape Elsevier}, 
+Países Bajos, 2018-2019}
+\item{\small Revisor en {\scshape WoS} \& {\scshape Scopus} revistas, desde 2013}
+\item{\small Revisor en {\scshape SciELO} \& {\scshape Latindex} revistas, desde 2013}
 \end{itemize}
@@
 \vspace{1mm}
-\end{cvparagraph}
+\end{publications}

### 2020-08-23 spanish/sections/teaching.tex
Create teaching.tex
Update teaching.tex

--- 2020-08-21 sections/teaching.tex
@@
 
-\cvsection{Relevant Teaching Experience}
+\cvsection{Experiencia en docencia relevante}
 
-\begin{cventries}
+\begin{publications}
 
 \begin{itemize}
-\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
+\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, RU}
 \begin{itemize}
-\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
+\item[$\circ$]{\small Gobierno Comparado (tutorial de pregrado, Prof. Petra Schleiter), Hilary 2020}
 \end{itemize}
-\item{\small Faculty of Economics and Management, {\bfseries Universidad de Santiago}, Santiago, Chile}
+\item{\small Facultad de Administración y Economía, {\bfseries Universidad de Santiago}, Santiago, Chile}
 \begin{itemize}
-\item[$\circ$]{\small Political Science I (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
-\item[$\circ$]{\small Political Science II (undergraduate lecture), Spring 2015-2018}
-\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), Fall 2018}
-\item[$\circ$]{\small Workshop for Research Design (graduate seminar), Spring 2017-2018}
-\item[$\circ$]{\small Research Methodology (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
-\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), Fall 2017}
+\item[$\circ$]{\small Ciencia Política I (curso de pregrado), primavera 2014, 2018, otoño 2015-2019}
+\item[$\circ$]{\small Ciencia Política II (curso de pregrado), primavera 2015-2018}
+\item[$\circ$]{\small Econometría para las Políticas Públicas (curso de pregrado), otoño 2018}
+\item[$\circ$]{\small Taller de Diseño de Investigación (seminario de postgrado), primavera 2017-2018}
+\item[$\circ$]{\small Metodología de la Investigación (curso de pregrado), primavera 2014-2015, otoño 2015-2017}
+\item[$\circ$]{\small Introducción a los Métodos Cuantitativos (curso de pregrado), otoño 2017}
 \end{itemize}
-\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
+\item{\small Escuela de Gobierno y Gestión Pública, {\bfseries Universidad de Chile}, Santiago, Chile}
 \begin{itemize}
-\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), Fall 2016}
-\item[$\circ$]{\small Political Analysis (undergraduate lecture), Fall 2014}
-\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
+\item[$\circ$]{\small Estudio de los Fenómenos Políticos (curso de pregrado), otoño 2016}
+\item[$\circ$]{\small Análisis Político (curso de pregrado), otoño 2014}
+\item[$\circ$]{\small Elitismo y Democracia (curso de pregrado, Prof. Alejandro Olivares), primavera 2013-2014}
 \end{itemize}
@@
 \vspace{1mm}
-\end{cventries}
+\end{publications}

### 2020-08-23 spanish/sections/working-papers.tex
Create working-papers.tex
Update working-papers.tex

--- 2020-08-21 sections/working-papers.tex
@@
 
-\cvsection{Working Papers}
+\cvsection{Documentos de trabajo}
 
-\begin{cventries}
+\begin{publications}
 
@@
 \item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
-({\itshape forthcoming}).
-Applying ForceAtlas2, a Continuous Graph LayoutAlgorithm, to the Elites Study.
-Tufte Working Papers, (1), 1--13.
-{\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
+({\itshape próximamente}).
+Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continúo, para el estudio de las élites.
+{\itshape Tufte Working Papers}, (1), 1--13.} \vspace{1mm}
 
@@
 (2016).
-Revolving Door.
-Analysis of Public-Private Circulation in Chile (2000-2014).
+¿Puerta giratoria?
+Análisis de la circulación público-privada en Chile (2000-2014).
 {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, (7), 1--40.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}
+\\ {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}
 
@@
 (2016).
-Undersecretaries Rotation in the Chilean Cabinets (1990-2014).
+A rotatividade de subsecretários dos ministérios no Chile (1990-2014).
 {\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil.
 NUSP/UFPR, 3}(5), 1--19.
-{\footnotesize \scshape [in Portuguese]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+\\ {\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
 
@@
 (2016).
-Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases.
+Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave.
 {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, (2), 1--26.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}

### 2020-08-24 spanish/sections/awards.tex
Update awards.tex

@@
 \cvhonor
-{Becas de Libros y Viaje St Hilda's College en la Universidad de Oxford} 
-{Asignaciones para libros y participación en conferencias (la subvención para viajes se rechazó debido a la pandemia de coronavirus), USD{\$} 970} 
+{Beca de Libros y de Viaje St Hilda's College en la Universidad de Oxford} 
+{Asignaciones para libros y participación en conferencias (la subvención para viajes se rechazó por la pandemia de coronavirus), USD{\$} 970} 
 {Oxford, RU}
@@
 {Beca Escuela de Verano CESS}
-{Apoyo financiero para participar en la Escuela de Verano Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), USD{\$} 260}
+{Apoyo financiero para participar en la Escuela de Verano en Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), USD{\$} 260}
 {Santiago, Chile}
@@
 {Beca Escuela de Invierno ACCP}
-{Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgado por la Asociación Chilena de Ciencia Política (ACCP), USD{\$} 400}
+{Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgada por la Asociación Chilena de Ciencia Política (ACCP), USD{\$} 400}
 {Montevideo, Uruguay}
@@
 \cvhonor
-{Mejor calificación en la tesis de Magíster}
+{Mejor calificación en tesis de Magíster}
 {La más alta calificación y las felicitaciones del jurado en la Universidad de Chile}

### 2020-08-24 spanish/sections/experience.tex
Update experience.tex

@@
 {Santiago, Chile} 
-{2018 - en comisión}
+{2019 - en comisión}
+{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
+
+\cventry
+{Profesor Adjunto} 
+{Universidad de Santiago} 
+{Santiago, Chile} 
+{2014 - 2018}
 {Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
@@
 \cventry
-{Profesor Adjunto} 
-{Universidad de Santiago} 
+{Docente} 
+{Universidad de Chile} 
 {Santiago, Chile} 
-{2014 - 2017}
-{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
+{2013 - 2016}
+{Escuela de Gobierno y Gestión Pública, Instituto de Asuntos Públicos}\vspace{1.5mm}
 

### 2020-08-24 spanish/sections/expertise.tex
Update expertise.tex

@@
 {Techniques} 
-{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}
+{Análisis de supervivencia, modelamiento con regresiones, modelos multinivel, análisis factorial,}
 
@@
 {} 
-{network analysis, qualitative comparative analysis, topic modelling} \\
+{análisis espacial, análisis de redes sociales, análisis comparado cualitativo, modelamiento}
+
+\cvskill
+{} 
+{temático} \\
 

### 2020-08-24 spanish/sections/papers.tex
Update papers.tex

@@
 {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \pagebreak %% \vspace{1mm}
 \end{benumerate}

### 2020-08-24 spanish/sections/reviewer.tex
Update reviewer.tex

@@
 
-\cvsection{Revisiones de pares y como experto}
+\cvsection{Revisiones como árbitro \& experto}
 
@@
 Países Bajos, 2018-2019}
-\item{\small Revisor en {\scshape WoS} \& {\scshape Scopus} revistas, desde 2013}
-\item{\small Revisor en {\scshape SciELO} \& {\scshape Latindex} revistas, desde 2013}
+\item{\small Revisor en revistas {\scshape WoS} \& {\scshape Scopus}, desde 2013}
+\item{\small Revisor en revistas {\scshape SciELO} \& {\scshape Latindex}, desde 2013}
 \end{itemize}

### 2020-08-24 spanish/sections/summary.tex
Update summary.tex

@@
 
-Soy doctorante en el programa de Ciencia Política en el Departamento de Política y Relaciones Internacionales en St Hilda's College en la Universidad de Oxford, Reino Unido.
+Soy doctorante en el programa de Ciencia Política en el Departamento de Política y Relaciones Internacionales y en St Hilda's College en la Universidad de Oxford, Reino Unido.
 Además, soy Profesor Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago, donde he trabajado desde el 2014.
@@
 Antes de comenzar mis estudios doctorales, obtuve una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública con distinción y un Magíster en Ciencia Política con máxima distinción, ambos grados en la Universidad de Chile.
-Además, trabajé como profesor en la Universidad de Santiago y de Chile y como consultor para el Programa de las Naciones Unidas para el Desarrollo.
+Además, trabajé como profesor en la Universidad de Santiago y en la Universidad de Chile y como consultor para el Programa de las Naciones Unidas para el Desarrollo.
 
@@
 Mi investigación es apoyada por la Agencia Nacional de Investigación y Desarrollo de Chile.
-Adicionalmente, estoy interesado la socialización de la élite política, servicios civiles, participación política, medios digitales y gobierno electrónico y abierto.
+Adicionalmente, estoy interesado en la socialización de la élite política, servicios civiles, participación política, medios digitales y gobierno electrónico y abierto.
 \vspace{1mm}

### 2020-08-24 sections/experience.tex
Update experience.tex

@@
 {Santiago, Chile} 
-{2018 - on leave}
+{2019 - on leave}
 {Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}
+
+\cventry
+{Adjunct Professor} 
+{Universidad de Santiago} 
+{Santiago, Chile} 
+{2014 - 2018}
+{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}
 
@@
 \cventry
-{Adjunct Professor} 
-{Universidad de Santiago} 
+{Lecturer} 
+{Universidad de Chile} 
 {Santiago, Chile} 
-{2014 - 2017}
-{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}
+{2013 - 2016}
+{School of Government and Public Management, Institute for Public Affairs}\vspace{1.5mm}
 

### 2020-08-24 sections/papers.tex
Update papers.tex

@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \pagebreak %% \vspace{1mm}
+\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
 \end{benumerate}

### 2020-08-24 sections/references.tex
Update references.tex

--- 2020-08-21 sections/references.tex
@@
 \item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \vspace{1.5mm}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \pagebreak %% \vspace{1.5mm}
 \item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}

### 2020-09-11 sections/working-papers.tex
Update working-papers.tex

@@
 \item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
-({\itshape forthcoming}).
-Applying ForceAtlas2, a Continuous Graph LayoutAlgorithm, to the Elites Study.
-Tufte Working Papers, (1), 1--13.
-{\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
+(2020).
+Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study.
+{\itshape Tufte Working Papers}, (1), 1--15.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape url:} \href{https://tuftepapers.com/2020/09/aplicacion-de-ForceAtlas2-algoritmo-de-diseno-grafico.html}{\textcolor{blue}{https://tuftepapers.com}}.
+{\scshape {\footnotesize SocArXiv} doi:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}
 

### 2020-09-11 spanish/sections/expertise.tex
Update expertise.tex

@@
 \cvskill
-{Interests}
+{Intereses}
 {Composición y nombramiento de gabinetes, rotación ministerial, socialización de élites políticas,}
@@
 \cvskill
-{Techniques} 
+{Técnicas} 
 {Análisis de supervivencia, modelamiento con regresiones, modelos multinivel, análisis factorial,}

### 2020-09-11 sections/papers.tex
Update papers.tex

@@
 \item{\small Gonz\'alez-Bustamante, B.
-({\itshape forthcoming}).
+(2021).
 Evolution and Early Government Responses to COVID-19 in South America.
-{\itshape World Development}.
-{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.}\vspace{1mm}
+{\itshape World Development, 137}.
+{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.
+{\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}.
+{\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
 \\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}

### 2020-09-11 spanish/sections/papers.tex
Update papers.tex

@@
 \begin{benumerate}{5}
-\item{\small Gonz\'alez-Bustamante, B. ({\itshape próximamente}). Evolution and Early Government Responses to COVID-19 in South America. {\itshape World Development}.}\vspace{1mm}
+\item{\small Gonz\'alez-Bustamante, B.
+(2021).
+Evolution and Early Government Responses to COVID-19 in South America.
+{\itshape World Development, 137}.
+{\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
 
@@
 {\itshape Iberoamericana, XX}(74), 229--259.
-{\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}.
+{\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
 {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}

### 2020-12-04 sections/expertise.tex
Update expertise.tex

@@
 \cvskill
-{Interests}
-{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}
+{Main Interests}
+{Cabinets composition and allocation, ministerial turnover, presidential systems, political elites, }
 
@@
 {}
-{systems, political participation, digital media, electronic government}\\
+{civil service systems, crisis management}\\
 
@@
 {Techniques} 
-{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}
+{Survival analysis and competing risks models, propensity score methods, multilevel models, }
 
@@
 {} 
-{network analysis, qualitative comparative analysis, topic modelling} \\
+{spatial analysis, social network analysis, qualitative comparative analysis} \\
 

### 2020-12-04 sections/summary.tex
Update summary.tex

@@
 My doctoral research is supervised by Professor Petra Schleiter at St Hilda’s College and focuses on the stability of cabinets in Latin American presidential democracies.
-My research is supported by the Chilean National Agency for Research and Development.
-Additionally, I am interested in the political elite’s socialisation, civil services, political participation, digital media, as well as electronic and open government.
+My research is financially supported by the Chilean National Agency for Research and Development.
+Additionally, I am interested in the political elite’s socialisation, civil services, and crisis management.
 \vspace{1mm}

### 2020-12-04 spanish/sections/experience.tex
Update experience.tex

@@
 \cventry
-{Profesor Instructor} 
+{Instructor} 
 {Universidad de Santiago} 

### 2020-12-04 spanish/sections/expertise.tex
Update expertise.tex

--- 2020-08-21 spanish/sections/expertise.tex
@@
 \cvskill
-{Interests}
-{Composición y nombramiento de gabinetes, rotación ministerial, socialización de élites políticas,}
+{Intereses}
+{Composición y nombramiento de gabinetes, rotación ministerial, sistemas presidenciales, élites}
 
@@
 {}
-{sistemas de servicio civil, participación política, medios digitales, gobierno electrónico}\\
+{políticas, sistemas de servicio civil, gestión de crisis}\\
 
 \cvskill
-{Techniques} 
-{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}
+{Técnicas} 
+{Análisis de supervivencia y modelos de riesgos competitivos, métodos de puntuación de propensión,}
 
@@
 {} 
-{network analysis, qualitative comparative analysis, topic modelling} \\
+{modelos multinivel, análisis espacial, análisis de redes sociales, análisis comparado cualitativo} \\
 

### 2020-12-04 spanish/sections/summary.tex
Update summary.tex

@@
 Soy doctorante en el programa de Ciencia Política en el Departamento de Política y Relaciones Internacionales y en St Hilda's College en la Universidad de Oxford, Reino Unido.
-Además, soy Profesor Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago, donde he trabajado desde el 2014.
+Además, soy Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago, donde he trabajado desde el 2014.
 
-Antes de comenzar mis estudios doctorales, obtuve una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública con distinción y un Magíster en Ciencia Política con máxima distinción, ambos grados en la Universidad de Chile.
+Antes de comenzar mis estudios doctorales, obtuve una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública con distinción y un Magíster en Ciencia Política con distinción máxima, ambos grados en la Universidad de Chile.
 Además, trabajé como profesor en la Universidad de Santiago y en la Universidad de Chile y como consultor para el Programa de las Naciones Unidas para el Desarrollo.
@@
 Mi investigación es apoyada por la Agencia Nacional de Investigación y Desarrollo de Chile.
-Adicionalmente, estoy interesado en la socialización de la élite política, servicios civiles, participación política, medios digitales y gobierno electrónico y abierto.
+Adicionalmente, estoy interesado en la socialización de la élite política, servicios civiles y gestión de crisis.
 \vspace{1mm}

### 2020-12-17 sections/summary.tex
Update summary.tex

@@
 
-I am a PRS in the DPhil in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
+I am a PRS in the DPhil (PhD) in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
 Furthermore, I am an Instructor in the Department of Public Administration and Policy at the Faculty of Economics and Management at the Universidad de Santiago, where I have been working since 2014.

### 2021-01-03 sections/awards.tex
Update awards.tex

@@
 {Becas Chile Doctoral Scholarship Abroad} 
-{Tuition fees, transport and living expenses for pursuing a DPhil at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
+{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
 {Oxford, UK}

### 2021-01-03 spanish/sections/papers.tex
Update papers.tex

@@
 Evolution and Early Government Responses to COVID-19 in South America.
-{\itshape World Development, 137}.
+{\itshape World Development, 137}, 105180.
 {\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2020).
+The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
+{\itshape Bulletin of Latin American Research, 39}(5), 582--597.
+\\ {\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
 
@@
 (2019).
-The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
-{\itshape Bulletin of Latin American Research}.
-Early View.
-\\ {\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, (80), 1--27.
+{\scshape url}: \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
+{\scshape {\footnotesize SocArXiv} doi}: \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+%% \item{\small Gonz\'alez-Bustamante, B.
 (2019).

### 2021-03-15 sections/experience.tex
Update experience.tex

@@
 \cventry
-{Instructor} 
-{Universidad de Santiago} 
+{Instructor Professor} 
+{Universidad de Santiago de Chile} 
 {Santiago, Chile} 
 {2019 - on leave}
-{Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}
+{Management and Public Policies Department, Faculty of Administration and Economics}\vspace{1.5mm}
 
@@
 {Adjunct Professor} 
-{Universidad de Santiago} 
+{Universidad de Santiago de Chile} 
 {Santiago, Chile} 
 {2014 - 2018}
-{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}
+{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
 
@@
 {Consultant} 
-{United Nations Development Programme} 
+{United Nations Development Programme (UNDP)} 
 {Santiago, Chile} 

### 2021-03-15 sections/summary.tex
Update summary.tex

--- 2020-12-04 sections/summary.tex
@@
 
-I am a PRS in the DPhil in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
-Furthermore, I am an Instructor in the Department of Public Administration and Policy at the Faculty of Economics and Management at the Universidad de Santiago, where I have been working since 2014.
+I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
+I am currently based at Oxford, working on my research.
+Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile.
 
-Before starting the DPhil, I earned a BA (2:1) in Government and an MA (1st) in Political Science, both from the Universidad de Chile.
-Moreover, I worked as a lecturer at the Universidad de Santiago and the Universidad de Chile, as well as a consultant for the United Nations Development Programme.
+Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
+Moreover, I was a lecturer at the Universidad de Chile and a consultant for the United Nations Development Programme (UNDP).
 
-My doctoral research is supervised by Professor Petra Schleiter at St Hilda’s College and focuses on the stability of cabinets in Latin American presidential democracies.
-My research is financially supported by the Chilean National Agency for Research and Development.
-Additionally, I am interested in the political elite’s socialisation, civil services, and crisis management.
+My doctoral research is supervised by Professor Petra Schleiter and focuses on cabinets’ stability in Latin American presidential democracies.
+In my DPhil project, I combine the principal-agent theory elements to evaluate the actors’ incentives and strategies in presidential systems.
+My empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations.
+My research is funded by the Chilean National Agency for Research and Development.
 \vspace{1mm}

### 2021-03-15 spanish/sections/experience.tex
Update experience.tex

@@
 {Instructor} 
-{Universidad de Santiago} 
+{Universidad de Santiago de Chile} 
 {Santiago, Chile} 
@@
 {Profesor Adjunto} 
-{Universidad de Santiago} 
+{Universidad de Santiago de Chile} 
 {Santiago, Chile} 
@@
 {Consultor} 
-{Programa de las Naciones Unidas para el Desarrollo} 
+{Programa de las Naciones Unidas para el Desarrollo (PNUD)} 
 {Santiago, Chile} 

### 2021-03-15 spanish/sections/summary.tex
Update summary.tex

@@
 
-Soy doctorante en el programa de Ciencia Política en el Departamento de Política y Relaciones Internacionales y en St Hilda's College en la Universidad de Oxford, Reino Unido.
-Además, soy Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago, donde he trabajado desde el 2014.
+Estoy completando mi tesis doctoral en el Departamento de Ciencia Política y Relaciones Internacionales y en St Hilda’s College en la Universidad de Oxford, Reino Unido.
+Actualmente me encuentro establecido en Oxford, trabajando en mi investigación.
+Además, soy Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago de Chile.
 
-Antes de comenzar mis estudios doctorales, obtuve una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública con distinción y un Magíster en Ciencia Política con distinción máxima, ambos grados en la Universidad de Chile.
-Además, trabajé como profesor en la Universidad de Santiago y en la Universidad de Chile y como consultor para el Programa de las Naciones Unidas para el Desarrollo.
+Antes de comenzar mis estudios doctorales, en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
+Además, fui profesor en la Universidad de Chile y consultor para el Programa de las Naciones Unidas para el Desarrollo (PNUD).
 
-Mi investigación doctoral es supervisada por la Profesora Petra Schleiter en St Hilda's College y se enfoca en la estabilidad de los gabinetes en las democracias presidenciales latinoamericanas.
-Mi investigación es apoyada por la Agencia Nacional de Investigación y Desarrollo de Chile.
-Adicionalmente, estoy interesado en la socialización de la élite política, servicios civiles y gestión de crisis.
+Mi investigación doctoral es supervisada por la Profesora Petra Schleiter y se enfoca en la estabilidad de los gabinetes en las democracias presidenciales latinoamericanas.
+En mi proyecto doctoral combino elementos de la teoría principal-agente para evaluar los incentivos y estrategias de los actores en los sistemas presidenciales.
+Mi estrategia empírica emplea métodos de puntuación de propensión y emparejamiento, modelos de riesgos competitivos y modelos de variables instrumentales.
+Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile.
 \vspace{1mm}

### 2021-04-26 sections/book-chapters.tex
Update book-chapters.tex

@@
 {\scshape doi}: \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}} \pagebreak %% \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}} \pagebreak %% \vspace{1mm}
 
@@
 In G.
-Sibaja (ed.), {\itshape Nuevos medios y comunicaci\'on pol\'itica digital}.
+Sibaja (ed.), {\itshape Nuevos Medios y Comunicaci\'on Pol\'itica Digital}.
 San Jose: Fundación Educativa San Judas Tadeo.

### 2021-04-26 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 Santiago: RIL Editores.
-\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
 

### 2021-04-26 spanish/sections/languages.tex
Create languages.tex
Update languages.tex

--- 2020-08-21 sections/languages.tex
@@
 
-\cvsection{Languages \& Softwares}
+\cvsection{Idiomas \& manejo de software}
 
@@
 \cvskill
-{Languages} 
-{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}
+{Idiomas} 
+{Español (hablante nativo), inglés (fluido), portugués (habilidades de lectura avanzadas),}
 
@@
 {} 
-{reading skills)} \\
+{francés (habilidades de lectura elementales)} \\
 
 \cvskill
-{Programming} 
+{Programación \&} 
 {R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}
@@
 \cvskill
-{} 
-{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}
+{software} 
+{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}
 
@@
 {} 
-{{\scshape xhtml}, Notepad{\footnotesize ++}} \\
+{{\scshape css}, {\scshape xhtml}} \\
 

### 2021-04-26 sections/languages.tex
Update languages.tex

--- 2020-08-21 sections/languages.tex
@@
 
-\cvsection{Languages \& Softwares}
+\cvsection{Languages \& Software}
 
@@
 {Languages} 
-{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}
+{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), French}
 
@@
 {} 
-{reading skills)} \\
+{(elemental reading skills)} \\
 
 \cvskill
-{Programming} 
+{Programming \&} 
 {R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}
@@
 \cvskill
-{} 
-{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}
+{Software} 
+{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}
 

### 2021-04-26 spanish/sections/papers.tex
Update papers.tex

@@
 \\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
 
@@
 {\itshape Convergencia.
-Revista de Ciencias Sociales}, (80), 1--27.
-{\scshape url}: \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
-{\scshape {\footnotesize SocArXiv} doi}: \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+Revista de Ciencias Sociales}, 80, 1--27.
+{\scshape url}: \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.\\ {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
 
@@
 {\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
 
@@
 {\itshape N\'oesis.
-Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42..
+Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
 {\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}
@@
 Cambios de gabinete y supervivencia de los ministros en Chile durante los gobiernos de la Concertación (1990-2010).
-{\itshape Colombia Internacional}, (87), 81--108.
+{\itshape Colombia Internacional}, 87, 81--108.
 \\ {\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
@@
 Los think tanks en el gabinete: Una exploración del caso chileno (2006-2014).
-{\itshape Revista de Sociolog\'ia,} (29), 37--54.
+{\itshape Revista de Sociolog\'ia,} 29, 37--54.
 {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
@@
 El estudio de las élites en Chile: Aproximaciones conceptuales y metodológicas.
-{\itshape Intersticios Sociales,} (6), 1--20.
+{\itshape Intersticios Sociales,} 6, 1--20.
 {\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
@@
 Campañas digitales: ¿Branding o participación política?
-{\itshape M\'as Poder Local,} (12), 32--39.
+{\itshape M\'as Poder Local,} 12, 32--39.
 {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}

### 2021-04-26 sections/papers.tex
Update papers.tex

@@
 \begin{benumerate}{5}
+%% \item{\small Gonz\'alez-Bustamante, B.
+(2021).
+Evolution and Early Government Responses to COVID-19 in South America.
+{\itshape World Development, 137}, 105180.
+{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.
+{\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
+
 \item{\small Gonz\'alez-Bustamante, B.
@@
 Evolution and Early Government Responses to COVID-19 in South America.
-{\itshape World Development, 137}.
-{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.
+{\itshape World Development, 137}, 105180.
 {\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
+%% \item{\small Gonz\'alez-Bustamante, B.
+(2020).
+The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
+{\itshape Bulletin of Latin American Research, 39}(5), 582--597.
+{\footnotesize \scshape [{\bfseries 0.586} 2019-JIF, {\bfseries Q3} Area Studies]}.
+{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2020).
+The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
+{\itshape Bulletin of Latin American Research, 39}(5), 582--597.
+{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+
+%% \item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
 (2020).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
-(2019).
-The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
-{\itshape Bulletin of Latin American Research}.
-Early View.
-{\footnotesize \scshape [{\bfseries 0.586} 2019-JIF, {\bfseries Q3} Area Studies]}.
-{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+\item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
+(2020).
+Determinants of E-Government in the Municipalities: Evidence from the Chilean Case.
+{\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+%% \item{\small Gonz\'alez-Bustamante, B.
 (2019).
@@
 
+%% \item{\small Gonz\'alez-Bustamante, B.
+(2019).
+Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, (80), 1--27.
+{\footnotesize \scshape [in Spanish, {\bfseries 0.704} 2019-JIF, {\bfseries Q4} Sociology]}.
+{\scshape url}: \\ \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
+{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2019).
+Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, 80, 1--27.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape url}:  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
+\\{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+
+%% \item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
+{\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
+{\footnotesize \scshape [in Spanish, {\bfseries 0.714} 2019-JIF, {\bfseries Q4} Political Science]}.
+{\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
+
 \item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L.
@@
 {\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.714} 2019-JIF, {\bfseries Q4} Political Science]}.
+{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
@@
 {\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
-\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
+\\{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
 
@@
 Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010).
-{\itshape Colombia Internacional}, (87), 81--108.
+{\itshape Colombia Internacional}, 87, 81--108.
 {\footnotesize \scshape [in Spanish]}.
@@
 Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014).
-{\itshape Revista de Sociolog\'ia,} (29), 37--54.
+{\itshape Revista de Sociolog\'ia,} 29, 37--54.
 {\footnotesize \scshape [in Spanish]}.
@@
 The Study of the Elites in Chile: Theoretical and Methodological Approaches.
-{\itshape Intersticios Sociales,} (6), 1--20.
+{\itshape Intersticios Sociales,} 6, 1--20.
 {\footnotesize \scshape [in Spanish]}.
@@
 Digital Campaigns: Branding or Political Participation?
-{\itshape M\'as Poder Local,} (12), 32--39.
+{\itshape M\'as Poder Local,} 12, 32--39.
 {\footnotesize \scshape [in Spanish]}.

### 2021-04-26 sections/working-papers.tex
Update working-papers.tex

@@
 
-\begin{benumerate}{4}
+\begin{benumerate}{5}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2021, {\itshape forthcoming}).
+Sophistication, Participation, and Political Engagement in Latin America.
+{\itshape Tufte Working Papers}, 2.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}} \vspace{1mm}
 
@@
 Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study.
-{\itshape Tufte Working Papers}, (1), 1--15.
+{\itshape Tufte Working Papers}, 1, 1--15.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://tuftepapers.com/2020/09/aplicacion-de-ForceAtlas2-algoritmo-de-diseno-grafico.html}{\textcolor{blue}{https://tuftepapers.com}}.
-{\scshape {\footnotesize SocArXiv} doi:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}
 
@@
 Analysis of Public-Private Circulation in Chile (2000-2014).
-{\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, (7), 1--40.
+{\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
 {\footnotesize \scshape [in Spanish]}.
@@
 Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases.
-{\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, (2), 1--26.
+{\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
 {\footnotesize \scshape [in Spanish]}.

### 2021-04-26 spanish/sections/working-papers.tex
Update working-papers.tex

@@
 
-\begin{benumerate}{4}
+\begin{benumerate}{5}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2021, {\itshape próximamente}).
+Sofisticación, participación y compromiso político en América Latina.
+{\itshape Tufte Working Papers}, 2.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}} \vspace{1mm}
 
 \item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
-({\itshape próximamente}).
+(2020).
 Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continúo, para el estudio de las élites.
-{\itshape Tufte Working Papers}, (1), 1--13.} \vspace{1mm}
+{\itshape Tufte Working Papers}, 1, 1--15.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}
 
@@
 Análisis de la circulación público-privada en Chile (2000-2014).
-{\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, (7), 1--40.
+{\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
 \\ {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}
@@
 Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave.
-{\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, (2), 1--26.
+{\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
 {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}

### 2021-04-26 spanish/sections/experience.tex
Update experience.tex

@@
 \cventry
-{Instructor} 
+{Profesor Instructor} 
 {Universidad de Santiago de Chile} 

### 2021-06-01 sections/experience.tex
Update experience.tex

@@
 {2013 - 2016}
-{School of Government and Public Management, Institute for Public Affairs}\vspace{1.5mm}
+{School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}
 

### 2021-06-01 sections/summary.tex
Update summary.tex

@@
 I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
-I am currently based at Oxford, working on my research.
+I am currently based in Oxford, working on my research.
 Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile.
@@
 Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
-Moreover, I was a lecturer at the Universidad de Chile and a consultant for the United Nations Development Programme (UNDP).
+Moreover, I served as a lecturer at the Universidad de Chile and a consultant for the United Nations Development Programme (UNDP).
 

### 2021-09-01 sections/book-chapters.tex
Update book-chapters.tex

@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \pagebreak %% \vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}} \pagebreak %% \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}} \vspace{1mm}
 

### 2021-09-01 sections/papers.tex
Update papers.tex

@@
 {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
+
 \end{benumerate}
@@
 
-\begin{benumerate}{7}
+\begin{benumerate}{8}
+
+\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2020).
+Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service.
+{\itshape Revista de Gestión Pública, IX}(2), 151--169.
+{\footnotesize \scshape [in Spanish and English]}.
+{\scshape doi}: \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}}\vspace{1mm}
+
 \item{\small Olivares, A.
@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}
+
 \end{benumerate}
@@
 {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+
 \end{benumerate}

### 2021-09-01 spanish/sections/papers.tex
Update papers.tex

@@
 \begin{benumerate}{5}
+
 \item{\small Gonz\'alez-Bustamante, B.
@@
 
-\begin{benumerate}{7}
+\begin{benumerate}{8}
+
+\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2020).
+Altos directivos públicos: Un nuevo conjunto de datos de miembros del servicio civil chileno.
+{\itshape Revista de Gestión Pública, IX}(2), 151--169.
+\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}}\vspace{1mm}
+
 \item{\small Olivares, A.
@@
 {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \pagebreak %% \vspace{1mm}
+\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}
+
 \end{benumerate}
@@
 \begin{benumerate}{9}
+
 \item{\small Gonz\'alez-Bustamante, B.

### 2021-09-22 sections/selected-training.tex
Create selected-training.tex

--- 2020-08-21 spanish/sections/training.tex
@@
 
-\cvsection{Certification \& Training}
+\cvsection{Selected Certifications \& Training}
 
-\vspace{1mm}
+%% OX|BER
+%% USACH-Nuffield
+%% R Conference
 
 \begin{cvhonors}
-\cvhonor
-{DPhil Traning Programme Trinity Term at the University of Oxford} 
-{Training in geospatial modelling} 
-{Oxford, UK}
-{2020}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{DPhil Traning Programme Hilary Term at the University of Oxford} 
-{Training in formal analysis and game theory, randomised trials, regression and matching, instrumental variables, regression discontinuity, differences-in-differences, and placebo tests} 
-{Oxford, UK}
-{2020}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
+\cvconf
 {Research Data Workshop IT Centre at the University of Oxford} 
-{Training in managing research data} 
 {Oxford, UK}
@@
 \begin{cvhonors}
-\cvhonor
-{DPhil Traning Programme Michaelmas Term at the University of Oxford}
-{Training in research design, logit and OLS models, multinomial models, ordinal logistic regressions,  OLS regularisation and cross-validation procedures, shrinkage methods, regression tree, random forest algorithm, principal component analysis based on unsupervised learning, and count models}
-{Oxford, UK}
-{2019}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
+\cvconf
 {Longitudinal Networks with RSiena Workshop at the Pontifica Universidad Cat\'olica}
-{Training in stochastic actor oriented models in R}
 {Santiago, Chile}
@@
 \begin{cvhonors}
-\cvhonor
+\cvconf
 {Universidad de Santiago Winter School for Academics}
-{Training in evaluation techniques and teaching strategies for academic writing}
 {Santiago, Chile}
@@
 \begin{cvhonors}
-\cvhonor
+\cvconf
 {Nuffield-USACH CEES Experimental Summer School}
-{Training in experiments in social sciences}
 {Santiago, Chile}
@@
 \begin{cvhonors}
-\cvhonor
+\cvconf
 {Universidad de Santiago Winter School for Academics}
-{Training in qualitative data analysis in {\scshape atlas}.ti}
 {Santiago, Chile}
@@
 \begin{cvhonors}
-\cvhonor
+\cvconf
 {Latin American Political Science Association Methodological School}
-{Training in programming in Python, social network analysis in R and Python, and qualitative comparative analysis in R}
 {Lima, Peru}
@@
 \begin{cvhonors}
-\cvhonor
+\cvconf
 {Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
-{Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
 {Montevideo, Uruguay}
@@
 \begin{cvhonors}
-\cvhonor
+\cvconf
 {Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
-{Training in set theory and logic, case studies and multi-methods, process tracing, and experiments in social sciences}
 {Santiago, Chile}

### 2021-09-23 sections/selected-training.tex
Update selected-training.tex

@@
 \cvconf
-{Longitudinal Networks with RSiena Workshop at the Pontifica Universidad Cat\'olica}
+{Longitudinal Networks with RSiena Workshop at the P Universidad Cat\'olica}
 {Santiago, Chile}
@@
 {Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
-{Montevideo, Uruguay}
+{MVD, Uruguay}
 {2015}
@@
 \cvconf
-{Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
+{P Universidad Ca\'olica Summer School in Mixed Methods}
 {Santiago, Chile}

### 2021-11-24 sections/awards.tex
Update awards.tex

@@
 %% Creative Commons Attribution 4.0 International License
-%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt
+%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md
 
@@
 \cvhonor
-{St Hilda's College at the University of Oxford Book and Travel Grants} 
-{Allowances for books and conference participation (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
+{St Hilda's College Travel Grant} 
+{Allowances for conference participation in the USA, {\pounds} 950} 
+{Oxford, UK}
+{2022}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
+{St Hilda's College Muriel Wise Fund and Book Grant} 
+{Research grant for the training of machine learning algorithms, DPhil (PhD) project data storage, and allowances for books, {\pounds} 530} 
+{Oxford, UK}
+{2021}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
+{St Hilda's College Travel and Book Grants} 
+{Allowances for conference participation in Portugal and books (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
 {Oxford, UK}
@@
 {Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
-{Montevideo, Uruguay}
+{Montevideo, URY}
 { 2015}

### 2021-11-24 sections/book-chapters.tex
Update book-chapters.tex

--- 2021-04-26 sections/book-chapters.tex
@@
 Santiago: Social-Ediciones.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}}\vspace{1mm}
 

### 2021-11-24 sections/conferences-full.tex
Create conferences-full.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{List of Conference and Seminar Presentations}

\begin{publications}

\begin{benumerate}{66}

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Dismissals of Ministers in Latin America}. Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, San Francisco, USA.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Ministerial Turnover in Latin America}. Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Cisternas, C. (2022). {\itshape Seniority and Cosponsorship in the Chilean Lower House 2006-2018}. Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}

\item{\small González-Bustamante, B. (2021). {\itshape The Use of Machine Learning for Public Affairs Research}. Presentation delivered the XII Chilean Congress of Public Administration, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2021). {\itshape Methodological Challenges and Innovations in the Study of Elites}. Presentation XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences, Virtual.}\vspace{1mm}

%% Bamberg

\item{\small González-Bustamante, B. (2021). {\itshape R Applications in Social Sciences: Data Mining and Economic Modelling}. Presentation delivered at the Political Science Method Lecture at the Universidad de Chile, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2021). {\itshape Vertically Integrated Project: Machine Learning Applications in Public Policy and Economics}. Presentation delivered at the VIP Project Workshop at the Universidad Mayor, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2021). {\itshape Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile}. Presentation delivered at the XXVI World Congress of Political Science, Virtual.}\vspace{1mm}

\item{\small Cisternas, C., \& González-Bustamante, B. (2021). {\itshape Political Careers and Co-Sponsorship in the Chilean Lower House 2010-2018}. Presentation delivered at the XXVI World Congress of Political Science, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2021). {\itshape Data Mining, Modelling and Machine Learning Applications for Social Sciences}. Presentation delivered at the I Workshop of the Training Data Lab, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape Evolution and early governmental responses to COVID-19 in South America}. Presentation delivered at the Workshop of the School of Political Science and Public Administration at the Universidad de Talca, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape New Approaches to Studying Political Elites}. Presentation delivered at the Colloquium of the Observatório de Elites, Universidade Federal do Paraná, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape Protest and Social Unrest in Latin America: Determinants and Critical Junctures}. Presentation delivered at the Seminar Cycle on Human Rights in Latin America, Virtual.}\vspace{1mm} %% Sergipe, Brazil

\item{\small González-Bustamante, B. (2020). {\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}. Presentation delivered at the PRS Workshop Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}

\item{\small Orchard, X., \& González-Bustamante, B. (2020). {\itshape An Exploration of Profiles and Perceptions in the Diagnosis of Journalistic Practice in Chile}. Presentation delivered at the VI Chilean Association of Communication Researchers Congress, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2019). {\itshape Presidential Stability and Minister Turnover in Argentina, Brazil, and Chile}. Presentation delivered at the XXXVII International Congress of the Latin American Studies Association, Boston, USA.}\vspace{1mm}

\item{\small González-Bustamante, B. (2018). {\itshape Cabinet Stability and Turnover from a Multilevel Approach}. Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Cisternas, C. (2018). {\itshape Social Network Analysis: Application for Elites Study}. Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2018). {\itshape Geospatial Analysis of Partisanship Density and Electoral Turnout: Evidence from the Chilean Case}. Presentation delivered at the XIII Chilean Congress of Political Science, Santiago, González.}\vspace{1mm}

\item{\small González-Bustamante, B. (2018). {\itshape Sophistication, Participation, and Political Engagement in Latin America}. Presentation delivered at the VII International Congress of Political Communication, Murcia, Spain.}\vspace{1mm}

\item{\small González-Bustamante, B. (2018). {\itshape Survival of Ministers and Vice-Ministers in Chile: Stability and Turnover from a Multilevel Approach}. Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics, Curitiba, Brazil.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Garrido-Vergara, L. (2018). {\itshape Trajectories and Post-Career of Ministers in Chile}. Presentation delivered at the Research Seminar of the Institute of Public Affairs at the Universidad de Chile, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Del Valle, N. (2017). {\itshape Media Pluralism and Digital Media Public Opinion}. Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A. (2017). {\itshape Revolving Door? Analysis of Public-Private Circulation in Chile}. Presentation delivered at the II Foreign Affairs Meeting, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Garrido-Vergara, L. (2017). {\itshape Socialisation Spaces and Ministerial Post-Career in the Chilean Transition and Post-Transition}. Presentation delivered at the IX Chilean Congress of Public Administration, Concepcion, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A. (2017). {\itshape Public-Private: An Especially Tenuous Frontier. Political-Professional Trajectories of the Chilean Authorities (2000-2014)}. Presentation delivered at the IX Latin American Congress of Political Science, Montevideo, Uruguay.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Joignant, A. (2016). {\itshape Gaps and Elite-Mass Congruence in Chile and Uruguay}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Joignant, A., \& González-Bustamante, B. (2016). {\itshape Family Ties in the Senate and the Chamber of Deputies, Chile from 1989 to 2014}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C. (2016). {\itshape Analysis of the Academic Production on Open Government in Spanish}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2016). {\itshape Revolving Door and Public-Private Circulation in Chile}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C. (2016). {\itshape Open Government in Latin America and Spain: Analysis of the Scientific Production in Spanish}. Presentation delivered at the XXI CLAD International Congress on the State Reform and Public Administration, Santiago, Chile.}\vspace{1mm}

\item{\small Joignant, A., \& González-Bustamante, B. (2016). {\itshape Performance of Family Political Capital in the Chilean Post-Authoritarianism}. Presentation delivered at the XII Chilean Congress of Political Science, Pucon, Chile.}\vspace{1mm}

\item{\small Olivares, A., \& González-Bustamante, B. (2016). {\itshape Turnover and Ministerial Survival Before the Chilean Democratic Breakdown}. Presentation delivered at the XII Chilean Congress of Political Science, Pucon, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Barría, D. (2016). {\itshape Production Patterns of the Contemporary Knowledge in Social Sciences}. Presentation delivered at the IX Chilean Congress of Sociology, Talca, González.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Cisternas, C. (2016). {\itshape Co-Authorship Networks of the Political Science in Spanish (2010-2015)}. Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}

\item{\small Cisternas, C., González-Bustamante, B., \& Barría, D. (2016). {\itshape Analysis of the Scientific Production in Spanish on Public Administration and Public Policies (2010-2012)}. Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}

\item{\small Cisternas, C., \& González-Bustamante, B. (2016). {\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}. Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times, Santiago, Chile.}\vspace{1mm}

\item{\small Alenda, S., \& González-Bustamante, B. (2016). {\itshape The Reshaping of the Political Right in Chile: Change and Continuity in the Perceptions of Social Inequalities}. Presentation delivered at the III ISA Forum of Sociology, Vienna, Austria.}\vspace{1mm}

\item{\small González-Bustamante, B. (2016). {\itshape Representation and Elite-Mass Congruence in Chile and Uruguay}. Presentation delivered at the XXXIV International Congress of the Latin American Studies Association, New York, USA.}\vspace{1mm}

\item{\small Alenda, S., González-Bustamante, B., \& Gartenlaub, A. (2016). {\itshape The Reshaping of the Political Right in Chile}. Presentation delivered at the XXXIV International Congress of the Latin American Studies Association, New York, USA.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Barría, D. (2015). {\itshape Stateness in the Chilean Post-Transition}. Presentation delivered at the VIII Chilean Congress of Public Administration, Rancagua, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2015). {\itshape Media Consumption and Political Participation in Argentina, Chile, and Uruguay}. Presentation delivered at the XII Argentinian Congress of Political Science, Mendoza, Argentina.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2015). {\itshape Trajectories of Ministers and Undersecretaries in Chile During Concertacion Governments (1990-2010)}. Presentation delivered at the VIII Latin American Congress of Political Science, Lima, Peru.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Barría, D. (2015). {\itshape Stateness' Support in Chile from 2007 to 2014}. Presentation delivered at the VIII Latin American Congress of Political Science, Lima, Peru.}\vspace{1mm}

\item{\small Olivares, A., \& González-Bustamante, B. (2015). {\itshape Survival of Ministers and Undersecretaries in Chile (1990-2014)}. Presentation delivered at the International Congress of Elites and Leadership, Salamanca, Spain.}\vspace{1mm}

\item{\small Garrido-Vergara, L., \& González-Bustamante, B. (2015). {\itshape Elites and Political Reforms: The Chilean Case}. Presentation delivered at the International Congress of Elites and Leadership, Salamanca, Spain.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Ruiz, I. (2014). {\itshape Radiography to the Popular Election of Regional Councillors 2013}. Presentation delivered at the XI Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}

\item{\small Thezá, M., \& González-Bustamante, B. (2014). {\itshape Dimensions of the Young People Multi-Associative Participation in Chile}. Presentation delivered at the XI Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2014). {\itshape Social Media and Malaise with Democracy in Argentina and Uruguay}. Presentation delivered at the VI Latin American Congress of Public Opinion, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2014). {\itshape Media Consumption and Political Participation in the Southern Cone}. Presentation delivered at the VI Latin American Congress of Public Opinion, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2014). {\itshape Chilean Elections 2013: Incumbency, Campaign Spending, and Electoral Success in the Congress}. Presentation delivered at the Research Colloquium of the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Digital Independent Media in Chile}. Presentation delivered at the Seminar of Mass Media Pluralism in Chile, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape The Governmental Political Elite in Chile}. Presentation delivered at the Seminar of Elites Studies in Chile, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Regional Barometer 2013: Regional Public Opinion in Bio-Bio, Los Lagos, and Los Rios}. Presentation delivered at the VI Chilean Congress of Public Administration, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Online Social Networks and Political Behaviour in Chile: Twitter as a Measure of Public Opinion During the Primary Presidential Elections in 2013}. Presentation delivered at the II International Congress of Political Communication, Toluca, Mexico.}\vspace{1mm}

\item{\small Chávez, D., \& González-Bustamante, B. (2013). {\itshape Partisanship Identification and Disaffection in Ecuador}. Presentation delivered at the XXIX Latin American Congress of Sociology, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Soto, D. (2013). {\itshape Digital Independent Media in Chile: Democratisation in the Media System?} Presentation delivered at the VII Latin American Congress of Political Science, Bogota, Colombia.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Trajectories and Patterns of the Ministers' Political Careers in Chile}. Presentation delivered at the XI Argentinian Congress of Political Science, Parana, Argentina.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Twitter as Public Opinion Measure: The Bachelet's Arrival to the Chilean Presidential Campaign 2013}. Presentation delivered at the XI Argentinian Congress of Political Science, Parana, Argentina.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Valenzuela, P. (2012). {\itshape Representation Gaps and Incorporated Capital: The Case of the Concertacion's Political Youths}. Presentation delivered at the VII Chilean Congress of Sociology, Pucon, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2012) {\itshape The Transversal Political Party Thesis: Beyond the Myth}. Presentation delivered at the X Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Chávez, D. (2012). {\itshape Bolivian Inter-Cultural Democracy: Advances and Challenges}. Presentation delivered at the X Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2012). {\itshape Lights and Shadows of the Public Management Professionalisation in the Chilean Case}. Presentation delivered at the XXII World Congress of Political Science, Madrid, Spain.}\vspace{1mm}

\item{\small Ríos, T. E., \& González-Bustamante, B. (2012). {\itshape Media System and Democratisation in the Chilean Case}. Presentation delivered at the XXII World Congress of Political Science, Madrid, Spain.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Henríquez, G. (2012). {\itshape The Role of the Online Social Networks in the Last Chilean Presidential Campaign}. Presentation delivered at the I International Congress of Political Communication, Madrid, Spain.}\vspace{1mm}

\item{\small González-Bustamante, B. (2012). {\itshape Research Notes and Reflections on the Study of Elites in Chile}. Presentation delivered at the VI Latin American Congress of Political Science, Quito, Ecuador.}

\end{benumerate}

\end{publications}

### 2021-11-24 spanish/sections/awards.tex
Update awards.tex

@@
 \cvhonor
-{Beca de Libros y de Viaje St Hilda's College en la Universidad de Oxford} 
-{Asignaciones para libros y participación en conferencias (la subvención para viajes se rechazó por la pandemia de coronavirus), USD{\$} 970} 
-{Oxford, RU}
+{Beca de Viaje de St Hilda's College} 
+{Asignaciones participación en conferencia en Estados Unidos, {\pounds} 950} 
+{Oxford, UK}
+{2022}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
+{Fondo Muriel Wise y Beca de Libros de St Hilda's College} 
+{Beca de investigación para el entrenamiento de algoritmos de aprendizaje automático, almacenamiento de datos del proyecto DPhil (PhD) y
+asignaciones para libros, {\pounds} 530} 
+{Oxford, UK}
+{2021}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
+{Beca de Viaje y Libros de St Hilda's College} 
+{Asignaciones participación en conferencia en Portugal y libros (la subvención para viajes se rechazó por la pandemia de coronavirus), {\pounds} 745} 
+{Oxford, UK}
 {2020}
@@
 {Beca Doctorado en el Extranjero Becas Chile} 
-{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), USD{\$} 210.000}
-{Oxford, RU}
+{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
+{Oxford, UK}
 {2019}
@@
 {Beca de Viaje LASA} 
-{Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), USD{\$} 520}
-{Nueva York, EUA}
+{Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), {\pounds} 400}
+{Nueva York, USA}
 {2016}
@@
 {Beca Escuela de Verano CESS}
-{Apoyo financiero para participar en la Escuela de Verano en Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), USD{\$} 260}
+{Apoyo financiero para participar en la Escuela de Verano en Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
 {Santiago, Chile}
@@
 {Beca Escuela de Invierno ACCP}
-{Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgada por la Asociación Chilena de Ciencia Política (ACCP), USD{\$} 400}
-{Montevideo, Uruguay}
+{Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgada por la Asociación Chilena de Ciencia Política (ACCP), {\pounds} 300}
+{Montevideo, URY}
 { 2015}
@@
 {Beca Escuela de Verano PUC}
-{Apoyo financiero para participar en la Escuela de Verano en Métodos Mixtos en la Pontifica Universidad Cat\'olica de Chile (PUC), USD{\$} 230}
+{Apoyo financiero para participar en la Escuela de Verano en Métodos Mixtos en la Pontifica Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
 {Santiago, Chile}
@@
 {Premio Comunicracia}
-{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares), USD{\$} 230}
+{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares), {\pounds} 170}
 {Paraná, Argentina}
@@
 {Beca para investigación de Mag\'ister FONDECYT}
-{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), USD{\$} 1,500}
+{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
 {Santiago, Chile}

### 2021-11-24 sections/experience.tex
Update experience.tex

@@
 {2019 - on leave}
-{Management and Public Policies Department, Faculty of Administration and Economics}\vspace{1.5mm}
+{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
 

### 2021-11-25 sections/awards.tex
Update awards.tex

@@
 {St Hilda's College Travel and Book Grants} 
-{Allowances for conference participation in Portugal and books (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
+{Allowances for conference participation in Portugal and books, {\pounds} 745} 
 {Oxford, UK}
@@
 {FONDECYT Thesis Writing Grant}
-{Financial support for MA field work (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
+{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
 {Santiago, Chile}

### 2021-11-25 spanish/sections/awards.tex
Update awards.tex

@@
 {Beca de Viaje y Libros de St Hilda's College} 
-{Asignaciones participación en conferencia en Portugal y libros (la subvención para viajes se rechazó por la pandemia de coronavirus), {\pounds} 745} 
+{Asignaciones participación en conferencia en Portugal y libros, {\pounds} 745} 
 {Oxford, UK}

### 2021-11-25 sections/papers.tex
Update papers.tex

--- 2020-09-11 sections/papers.tex
@@
 Evolution and Early Government Responses to COVID-19 in South America.
-{\itshape World Development, 137}.
-{\footnotesize \scshape [{\bfseries 3.869} 2019-JIF, {\bfseries Q1} Economics]}.
+{\itshape World Development, 137}, 105180.
 {\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2020).
+The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
+{\itshape Bulletin of Latin American Research, 39}(5), 582--597.
+{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
 
@@
 {\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.222} 2019-JIF, {\bfseries Q4} Public Administration]}.
+{\footnotesize \scshape [in Spanish]}.
 {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2019).
-The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition.
-{\itshape Bulletin of Latin American Research}.
-Early View.
-{\footnotesize \scshape [{\bfseries 0.586} 2019-JIF, {\bfseries Q3} Area Studies]}.
-{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
 
@@
 {\itshape Convergencia.
-Revista de Ciencias Sociales}, (80), 1--27.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.704} 2019-JIF, {\bfseries Q4} Sociology]}.
-\\ {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-{\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+Revista de Ciencias Sociales}, 80, 1--27.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape url}:  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
 
@@
 {\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
-{\footnotesize \scshape [in Spanish, {\bfseries 0.714} 2019-JIF, {\bfseries Q4} Political Science]}.
+{\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
+
 \end{benumerate}
@@
 Digital Campaigns: Branding or Political Participation?
-{\itshape M\'as Poder Local,} (12), 32--39.
+{\itshape M\'as Poder Local,} 12, 32--39.
 {\footnotesize \scshape [in Spanish]}.
 {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+
 \end{benumerate}

### 2021-11-25 spanish/sections/papers.tex
Update papers.tex

@@
 
-\cvsection{Publicaciones revisadas por pares}
+\cvsection{Artículos revisados por pares}
 
@@
 Revista de Ciencias Sociales}, 80, 1--27.
-{\scshape url}: \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.\\ {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
-
-%% \item{\small Gonz\'alez-Bustamante, B.
-(2019).
-Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
-{\itshape Convergencia.
-Revista de Ciencias Sociales}, (80), 1--27.
 {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-\\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+\\ {\scshape url}: \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
 

### 2021-11-25 spanish/sections/summary.tex
Update summary.tex

@@
 Antes de comenzar mis estudios doctorales, en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
-Además, fui profesor en la Universidad de Chile y consultor para el Programa de las Naciones Unidas para el Desarrollo (PNUD).
+Además, me desempeñé como profesor en la Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
 
@@
 Mi estrategia empírica emplea métodos de puntuación de propensión y emparejamiento, modelos de riesgos competitivos y modelos de variables instrumentales.
-Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile.
+Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile y St Hilda's College.
 \vspace{1mm}

### 2021-11-25 sections/languages.tex
Update languages.tex

@@
 {Programming \&} 
-{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}
+{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}
 
@@
 {Software} 
-{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}
-
-\cvskill
-{} 
-{{\scshape css}, {\scshape xhtml}} \\
+{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}} \\
 

### 2021-11-25 spanish/sections/languages.tex
Update languages.tex

@@
 {Programación \&} 
-{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}
+{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}
 
@@
 {software} 
-{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}
-
-\cvskill
-{} 
-{{\scshape css}, {\scshape xhtml}} \\
+{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}} \\
 

### 2021-11-25 sections/conferences-full.tex
Update conferences-full.tex

@@
 {\itshape Methodological Challenges and Innovations in the Study of Elites}.
-Presentation XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences, Virtual.}\vspace{1mm}
+Presentation delivered at the XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences, Virtual.}\vspace{1mm}
 
@@
 (2021).
-{\itshape R Applications in Social Sciences: Data Mining and Economic Modelling}.
+{\itshape R Applications in Social Sciences: Data Mining and Econometric Modelling}.
 Presentation delivered at the Political Science Method Lecture at the Universidad de Chile, Virtual.}\vspace{1mm}
@@
 {\itshape Data Mining, Modelling and Machine Learning Applications for Social Sciences}.
-Presentation delivered at the I Workshop of the Training Data Lab, Virtual.}\vspace{1mm}
+Presentation delivered at the I Training Data Lab Workshop, Virtual.}\vspace{1mm}
 
@@
 (2020).
-{\itshape Evolution and early governmental responses to COVID-19 in South America}.
+{\itshape Evolution and Early Governmental Responses to COVID-19 in South America}.
 Presentation delivered at the Workshop of the School of Political Science and Public Administration at the Universidad de Talca, Virtual.}\vspace{1mm}
@@
 {\itshape New Approaches to Studying Political Elites}.
-Presentation delivered at the Colloquium of the Observatório de Elites, Universidade Federal do Paraná, Virtual.}\vspace{1mm}
+Presentation delivered at the Colloquium of the Observatório de Elites at the Universidade Federal do Paraná, Virtual.}\vspace{1mm}
 
@@
 {\itshape Protest and Social Unrest in Latin America: Determinants and Critical Junctures}.
-Presentation delivered at the Seminar Cycle on Human Rights in Latin America, Virtual.}\vspace{1mm} %% Sergipe, Brazil
+Presentation delivered at the Seminar Cycle on Human Rights in Latin America at the Universidade Tiradentes, Virtual.}\vspace{1mm} %% Sergipe, Brazil
 
@@
 {\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}.
-Presentation delivered at the PRS Workshop Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}
+Presentation delivered at the PRS DPhil in Politics Workshop in Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}
 
@@
 {\itshape Cabinet Stability and Turnover from a Multilevel Approach}.
-Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Social Network Analysis: Application for Elites Study}.
-Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Geospatial Analysis of Partisanship Density and Electoral Turnout: Evidence from the Chilean Case}.
-Presentation delivered at the XIII Chilean Congress of Political Science, Santiago, González.}\vspace{1mm}
+Presentation delivered at the XIII Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Survival of Ministers and Vice-Ministers in Chile: Stability and Turnover from a Multilevel Approach}.
-Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics, Curitiba, Brazil.}\vspace{1mm}
+Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics at the Universidade Federal do Paraná, Curitiba, Brazil.}\vspace{1mm}
 
@@
 {\itshape Media Pluralism and Digital Media Public Opinion}.
-Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile at the Universidad Alberto Hurtado, Santiago, Chile.}\vspace{1mm}
 
@@
 Analysis of Public-Private Circulation in Chile}.
-Presentation delivered at the II Foreign Affairs Meeting, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the II Foreign Affairs Meeting at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Gaps and Elite-Mass Congruence in Chile and Uruguay}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Family Ties in the Senate and the Chamber of Deputies, Chile from 1989 to 2014}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Analysis of the Academic Production on Open Government in Spanish}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Revolving Door and Public-Private Circulation in Chile}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Production Patterns of the Contemporary Knowledge in Social Sciences}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, González.}\vspace{1mm}
+Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
 
@@
 {\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}.
-Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times at the Universidad Bernardo O'Higgins, Santiago, Chile.}\vspace{1mm}
 
@@
 {\itshape Survival of Ministers and Undersecretaries in Chile (1990-2014)}.
-Presentation delivered at the International Congress of Elites and Leadership, Salamanca, Spain.}\vspace{1mm}
+Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
 
@@
 {\itshape Elites and Political Reforms: The Chilean Case}.
-Presentation delivered at the International Congress of Elites and Leadership, Salamanca, Spain.}\vspace{1mm}
+Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
 
@@
 {\itshape Chilean Elections 2013: Incumbency, Campaign Spending, and Electoral Success in the Congress}.
-Presentation delivered at the Research Colloquium of the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Centre for Political Analysis and Research Colloquium, Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B. (2013). {\itshape Digital Independent Media in Chile}. Presentation delivered at the Seminar of Mass Media Pluralism in Chile, Santiago, Chile.}\vspace{1mm}
+\item{\small González-Bustamante, B.
+(2013).
+{\itshape Digital Independent Media in Chile}.
+Presentation delivered at the Seminar of Mass Media Pluralism in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B. (2013). {\itshape The Governmental Political Elite in Chile}. Presentation delivered at the Seminar of Elites Studies in Chile, Santiago, Chile.}\vspace{1mm}
+\item{\small González-Bustamante, B.
+(2013).
+{\itshape The Governmental Political Elite in Chile}.
+Presentation delivered at the Seminar of Elites Studies in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
 

### 2021-11-25 spanish/sections/teaching.tex
Update teaching.tex

@@
 
-\cvsection{Experiencia en docencia relevante}
+\cvsection{Experiencia docente relevante}
 
@@
 \begin{itemize}
-\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, RU}
+\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, UK}
 \begin{itemize}
@@
 \item[$\circ$]{\small Metodología de la Investigación (curso de pregrado), primavera 2014-2015, otoño 2015-2017}
-\item[$\circ$]{\small Introducción a los Métodos Cuantitativos (curso de pregrado), otoño 2017}
+%% \item[$\circ$]{\small Introducción a los Métodos Cuantitativos (curso de pregrado), otoño 2017}
 \end{itemize}

### 2022-01-03 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 
-\cvsection{Capítulos en libros editados}
+\cvsection{Capítulos de libros}
 
@@
 
-\begin{benumerate}{12}
+\begin{benumerate}{13}
+\item{\small González-Bustamante.
+B.
+({\itshape próximamente}).
+Métodos cuantitativos y mixtos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
+In F.
+Robles, I.
+Nercesián \& M.
+Serna (eds.), {\itshape Elites económicas, Estado y dominación en América Latina: Cambios y continuidades en la época post COVID}.
+Buenos Aires: Siglo XXI Editores.}\vspace{1mm}
+
 \item{\small Gonz\'alez-Bustamante, B.
@@
 Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras posibilidades de Comprensi\'on e Investigaci\'on}.
-Santiago: Social-Ediciones.}\vspace{1mm}
+Santiago: Social-Ediciones.
+{\scshape doi}: \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}}\vspace{1mm}
 

### 2022-01-03 spanish/sections/papers.tex
Update papers.tex

@@
 
-\begin{benumerate}{5}
+\begin{benumerate}{6}
+
+\item{\small Cuevas, C.
+{\itshape et al.} ({\itshape próximamente}).
+Motivación de servicio público entre funcionarios públicos chilenos.
+{\itshape Revista del CLAD Reforma y Democracia}, 80.}\vspace{1mm}
 
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
+({\itshape próximamente}).
+Élites políticas en América Latina: Socialización, trayectorias y capitales.
+Introducción.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.}\vspace{1mm}
 
@@
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}} \vspace{1mm}
+
+%% \item{\small Gonz\'alez-Bustamante, B.
+(2013).
+Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
 {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}

### 2022-01-03 sections/papers.tex
Update papers.tex

@@
 
-\begin{benumerate}{5}
+\begin{benumerate}{6}
+
+\item{\small Cuevas, C.
+{\itshape et al.} ({\itshape forthcoming}).
+Public Service Motivation Among Chilean Public Employees.
+{\itshape Revista del CLAD Reforma y Democracia}, 80.
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
 
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
+\item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
+({\itshape forthcoming}).
+Political Elites in Latin America: Socialisation, Trajectories, and Capitals.
+Introduction.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+
 \item{\small Gonz\'alez-Bustamante, B.
@@
 {\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}} \vspace{1mm}
+
+%% \item{\small Gonz\'alez-Bustamante, B.
+(2013).
+Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+{\footnotesize \scshape [in Spanish]}.
 \\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}

### 2022-01-03 sections/working-papers.tex
Update working-papers.tex

@@
 
-\cvsection{Working Papers}
+\cvsection{Working Papers and Reviews}
 
@@
 
-\begin{benumerate}{5}
-
+\begin{benumerate}{6}
 \item{\small Gonz\'alez-Bustamante, B.
-(2021, {\itshape forthcoming}).
+(2021).
 Sophistication, Participation, and Political Engagement in Latin America.
-{\itshape Tufte Working Papers}, 2.
+{\itshape Tufte Working Papers}, 2, 1--21.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}
+{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Portuguese]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}
+{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2015).
+Programas de Naciones Unidas para el Desarrollo (PNUD).
+(2014).
+Ciudadanía Política: Voz y Participación Ciudadana en América Latina.
+Buenos Aires: Siglo Veintiuno Editores.
+{\itshape Revista de Gestión Pública, IV}(1), 143--149.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}}
 \end{benumerate}

### 2022-01-03 spanish/sections/working-papers.tex
Update working-papers.tex

@@
 
-\cvsection{Documentos de trabajo}
+\cvsection{Documentos de trabajo y reseñas}
 
@@
 
-\begin{benumerate}{5}
+\begin{benumerate}{6}
 
 \item{\small Gonz\'alez-Bustamante, B.
-(2021, {\itshape próximamente}).
+(2021).
 Sofisticación, participación y compromiso político en América Latina.
-{\itshape Tufte Working Papers}, 2.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}} \vspace{1mm}
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
 
@@
 {\itshape Tufte Working Papers}, 1, 1--15.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
 
@@
 {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
-\\ {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}
+\\ {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}}\vspace{1mm}
 
@@
 NUSP/UFPR, 3}(5), 1--19.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+\\ {\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}
+{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2015).
+Programas de Naciones Unidas para el Desarrollo (PNUD).
+(2014).
+Ciudadanía Política: Voz y Participación Ciudadana en América Latina.
+Buenos Aires: Siglo Veintiuno Editores.
+{\itshape Revista de Gestión Pública, IV}(1), 143--149.
+{\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}}
+
 \end{benumerate}

### 2022-01-03 sections/book-chapters.tex
Update book-chapters.tex

@@
 
-\cvsection{Peer-Reviewed Book Chapters}
+\cvsection{Book Chapters}
 
@@
 
-\begin{benumerate}{12}
+\begin{benumerate}{13}
+
+\item{\small González-Bustamante.
+B.
+({\itshape forthcoming}).
+Quantitative and Mixed Methods for Studying Elites: Practical Applications, Biases and Potential.
+In F.
+Robles, I.
+Nercesián \& M.
+Serna (eds.), {\itshape Elites económicas, Estado y dominación en América Latina: Cambios y continuidades en la época post COVID}.
+Buenos Aires: Siglo XXI Editores.
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+
 \item{\small Gonz\'alez-Bustamante, B.
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.} \vspace{1mm}
+{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
 
@@
 San Jose: Fundación Educativa San Judas Tadeo.
-{\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 Santiago: Instituto Igualdad.
-{\footnotesize \scshape [in Spanish]}.} \vspace{1mm}
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
 
@@
 Buenos Aires: Editorial Biblos.
-{\footnotesize \scshape [in Spanish].}} \vspace{1mm}
+{\footnotesize \scshape [in Spanish].}}\vspace{1mm}
+
 \end{benumerate}

### 2022-01-03 sections/papers.tex
Update papers.tex

@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}} \vspace{1mm}
-
-%% \item{\small Gonz\'alez-Bustamante, B.
-(2013).
-Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}.
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 

### 2022-01-03 spanish/sections/editor.tex
Update editor.tex

@@
 \begin{benumerate}{2}
-\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. {\itshape Pleyade}.}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
+({\itshape próximamente}).
+Political Elites in Latin America: Socialisation, Trajectories, and Capitals.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.}\vspace{1mm}
 
@@
 (2016).
-Political, Economic, and Intellectual Elites.
+Élites políticas, económicas e intelectuales.
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1).
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+
 \end{benumerate}

### 2022-01-03 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 \begin{benumerate}{13}
+
 \item{\small González-Bustamante.
@@
 Curitiba: Editora da Universidade Federal do Paraná.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 Ciudad de México: INFOTEC.
-{\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [2da edición]}.} \vspace{1mm}
+{\footnotesize \scshape [2da edición]}.}\vspace{1mm}
 
@@
 Sibaja (ed.), {\itshape Nuevos Medios y Comunicaci\'on Pol\'itica Digital}.
-San José: Fundación Educativa San Judas Tadeo.} \vspace{1mm}
+San José: Fundación Educativa San Judas Tadeo.}\vspace{1mm}
 
@@
 Santiago: Fundación Democracia y Desarrollo.
-{\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica Pol\'itica y Medios Digitales}.
-Santiago: Instituto Igualdad.} \vspace{1mm}
+Santiago: Instituto Igualdad.}\vspace{1mm}
 
@@
 del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}.
-Buenos Aires: Editorial Biblos.} \vspace{1mm}
+Buenos Aires: Editorial Biblos.}\vspace{1mm}
+
 \end{benumerate}

### 2022-01-03 sections/papers.tex
Update papers.tex

@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
+{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
+\\ {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
 

### 2022-03-02 sections/papers.tex
Update papers.tex

@@
 
-\begin{benumerate}{6}
+\begin{benumerate}{7}
+
+\item{Orchard, X., \& González-Bustamante, B.
+({\itshape forthcoming}).
+Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
+{\itshape The International Journal of Press/Politics}.}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}
+\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}\pagebreak
 

### 2022-03-02 sections/teaching.tex
Update teaching.tex

@@
 
-\begin{cventries}
+\begin{publications}
 
 \begin{itemize}
+\item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, Chile}
+\begin{itemize}
+\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), Spring 2021}
+\end{itemize}
 \item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
@@
 \end{itemize}
-\item{\small Faculty of Economics and Management, {\bfseries Universidad de Santiago}, Santiago, Chile}
+\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, Chile}
 \begin{itemize}

### 2022-03-02 spanish/sections/papers.tex
Update papers.tex

--- 2021-11-25 spanish/sections/papers.tex
@@
 
-\begin{benumerate}{5}
+\begin{benumerate}{7}
+
+\item{Orchard, X., \& González-Bustamante, B.
+({\itshape próximamente}).
+Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
+{\itshape The International Journal of Press/Politics}.}
+
+\item{\small Cuevas, C.
+{\itshape et al.} ({\itshape próximamente}).
+Motivación de servicio público entre funcionarios públicos chilenos.
+{\itshape Revista del CLAD Reforma y Democracia}, 80.}\vspace{1mm}
 
@@
 (2018).
-Agenda política, periodismo y medios digitales en Chile.
-Notas de investigación sobre pluralismo informativo.
+Agenda política, periodismo y medios digitales en Chile: Notas de investigación sobre pluralismo informativo.
 {\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
@@
 \end{publications}
+\pagebreak
 
@@
 {\itshape Revista de Sociolog\'ia,} 29, 37--54.
+{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
 {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
@@
 {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
 {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}

### 2022-03-10 sections/papers.tex
Update papers.tex

@@
 {\itshape Revista del CLAD Reforma y Democracia}, 80.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+{\footnotesize \scshape [in Spanish]}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}
 
@@
 Introduction.
-{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
 

### 2022-03-10 sections/teaching.tex
Update teaching.tex

@@
 \begin{itemize}
-\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), Spring 2021}
+\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021}
 \end{itemize}
@@
 \begin{itemize}
-\item[$\circ$]{\small Political Science I (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
-\item[$\circ$]{\small Political Science II (undergraduate lecture), Spring 2015-2018}
-\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), Fall 2018}
-\item[$\circ$]{\small Workshop for Research Design (graduate seminar), Spring 2017-2018}
-\item[$\circ$]{\small Research Methodology (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
-\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), Fall 2017}
+\item[$\circ$]{\small Political Science I (undergraduate lecture), spring 2014, 2018, fall 2015-2019}
+\item[$\circ$]{\small Political Science II (undergraduate lecture), spring 2015-2018}
+\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), fall 2018}
+\item[$\circ$]{\small Workshop for Research Design (graduate seminar), spring 2017-2018}
+\item[$\circ$]{\small Research Methodology (undergraduate lecture), spring 2014-2015, fall 2015-2017}
+\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), fall 2017}
 \end{itemize}
@@
 \begin{itemize}
-\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), Fall 2016}
-\item[$\circ$]{\small Political Analysis (undergraduate lecture), Fall 2014}
-\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
+\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), fall 2016}
+\item[$\circ$]{\small Political Analysis (undergraduate lecture), fall 2014}
+\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014}
 \end{itemize}

### 2022-03-10 sections/reviewer.tex
Update reviewer.tex

@@
 \item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, 
-Netherlands, 2018-2019}
-\item{\small Reviewer in {\scshape WoS} \& {\scshape Scopus} journals, since 2013}
+Netherlands, 2018-2019, 2022}
+\item{\small Reviewer in {\scshape WoS-ISI/SSCI/ESCI} \& {\scshape Scopus} journals, since 2013}
 \item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, since 2013}

### 2022-03-10 spanish/sections/summary.tex
Update summary.tex

@@
 Actualmente me encuentro establecido en Oxford, trabajando en mi investigación.
-Además, soy Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago de Chile.
+Además, soy Profesor Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago de Chile.
 

### 2022-03-10 spanish/sections/reviewer.tex
Update reviewer.tex

@@
 \item{\small Comisión Sectorial de Investigación, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
-\item{\small Times Higher Education Ranking, {\scshape Elsevier}, 
-Países Bajos, 2018-2019}
-\item{\small Revisor en revistas {\scshape WoS} \& {\scshape Scopus}, desde 2013}
+\item{\small Times Higher Education Ranking, {\scshape Elsevier}, Países Bajos, 2018-2019, 2022}
+\item{\small Revisor en revistas {\scshape WoS-ISI/SSCI/ESCI} \& {\scshape Scopus}, desde 2013}
 \item{\small Revisor en revistas {\scshape SciELO} \& {\scshape Latindex}, desde 2013}

### 2022-03-10 spanish/sections/papers.tex
Update papers.tex

@@
 Motivación de servicio público entre funcionarios públicos chilenos.
-{\itshape Revista del CLAD Reforma y Democracia}, 80.}\vspace{1mm}
+{\itshape Revista del CLAD Reforma y Democracia}, 80.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}
 
@@
 Introducción.
-{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.}\vspace{1mm}
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+\\ {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
 

### 2022-03-10 spanish/sections/editor.tex
Update editor.tex

@@
 ({\itshape próximamente}).
-Political Elites in Latin America: Socialisation, Trajectories, and Capitals.
-{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.}\vspace{1mm}
+Élites políticas en América Latina: Socialización, trayectorias y capitales.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.}\vspace{1mm}
 

### 2022-04-08 spanish/sections/working-papers.tex
Update working-papers.tex

@@
 
+\cvsection{Data Collection Projects}
+
+\begin{publications}
+
+\begin{benumerate}{2}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2022).
+Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}}\vspace{1mm}
+
+\item{Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2022).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}}\vspace{1mm}
+
+\end{benumerate}
+
+\end{publications}
+
 \cvsection{Documentos de trabajo y reseñas}
@@
 
-\begin{benumerate}{6}
-
-\item{\small Gonz\'alez-Bustamante, B.
-(2021).
-Sofisticación, participación y compromiso político en América Latina.
-{\itshape Tufte Working Papers}, 2, 1--21.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
-(2020).
-Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continúo, para el estudio de las élites.
-{\itshape Tufte Working Papers}, 1, 1--15.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
+\begin{benumerate}{4}
 
@@
 {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}\vspace{1mm}
+{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}}\vspace{1mm}
 

### 2022-04-08 sections/papers.tex
Update papers.tex

@@
 \item{Orchard, X., \& González-Bustamante, B.
-({\itshape forthcoming}).
+(2022).
 Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
-{\itshape The International Journal of Press/Politics}.}
+{\itshape The International Journal of Press/Politics}.
+Online First.
+{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}}\vspace{1mm}
 
@@
 
-\begin{benumerate}{10}
+\begin{benumerate}{12}
 \item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
@@
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2021).
+Sophistication, Participation, and Political Engagement in Latin America.
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
+(2020).
+Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study.
+{\itshape Tufte Working Papers}, 1, 1--15.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
 

### 2022-04-08 sections/working-papers.tex
Update working-papers.tex

@@
 
+\cvsection{Data Collection Projects}
+
+\begin{publications}
+
+\begin{benumerate}{2}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2022).
+Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}}\vspace{1mm}
+
+\item{Gonz\'alez-Bustamante, B., \& Olivares, A.
+(2022).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}}\vspace{1mm}
+
+\end{benumerate}
+
+\end{publications}
+
 \cvsection{Working Papers and Reviews}
@@
 
-\begin{benumerate}{6}
-\item{\small Gonz\'alez-Bustamante, B.
-(2021).
-Sophistication, Participation, and Political Engagement in Latin America.
-{\itshape Tufte Working Papers}, 2, 1--21.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
-(2020).
-Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study.
-{\itshape Tufte Working Papers}, 1, 1--15.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
+\begin{benumerate}{4}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}\vspace{1mm}
+{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}}
+{\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}}\vspace{1mm}
+
 \end{benumerate}

### 2022-04-08 spanish/sections/papers.tex
Update papers.tex

@@
 \item{Orchard, X., \& González-Bustamante, B.
-({\itshape próximamente}).
+(2022).
 Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
-{\itshape The International Journal of Press/Politics}.}
+{\itshape The International Journal of Press/Politics}.
+Online First.
+{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}}
 
@@
 
-\begin{benumerate}{10}
+\begin{benumerate}{12}
 
@@
 \\ {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B.
+(2021).
+Sofisticación, participación y compromiso político en América Latina.
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
+
+\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
+(2020).
+Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continúo, para el estudio de las élites.
+{\itshape Tufte Working Papers}, 1, 1--15.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
 

### 2022-04-27 sections/papers.tex
LPPL v1.3c
Update papers.tex

@@
 
-%% Creative Commons Attribution 4.0 International License
+%% LaTeX Project Public License v1.3c
 %% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md
@@
 
-\begin{benumerate}{7}
+\begin{benumerate}{8}
+
+\item{Fleming, T., González-Bustamante, B., \& Schleiter, P.
+(2022, {\itshape forthcoming}).
+Cabinet Reshuffles and Parliamentary No-Confidence Motions.
+{\itshape Government and Opposition}.}\vspace{1mm}
 
@@
 \item{\small Cuevas, C.
-{\itshape et al.} ({\itshape forthcoming}).
+{\itshape et al.} (2021, {\itshape forthcoming}).
 Public Service Motivation Among Chilean Public Employees.
@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}\pagebreak
+\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}
 
@@
 \item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
-({\itshape forthcoming}).
+(2021, {\itshape forthcoming}).
 Political Elites in Latin America: Socialisation, Trajectories, and Capitals.

### 2022-04-27 sections/summary.tex
Update summary.tex
LPPL v1.3c

@@
 
-%% Creative Commons Attribution 4.0 International License
-%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt
+%% LaTeX Project Public License v1.3c
+%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md
 
@@
 I am currently based in Oxford, working on my research.
-Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile.
+Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile (USACH).
 
@@
 In my DPhil project, I combine the principal-agent theory elements to evaluate the actors’ incentives and strategies in presidential systems.
-My empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations.
-My research is funded by the Chilean National Agency for Research and Development.
+My data gathering strategy is based on archives revision using Optical Character Recognition (OCR), Natural Language Processing (NLP), and machine learning techniques.
+In addition, my empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations.
+
+My research is funded by the Chilean National Agency for Research and Development and the St Hilda’s College Muriel Wise Fund.
 \vspace{1mm}

### 2022-04-27 spanish/sections/summary.tex
LPPL v1.3c
Update summary.tex

--- 2021-11-25 spanish/sections/summary.tex
@@
 Actualmente me encuentro establecido en Oxford, trabajando en mi investigación.
-Además, soy Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago de Chile.
+Además, soy Profesor Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago de Chile (USACH).
 
@@
 En mi proyecto doctoral combino elementos de la teoría principal-agente para evaluar los incentivos y estrategias de los actores en los sistemas presidenciales.
-Mi estrategia empírica emplea métodos de puntuación de propensión y emparejamiento, modelos de riesgos competitivos y modelos de variables instrumentales.
-Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile y St Hilda's College.
+Mi estrategia de recopilación de datos se basa en la revisión de archivos mediante reconocimiento óptico de caracteres (OCR), procesamiento del lenguaje natural (NLP) y técnicas de aprendizaje automático.
+Además, mi estrategia empírica emplea métodos de puntuación de propensión y emparejamiento, modelos de riesgos competitivos y modelos de variables instrumentales.
+
+Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile y St Hilda's College Muriel Wise Fund.
 \vspace{1mm}

### 2022-05-22 sections/conferences-full.tex
Update conferences-full.tex
LPPL v1.3c

@@
 
-\begin{benumerate}{66}
+\begin{benumerate}{68}
+
+\item{\small González-Bustamante, B., \& Aguilar, D.
+(2022).
+{\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Municipalities}.
+Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}
 
@@
 (2022).
-{\itshape Resignation Calls and Dismissals of Ministers in Latin America}.
-Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, San Francisco, USA.}\vspace{1mm}
+{\itshape Resignation Calls and Dismissals of Ministers in Latin America: ata Gathering using NLP and Machine Learning}.
+Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
 
@@
 (2022).
-{\itshape Resignation Calls and Ministerial Turnover in Latin America}.
+{\itshape Insights of a Number of Ongoing Research on Elites in Latin America: Topics, Methods and Possibilities for Comparison}.
+Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2022).
+{\itshape Resignation Calls and Ministerial Turnover in Latin America: Notes on Data Gathering using Machine Learning}.
 Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}

### 2022-05-22 sections/papers.tex
Update papers.tex

@@
 
-\item{Fleming, T., González-Bustamante, B., \& Schleiter, P.
+\item{Fleming, T.
+G., González-Bustamante, B., \& Schleiter, P.
 (2022, {\itshape forthcoming}).
@@
 
-\begin{benumerate}{8}
+\begin{benumerate}{9}
+
+\item{\small Cisternas, C., \& González-Bustamante, B.
+(2022, {\itshape forthcoming}).
+Social Sciences in Repression Contexts: Bibliometric Analysis of the Historical Production of the Corporación de Estudios para Latinoamérica (1979-1989).
+{\itshape e-Ciencias de la Información}.
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
 
@@
 \begin{benumerate}{12}
+
 \item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
-(2021, {\itshape forthcoming}).
+(2021).
 Political Elites in Latin America: Socialisation, Trajectories, and Capitals.
-Introduction.
-{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28, 21--32.
 {\footnotesize \scshape [in Spanish]}.
+\\ {\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}

### 2022-05-22 spanish/sections/papers.tex
LPPL v1.3c
Update papers.tex

@@
 
-\begin{benumerate}{7}
+\begin{benumerate}{8}
+
+\item{Fleming, T.
+G., González-Bustamante, B., \& Schleiter, P.
+(2022, {\itshape próximamente}).
+Cabinet Reshuffles and Parliamentary No-Confidence Motions.
+{\itshape Government and Opposition}.}\vspace{1mm}
 
@@
 \item{\small Cuevas, C.
-{\itshape et al.} ({\itshape próximamente}).
+{\itshape et al.} (2021, {\itshape próximamente}).
 Motivación de servicio público entre funcionarios públicos chilenos.
@@
 
-\begin{benumerate}{8}
+\begin{benumerate}{9}
+
+\item{\small Cisternas, C., \& González-Bustamante, B.
+(2022, {\itshape próximamente}).
+Ciencias sociales en contextos de represión: Análisis bibliométrico de la producción histórica de la Corporación de Estudios para Latinoamérica (1979-1989).
+{\itshape e-Ciencias de la Información}.}\vspace{1mm}
 
@@
 \end{publications}
-\pagebreak
 
@@
 \item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
-({\itshape próximamente}).
+(2021).
 Élites políticas en América Latina: Socialización, trayectorias y capitales.
-Introducción.
 {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+21--32.
+{\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
 \\ {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
@@
 (2020).
-Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continúo, para el estudio de las élites.
+Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continuo, para el estudio de las élites.
 {\itshape Tufte Working Papers}, 1, 1--15.

### 2022-05-26 sections/conferences-full.tex
Update conferences-full.tex

@@
 
-\begin{benumerate}{68}
+\begin{benumerate}{69}
 
@@
 (2022).
-{\itshape Resignation Calls and Dismissals of Ministers in Latin America: ata Gathering using NLP and Machine Learning}.
+{\itshape Resignation Calls and Dismissals of Ministers in Latin America: Data Gathering using NLP and Machine Learning}.
 Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
@@
 
-%% Bamberg
+\item{\small Fleming, T.
+G., González-Bustamante, B., \& Schleiter, P.
+(2021).
+{\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}.
+Presentation delivered at the Otto-Friedrich-Universität Bamberg Workshop, Virtual.}\vspace{1mm}
 

### 2022-05-27 sections/conferences-full.tex
Update conferences-full.tex

@@
 
-\begin{benumerate}{69}
+\begin{benumerate}{71}
 
@@
 Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2022).
+{\itshape Ministerial Stability During Presidential Approval Crises: Evidence from Brazil and Chile}.
+Presentation delivered at the Political Studies Association Early Career Network Annual Conference, Sheffield, UK.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2022).
+{\itshape Time-Dependent Data Encoding and Time-Varying Exposure Survival Models to Study Presidential Crises}.
+Presentation delivered at the R User Conference 2022, Virtual.}\vspace{1mm}
 

### 2022-06-15 sections/conferences-full.tex
Update conferences-full.tex

@@
 
-\begin{benumerate}{71}
+\begin{benumerate}{72}
+
+%% \item{González-Bustamante, B., \& Aguilar, D.
+(2022).
+{\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Local Governments}.
+Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2022).
+{\itshape Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential}.
+Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}
 
@@
 {\itshape Time-Dependent Data Encoding and Time-Varying Exposure Survival Models to Study Presidential Crises}.
-Presentation delivered at the R User Conference 2022, Virtual.}\vspace{1mm}
+Presentation delivered at the R User Annual Conference, Virtual.}\vspace{1mm}
 
@@
 {\itshape Media Consumption and Political Participation in Argentina, Chile, and Uruguay}.
-Presentation delivered at the XII Argentinian Congress of Political Science, Mendoza, Argentina.}\vspace{1mm}
+Presentation delivered at the XII Argentine Congress of Political Science, Mendoza, Argentina.}\vspace{1mm}
 
@@
 {\itshape Trajectories and Patterns of the Ministers' Political Careers in Chile}.
-Presentation delivered at the XI Argentinian Congress of Political Science, Parana, Argentina.}\vspace{1mm}
+Presentation delivered at the XI Argentine Congress of Political Science, Parana, Argentina.}\vspace{1mm}
 
@@
 {\itshape Twitter as Public Opinion Measure: The Bachelet's Arrival to the Chilean Presidential Campaign 2013}.
-Presentation delivered at the XI Argentinian Congress of Political Science, Parana, Argentina.}\vspace{1mm}
+Presentation delivered at the XI Argentine Congress of Political Science, Parana, Argentina.}\vspace{1mm}
 

### 2022-06-15 spanish/sections/awards.tex
Update awards.tex
LPPL v1.3c

@@
 
-\cvsection{Honores \& premios}
+\cvsection{Honores \& premios relevantes}
 
@@
 \cvhonor
-{Beca de Viaje de St Hilda's College} 
-{Asignaciones participación en conferencia en Estados Unidos, {\pounds} 950} 
-{Oxford, UK}
+{Premio de investigación de postgrado y postdoctoral SLAS y beca para conferencia} 
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1,400}
+{Bath, UK}
 {2022}
@@
 \cvhonor
-{Fondo Muriel Wise y Beca de Libros de St Hilda's College} 
-{Beca de investigación para el entrenamiento de algoritmos de aprendizaje automático, almacenamiento de datos del proyecto DPhil (PhD) y
-asignaciones para libros, {\pounds} 530} 
+{Fondo Muriel Wise de St Hilda's College y beca para viajes y libros} 
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2,225} 
 {Oxford, UK}
-{2021}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{Beca de Viaje y Libros de St Hilda's College} 
-{Asignaciones participación en conferencia en Portugal y libros, {\pounds} 745} 
-{Oxford, UK}
-{2020}
+{2022}
 \end{cvhonors}
@@
 
-\begin{cvhonors}
-\cvhonor
-{Beca de Viaje LASA} 
-{Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), {\pounds} 400}
-{Nueva York, USA}
-{2016}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Beca de Viaje LASA} 
+%% {Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), {\pounds} 400}
+%% {Nueva York, USA}
+%% {2016}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
-\begin{cvhonors}
-\cvhonor
-{Beca Escuela de Verano CESS}
-{Apoyo financiero para participar en la Escuela de Verano en Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
-{Santiago, Chile}
-{2016}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Beca Escuela de Verano CESS}
+%% {Apoyo financiero para participar en la Escuela de Verano en Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
+%% {Santiago, Chile}
+%% {2016}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
@@
 
-\begin{cvhonors}
-\cvhonor
-{Beca Escuela de Invierno ACCP}
-{Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgada por la Asociación Chilena de Ciencia Política (ACCP), {\pounds} 300}
-{Montevideo, URY}
-{ 2015}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Beca Escuela de Invierno ACCP}
+%% {Apoyo financiero para participar en la Escuela de Invierno en Métodos y Análisis de Datos en la Universidad Cat\'olica de Uruguay, otorgada por la Asociación Chilena de Ciencia Política (ACCP), {\pounds} 300}
+%% {Montevideo, URY}
+%% { 2015}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
-\begin{cvhonors}
-\cvhonor
-{Beca Escuela de Verano PUC}
-{Apoyo financiero para participar en la Escuela de Verano en Métodos Mixtos en la Pontifica Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
-{Santiago, Chile}
-{2014} 
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Beca Escuela de Verano PUC}
+%% {Apoyo financiero para participar en la Escuela de Verano en Métodos Mixtos en la Pontifica Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
+%% {Santiago, Chile}
+%% {2014} 
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
@@
 {Premio Comunicracia}
-{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares), {\pounds} 170}
+{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares)} %% {\pounds} 170
 {Paraná, Argentina}
@@
 
-\begin{cvhonors}
-\cvhonor
-{Mejor calificación en tesis de Magíster}
-{La más alta calificación y las felicitaciones del jurado en la Universidad de Chile}
-{Santiago, Chile}
-{2013}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Mejor calificación en tesis de Magíster}
+%% {La más alta calificación y las felicitaciones del jurado en la Universidad de Chile}
+%% {Santiago, Chile}
+%% {2013}
+%% \end{cvhonors}
 

### 2022-06-15 sections/summary.tex
Update summary.tex

@@
 
-My research is funded by the Chilean National Agency for Research and Development and the St Hilda’s College Muriel Wise Fund.
+My research is funded by the Chilean National Agency for Research and Development, the St Hilda’s College Muriel Wise Fund and the Society for Latin American Studies Postgraduate and Postdoctoral Research Award.
 \vspace{1mm}

### 2022-06-15 sections/awards.tex
Update awards.tex
LPPL v1.3c

@@
 
-\cvsection{Honours \& Awards}
+\cvsection{Relevant Honours \& Awards}
 
@@
 \cvhonor
-{St Hilda's College Travel Grant} 
-{Allowances for conference participation in the USA, {\pounds} 950} 
-{Oxford, UK}
+{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
+{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1,400}
+{Bath, UK}
 {2022}
@@
 \cvhonor
-{St Hilda's College Muriel Wise Fund and Book Grant} 
-{Research grant for the training of machine learning algorithms, DPhil (PhD) project data storage, and allowances for books, {\pounds} 530} 
+{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
+{Research support grant for my DPhil (PhD) project and allowance for participation in conferences and purchase of books, {\pounds} 2,225} 
 {Oxford, UK}
-{2021}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{St Hilda's College Travel and Book Grants} 
-{Allowances for conference participation in Portugal and books, {\pounds} 745} 
-{Oxford, UK}
-{2020}
+{2022}
 \end{cvhonors}
@@
 
-\begin{cvhonors}
-\cvhonor
-{LASA Travel Grant} 
-{Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
-{New York, USA}
-{2016}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {LASA Travel Grant} 
+%% {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
+%% {New York, USA}
+%% {2016}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
-\begin{cvhonors}
-\cvhonor
-{CESS Summer School Scholarship}
-{Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
-{Santiago, Chile}
-{2016}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {CESS Summer School Scholarship}
+%% {Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
+%% {Santiago, Chile}
+%% {2016}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
@@
 {ALACIP Methodological School Prize}
-{Best methodological work at the Latin American Political Association School (ALACIP)}
+{Best methodological work at the Latin American Political Association (ALACIP) School}
 {Lima, Peru}
@@
 
-\begin{cvhonors}
-\cvhonor
-{ACCP Winter School Scholarship}
-{Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
-{Montevideo, URY}
-{ 2015}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {ACCP Winter School Scholarship}
+%% {Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
+%% {Montevideo, URY}
+%% { 2015}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
-\begin{cvhonors}
-\cvhonor
-{PUC Summer School Scholarship}
-{Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
-{Santiago, Chile}
-{2014} 
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {PUC Summer School Scholarship}
+%% {Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
+%% {Santiago, Chile}
+%% {2014} 
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 
@@
 {Comunicracia Prize}
-{Best paper of the political communication area at the XI Argentinian Congress of Political Science (double-blind peer-review), {\pounds} 170}
+{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review)} %% {\pounds} 170
 {Parana, Argentina}
@@
 
-\begin{cvhonors}
-\cvhonor
-{Highest Rating MA Dissertation}
-{The highest rating and the congratulations from the jury at the Universidad de Chile}
-{Santiago, Chile}
-{2013}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Highest Rating MA Dissertation}
+%% {The highest rating and the congratulations from the jury at the Universidad de Chile}
+%% {Santiago, Chile}
+%% {2013}
+%% \end{cvhonors}
 
-\vspace{1mm}
+%% \vspace{1mm}
 

### 2022-06-15 sections/awards.tex
Update awards.tex

@@
 {St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
-{Research support grant for my DPhil (PhD) project and allowance for participation in conferences and purchase of books, {\pounds} 2,225} 
+{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2,225} 
 {Oxford, UK}

### 2022-07-11 sections/awards.tex
Update awards.tex

--- 2022-06-15 sections/awards.tex
@@
 {St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
-{Research support grant for my DPhil (PhD) project and allowance for participation in conferences and purchase of books, {\pounds} 2,225} 
+{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2,255} 
 {Oxford, UK}

### 2022-07-11 sections/papers.tex
Update papers.tex

@@
 
-\begin{benumerate}{8}
+\begin{benumerate}{9}
+
+\item{González-Bustamante, B.
+(2022, {\itshape forthcoming}).
+Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
+{\itshape The British Journal of Politics and International Relations}.}\vspace{1mm}
 
@@
 \item{\small Cisternas, C., \& González-Bustamante, B.
-(2022, {\itshape forthcoming}).
-Social Sciences in Repression Contexts: Bibliometric Analysis of the Historical Production of the Corporación de Estudios para Latinoamérica (1979-1989).
-{\itshape e-Ciencias de la Información}.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+(2022).
+Social Sciences in Repression Contexts: Bibliometric Analysis of the Historical Production of the Corporación de Estudios para Latinoamérica, Chile (1979-1989).
+{\itshape e-Ciencias de la Información, 12}(2), 1--18.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}.
+\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{http://revistas.ufro.cl}}}\vspace{1mm}
+{\scshape url}: \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
@@
 {\footnotesize \scshape [in Spanish]}.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
@@
 \end{publications}
+\pagebreak

### 2022-07-11 spanish/sections/awards.tex
Update awards.tex

@@
 {Fondo Muriel Wise de St Hilda's College y beca para viajes y libros} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2,225} 
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2,255} 
 {Oxford, UK}

### 2022-07-11 spanish/sections/papers.tex
Update papers.tex

@@
 
-\begin{benumerate}{8}
+\begin{benumerate}{9}
+
+\item{González-Bustamante, B.
+(2022, {\itshape próximamente}).
+Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
+{\itshape The British Journal of Politics and International Relations}.}\vspace{1mm}
 
@@
 \item{\small Cisternas, C., \& González-Bustamante, B.
-(2022, {\itshape próximamente}).
-Ciencias sociales en contextos de represión: Análisis bibliométrico de la producción histórica de la Corporación de Estudios para Latinoamérica (1979-1989).
-{\itshape e-Ciencias de la Información}.}\vspace{1mm}
+(2022).
+Ciencias sociales en contextos de represión: Análisis bibliométrico de la producción histórica de la Corporación de Estudios para Latinoamérica, Chile (1979-1989).
+{\itshape e-Ciencias de la Información, 12}(2), 1--18.
+{\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm}
 
@@
 {\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
-{\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{http://revistas.ufro.cl}}}\vspace{1mm}
+{\scshape url}: \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}}\vspace{1mm}
 
@@
 {\itshape Tufte Working Papers}, 2, 1--21.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
@@
 {\itshape Tufte Working Papers}, 1, 1--15.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}

### 2022-07-19 sections/conferences-full.tex
Update conferences-full.tex

@@
 
-\begin{benumerate}{72}
+\begin{benumerate}{74}
 
-%% \item{González-Bustamante, B., \& Aguilar, D.
+\item{González-Bustamante, B., \& Aguilar, D.
+(2022).
+{\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}.
+Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Aguilar, D.
 (2022).

### 2022-07-27 spanish/sections/book-chapters.tex
Update book-chapters.tex
LPPL v1.3c

@@
 
-\begin{benumerate}{13}
+\begin{benumerate}{12}
 
-\item{\small González-Bustamante.
-B.
-({\itshape próximamente}).
-Métodos cuantitativos y mixtos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
-In F.
-Robles, I.
-Nercesián \& M.
-Serna (eds.), {\itshape Elites económicas, Estado y dominación en América Latina: Cambios y continuidades en la época post COVID}.
-Buenos Aires: Siglo XXI Editores.}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2018).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2018).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2018).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Barr\'ia, D.
+\item{\small González-Bustamante, B., \& Barría, D.
 (2018).
@@
 
-\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Araya, J.
+\item{\small Barría, D., González-Bustamante, B., \& Araya, J.
 E.
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2016).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D.
+\item{\small González-Bustamante, B., \& Sazo, D.
 (2016).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2014).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G.
+\item{\small González-Bustamante, B., \& Henr\'iquez, G.
 (2013).

### 2022-07-27 spanish/sections/papers.tex
Update papers.tex

@@
 G., González-Bustamante, B., \& Schleiter, P.
-(2022, {\itshape próximamente}).
+(2022).
 Cabinet Reshuffles and Parliamentary No-Confidence Motions.
-{\itshape Government and Opposition}.}\vspace{1mm}
+{\itshape Government and Opposition}.
+FirstView.
+{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}}\vspace{1mm}
 
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2021).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2020).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
+\item{\small González-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
 (2020).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2019).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L.
+\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
@@
 
-\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2019).
@@
 
-\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Cisternas, C.
+\item{\small Barr\'ia, D., González-Bustamante, B., \& Cisternas, C.
 (2019).
@@
 
-\item{\small Del Valle, N., \& Gonz\'alez-Bustamante, B.
+\item{\small Del Valle, N., \& González-Bustamante, B.
 (2018).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 {\itshape et al.} (2016).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2015).
@@
 
-\begin{benumerate}{12}
+\begin{benumerate}{13}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
+\item{\small González-Bustamante.
+B.
+(2022, {\itshape próximamente}).
+Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
+{\itshape Revista Chilena de Derecho y Ciencia Política}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Luci, F.
 (2021).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
+\item{\small González-Bustamante, B., \& Cisternas, C.
 (2020).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C.
+\item{\small González-Bustamante, B., \& Cisternas, C.
 (2016).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2015).
@@
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2013).
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G.
+\item{\small González-Bustamante, B., \& Henríquez, G.
 (2012).

### 2022-07-27 sections/papers.tex
Update papers.tex

@@
 G., González-Bustamante, B., \& Schleiter, P.
-(2022, {\itshape forthcoming}).
+(2022).
 Cabinet Reshuffles and Parliamentary No-Confidence Motions.
-{\itshape Government and Opposition}.}\vspace{1mm}
+{\itshape Government and Opposition}.
+FirstView.
+{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}}\vspace{1mm}
 
@@
 
-\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Cisternas, C.
+\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2019).
@@
 
-\begin{benumerate}{12}
+\begin{benumerate}{13}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
+\item{\small González-Bustamante.
+B.
+(2022, {\itshape forthcoming}).
+Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential.
+{\itshape Revista Chilena de Derecho y Ciencia Política}.
+{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Luci, F.
 (2021).

### 2022-09-01 spanish/sections/summary.tex
Update summary.tex

@@
 Estoy completando mi tesis doctoral en el Departamento de Ciencia Política y Relaciones Internacionales y en St Hilda’s College en la Universidad de Oxford, Reino Unido.
-Actualmente me encuentro establecido en Oxford, trabajando en mi investigación.
-Además, soy Profesor Instructor en el Departamento de Gestión y Políticas Públicas de la Facultad de Administración y Economía de la Universidad de Santiago de Chile (USACH).
-
 Antes de comenzar mis estudios doctorales, en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
-Además, me desempeñé como profesor en la Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
+Además, me desempeñé como profesor en la Universidad de Santiago y Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
 
@@
 
-Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile y St Hilda's College Muriel Wise Fund.
+Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile, St Hilda's College Muriel Wise Fund y Society for Latin American Studies Postgraduate and Postdoctoral Research Award.
 \vspace{1mm}

### 2022-09-01 sections/experience.tex
LPPL v1.3c
Update experience.tex

@@
 \cventry
-{Instructor Professor} 
+{Lecturer} 
 {Universidad de Santiago de Chile} 
 {Santiago, Chile} 
-{2019 - on leave}
-{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
-
-\cventry
-{Adjunct Professor} 
-{Universidad de Santiago de Chile} 
-{Santiago, Chile} 
-{2014 - 2018}
+{2014 - 2019}
 {Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
@@
 {School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}
-
 \end{cventries}
+\pagebreak

### 2022-09-01 sections/papers.tex
Update papers.tex

@@
 \item{\small Cuevas, C.
-{\itshape et al.} (2021, {\itshape forthcoming}).
+{\itshape et al.} (2021).
 Public Service Motivation Among Chilean Public Employees.
-{\itshape Revista del CLAD Reforma y Democracia}, 80.
+{\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
 {\footnotesize \scshape [in Spanish]}.
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}.
-\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078cr}}.
+\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
 
@@
 
-\begin{benumerate}{13}
+\begin{benumerate}{14}
 
@@
 {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2021).
+Sophistication, Participation, and Political Engagement in Latin America.
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
 
@@
 (2021).
-Sophistication, Participation, and Political Engagement in Latin America.
-{\itshape Tufte Working Papers}, 2, 1--21.
+Digital Hybridization in the Southern Cone: Consumption of Traditional and Digital Media and Use of Social Networks.
+{\itshape Comunifé}, 21, 31--39.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
+\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}}\vspace{1mm}
 
@@
 
-\item{\small González-Bustamante, B.
-(2016).
-Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
-
 \item{\small González-Bustamante, B., \& Cisternas, C.
@@
 \item{\small González-Bustamante, B.
-(2015).
-Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013.
-{\itshape Revista SAAP, 9}(1), 119--141.
+(2016).
+Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science.
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
 
@@
 \item{\small González-Bustamante, B.
-(2014).
-Popular Election of Regional Councillors 2013.
-Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
+(2015).
+Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013.
+{\itshape Revista SAAP, 9}(1), 119--141.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+\\ {\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
 
@@
 \item{\small González-Bustamante, B.
-(2013).
-Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+(2014).
+Popular Election of Regional Councillors 2013.
+Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile.
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 {\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2013).
+Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}.
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 \end{publications}
-\pagebreak
+%% \pagebreak

### 2022-09-01 sections/summary.tex
Update summary.tex

@@
 I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
-I am currently based in Oxford, working on my research.
-Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile (USACH).
-
 Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
-Moreover, I served as a lecturer at the Universidad de Chile and a consultant for the United Nations Development Programme (UNDP).
+Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).
 

### 2022-09-01 spanish/sections/papers.tex
Update papers.tex

@@
 \item{\small Cuevas, C.
-{\itshape et al.} (2021, {\itshape próximamente}).
+{\itshape et al.} (2021).
 Motivación de servicio público entre funcionarios públicos chilenos.
-{\itshape Revista del CLAD Reforma y Democracia}, 80.
+{\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
 {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}
@@
 {\itshape e-Ciencias de la Información, 12}(2), 1--18.
-{\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
 
@@
 {\itshape Revista Chilena de Derecho y Ciencia Política}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2021).
+Sofisticación, participación y compromiso político en América Latina.
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
+{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
 
@@
 (2021).
-Sofisticación, participación y compromiso político en América Latina.
-{\itshape Tufte Working Papers}, 2, 1--21.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
+Hibridación digital en el Cono Sur: Consumo de medios tradicionales, digitales y uso de redes sociales.
+{\itshape Comunifé}, 21, 31--39.
+{\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}}\vspace{1mm}
 
@@
 
-\item{\small González-Bustamante, B.
-(2016).
-Élites políticas, económicas e intelectuales: Una agenda de investigación creciente para la ciencia política.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
-
 \item{\small González-Bustamante, B., \& Cisternas, C.
@@
 \item{\small González-Bustamante, B.
-(2015).
-Evaluando Twitter como indicador de opinión pública: Una mirada al arribo de Bachelet a la presidencial chilena 2013.
-{\itshape Revista SAAP, 9}(1), 119--141.
-{\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+(2016).
+Élites políticas, económicas e intelectuales: Una agenda de investigación creciente para la ciencia política.
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
+\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
 
@@
 \item{\small González-Bustamante, B.
-(2014).
-Elección directa de consejeros regionales 2013.
-Rendimiento del capital político, familiar y económico en una nueva arena electoral en Chile.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+(2015).
+Evaluando Twitter como indicador de opinión pública: Una mirada al arribo de Bachelet a la presidencial chilena 2013.
+{\itshape Revista SAAP, 9}(1), 119--141.
+{\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
 
@@
 \item{\small González-Bustamante, B.
-(2013).
-Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+(2014).
+Elección directa de consejeros regionales 2013.
+Rendimiento del capital político, familiar y económico en una nueva arena electoral en Chile.
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 {\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2013).
+Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
+{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
+{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 

### 2022-09-01 spanish/sections/experience.tex
Update experience.tex
LPPL v1.3c

--- 2021-03-15 spanish/sections/experience.tex
@@
 \cventry
-{Instructor} 
-{Universidad de Santiago de Chile} 
-{Santiago, Chile} 
-{2019 - en comisión}
-{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
-
-\cventry
 {Profesor Adjunto} 
@@
 {Santiago, Chile} 
-{2014 - 2018}
+{2014 - 2019}
 {Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
@@
 {Escuela de Gobierno y Gestión Pública, Instituto de Asuntos Públicos}\vspace{1.5mm}
-
 \end{cventries}

### 2022-10-17 sections/conferences-full.tex
Update conferences-full.tex

@@
 
-\begin{benumerate}{74}
+\begin{benumerate}{77}
+
+\item{González-Bustamante, B.
+(2022, {\itshape forthcoming}).
+{\itshape Machine Learning and Political Events: Application of Semisupervised Approach to Produce a Data Set on Latin American Cabinets}.
+Presentation delivered at the II Training Data Lab Workshop, Virtual.}\vspace{1mm}
 
 \item{González-Bustamante, B., \& Aguilar, D.
-(2022).
+(2022, {\itshape forthcoming}).
 {\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}.
 Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2022).
+{\itshape Machine Learning for the Study of Political Events: Application of Semisupervised Models on Latin American Archives}.
+Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Integrated Repository on Local Government Indicators in Chile}. Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}
 
@@
 {\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}.
-Presentation delivered at the Otto-Friedrich-Universität Bamberg Workshop, Virtual.}\vspace{1mm}
+Presentation delivered at the Workshop on Coalition Politics and Portfolio Design at the University of Bamberg, Virtual.}\vspace{1mm}
 

### 2022-10-17 sections/working-papers.tex
LPPL v1.3c
Update working-papers.tex

@@
 
-\begin{benumerate}{2}
+\begin{benumerate}{3}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Aguilar, D.
+(2022).
+Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set].
+Pre-release version under restricted access.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2022).
 Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
 
-\item{Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2022).
 Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
 
@@
 
-\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}}\vspace{1mm}
+{\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 {\footnotesize \scshape [in Portuguese]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Soto, D.
+\item{\small González-Bustamante, B., \& Soto, D.
 (2016).
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}}\vspace{1mm}
+{\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2015).
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}\vspace{1mm}
 

### 2022-10-17 sections/summary.tex
Update summary.tex

@@
 I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
-Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
+Before starting the DPhil in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
 Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).
 
-My doctoral research is supervised by Professor Petra Schleiter and focuses on cabinets’ stability in Latin American presidential democracies.
-In my DPhil project, I combine the principal-agent theory elements to evaluate the actors’ incentives and strategies in presidential systems.
-My data gathering strategy is based on archives revision using Optical Character Recognition (OCR), Natural Language Processing (NLP), and machine learning techniques.
-In addition, my empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations.
+My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date.
+My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features.
+In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives.
+In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.
 
-My research is funded by the Chilean National Agency for Research and Development, the St Hilda’s College Muriel Wise Fund and the Society for Latin American Studies Postgraduate and Postdoctoral Research Award.
+My research is funded by the Chilean National Agency for Research and Development (ANID), the St Hilda’s College Muriel Wise Fund and the Postgraduate and Postdoctoral Award of the Society for Latin American Studies (SLAS).
 \vspace{1mm}

### 2022-10-17 sections/papers.tex
Update papers.tex

@@
 \item{González-Bustamante, B.
-(2022, {\itshape forthcoming}).
+(2022).
 Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
-{\itshape The British Journal of Politics and International Relations}.}\vspace{1mm}
+{\itshape The British Journal of Politics and International Relations}.
+OnlineFirst.
+{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
 
@@
 FirstView.
-{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 
@@
 {\itshape The International Journal of Press/Politics}.
-Online First.
-{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}}\vspace{1mm}
+OnlineFirst.
+{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}
+{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
 
@@
 {\itshape World Development, 137}, 105180.
-{\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}.}\vspace{1mm}
 
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
+\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).
 Determinants of E-Government in the Municipalities: Evidence from the Chilean Case.
-{\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129.
+{\itshape Gestión y Política Pública, XXIX}(1), 97--129.
 {\footnotesize \scshape [in Spanish]}.
 {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-{\scshape url}:  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:}  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
 
@@
 Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
-{\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
+{\itshape Política y Gobierno, XXV}(1), 31--64.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
+{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
 
@@
 {\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078cr}}.
-\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \\ \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
 
@@
 {\footnotesize \scshape [in Spanish and English]}.
-{\scshape doi}: \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
-\\{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
 
@@
 {\itshape Latin American Business Review, 20}(4), 367--387.
-{\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
 
@@
 Analysis of the Dynamics of Production and Citation.
-{\itshape N\'oesis.
+{\itshape Nóesis.
 Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}
+{\scshape doi:} \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
 
@@
 Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism.
-{\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
+{\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}}\vspace{1mm}
+{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
 
@@
 Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13).
-{\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59--79.
+{\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}} \vspace{1mm}
+{\scshape doi:} \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
 
@@
 Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014.
-{\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
+{\itshape Revista de Gestión Pública, IV}(2), 151--190.
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}
+{\scshape doi:} \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
 
@@
 {\itshape Revista Chilena de Derecho y Ciencia Política}.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
+{\footnotesize \scshape [in Spanish]}.
+{\scshape \footnotesize SocArXiv:} \\ \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
 
@@
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
+{\scshape url:} \\ \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.33539/comunife.2021.n21.2580}{\textcolor{blue}{10.33539/comunife.2021.n21.2580}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}
 
@@
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}.}\vspace{1mm}
 
@@
 Political Elites in the Chilean Legislative Branch: The Chamber of Deputies (1990-2014).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 19--52.
+{\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
+{\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 Electoral Success and Campaign Spending in Elections of Senators and Deputies in Chile 2013.
-{\itshape Pol\'iticas P\'ublicas, 8}(1), 21--35.
+{\itshape Políticas Públicas, 8}(1), 21--35.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}} \vspace{1mm}
+{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-\\ {\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+{\scshape url:} \\ \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014).
-{\itshape Revista de Sociolog\'ia,} 29, 37--54.
+{\itshape Revista de Sociología,} 29, 37--54.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
-\\ {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
 
@@
 Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
+{\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.} \vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
+{\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
 
@@
 Digital Campaigns: Branding or Political Participation?
-{\itshape M\'as Poder Local,} 12, 32--39.
+{\itshape Más Poder Local,} 12, 32--39.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
 

### 2022-10-17 sections/book-chapters.tex
Update book-chapters.tex
LPPL v1.3c

@@
 
-\begin{benumerate}{13}
+\begin{benumerate}{12}
 
-\item{\small González-Bustamante.
-B.
-({\itshape forthcoming}).
-Quantitative and Mixed Methods for Studying Elites: Practical Applications, Biases and Potential.
-In F.
-Robles, I.
-Nercesián \& M.
-Serna (eds.), {\itshape Elites económicas, Estado y dominación en América Latina: Cambios y continuidades en la época post COVID}.
-Buenos Aires: Siglo XXI Editores.
-{\footnotesize \scshape [in Spanish]}.}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2018).
@@
 Cham: Springer.
-{\scshape doi}: \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
-(2018).
-Internet, Digital Social Networks Usage, and Participation in the Southern Cone.
-In P.
-Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras Posibilidades de Comprensi\'on e Investigaci\'on}.
-Santiago: Social-Ediciones.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi}: \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2018).
@@
 Codato \& F.
-Espinoza (eds.), {\itshape Las \'Elites en las Am\'ericas: Diferentes Perspectivas}.
+Espinoza (eds.), {\itshape Las Élites en las Américas: Diferentes Perspectivas}.
 Curitiba: Editora da Universidade Federal do Paraná.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Barr\'ia, D.
+\item{\small González-Bustamante, B., \& Barría, D.
 (2018).
@@
 In N.
-Del Valle (ed.), {\itshape Transformaciones de la Esfera P\'ublica en Chile.
-Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}.
+Del Valle (ed.), {\itshape Transformaciones de la Esfera Pública en Chile.
+Luchas Sociales, Espacio Público y Pluralismo Informativo}.
 Santiago: RIL Editores.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}.}\vspace{1mm}
 
-\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Araya, J.
+\item{\small González-Bustamante, B.
+(2018).
+Internet, Digital Social Networks Usage, and Participation in the Southern Cone.
+In P.
+Cottet (ed.), {\itshape Opinión Pública Contemporánea: Otras Posibilidades de Comprensión e Investigación}.
+Santiago: Social-Ediciones.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi:} \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}.}\vspace{1mm}
+
+\item{\small Barría, D., González-Bustamante, B., \& Araya, J.
 E.
@@
 R.
-Gil-Garc\'ia, J.
+Gil-García, J.
 I.
@@
 C.
-T\'ellez (eds.), {\itshape Tecnolog\'ias de Informaci\'on y Comunicaci\'on en la Administraci\'on P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}.
+Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración Pública: Conceptos, Enfoques, Aplicaciones y Resultados}.
 Mexico City: INFOTEC.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B., \& Sazo, D.
+(2016).
+Viral Campaign.
+In I.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Madrid: Centro de Estudios Políticos y Constitucionales.
+{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Sazo, D.
+(2016).
+Political Branding.
+In I.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Madrid: Centro de Estudios Políticos y Constitucionales.
+{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
 (2016).
@@
 In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D.
-(2016).
-Viral Campaign.
-In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D.
-(2016).
-Political Branding.
-In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
-
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2014).
@@
 In G.
-Sibaja (ed.), {\itshape Nuevos Medios y Comunicaci\'on Pol\'itica Digital}.
+Sibaja (ed.), {\itshape Nuevos Medios y Comunicación Política Digital}.
 San Jose: Fundación Educativa San Judas Tadeo.
@@
 Millaleo \& P.
-C\'arcamo (eds.), {\itshape Mediaciones del Sistema Pol\'itico frente al Activismo Digital}.
+Cárcamo (eds.), {\itshape Mediaciones del Sistema Político frente al Activismo Digital}.
 Santiago: Fundación Democracia y Desarrollo.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2014).
@@
 In O.
-Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica Pol\'itica y Medios Digitales}.
+Avilés {\itshape et al.} (eds.), {\itshape Práctica Política y Medios Digitales}.
 Santiago: Instituto Igualdad.
@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G.
+\item{\small González-Bustamante, B., \& Henríquez, G.
 (2013).
@@
 Crespo \& J.
-del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}.
+del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina}.
 Buenos Aires: Editorial Biblos.
@@
 \end{publications}
+%% \pagebreak

### 2022-10-17 sections/awards.tex
Update awards.tex

--- 2022-06-15 sections/awards.tex
@@
 {SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
-{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1,400}
+{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1 400.}
 {Bath, UK}
@@
 {St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
-{Research support grant for my DPhil (PhD) project and allowance for participation in conferences and purchase of books, {\pounds} 2,225} 
+{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2 255.} 
 {Oxford, UK}
@@
 {Becas Chile Doctoral Scholarship Abroad} 
-{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
+{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
 {Oxford, UK}
@@
 {ALACIP Methodological School Prize}
-{Best methodological work at the Latin American Political Association (ALACIP) School}
+{Best methodological work at the Latin American Political Association (ALACIP) School.}
 {Lima, Peru}
@@
 {Comunicracia Prize}
-{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review)} %% {\pounds} 170
+{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review).} %% {\pounds} 170
 {Parana, Argentina}
@@
 {FONDECYT Thesis Writing Grant}
-{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
+{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
 {Santiago, Chile}

### 2022-10-17 spanish/sections/working-papers.tex
LPPL v1.3c
Update working-papers.tex

@@
 
-\cvsection{Data Collection Projects}
+\cvsection{Proyectos de recopilación de datos}
 
@@
 
-\begin{benumerate}{2}
+\begin{benumerate}{3}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Aguilar, D.
+(2022).
+Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set].
+Versión previa al lanzamiento bajo acceso restringido.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2022).
 Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
 
-\item{Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2022).
 Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
 
@@
 {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
-\\ {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}}\vspace{1mm}
+{\scshape doi:} \\ \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 NUSP/UFPR, 3}(5), 1--19.
-\\ {\scshape url}: \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \\ \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B., \& Soto, D.
+\item{\small González-Bustamante, B., \& Soto, D.
 (2016).
@@
 {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
-{\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}}\vspace{1mm}
+{\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2015).
@@
 {\itshape Revista de Gestión Pública, IV}(1), 143--149.
-{\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}}
+{\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}
 

### 2022-10-17 spanish/sections/summary.tex
Update summary.tex

@@
 Estoy completando mi tesis doctoral en el Departamento de Ciencia Política y Relaciones Internacionales y en St Hilda’s College en la Universidad de Oxford, Reino Unido.
-Antes de comenzar mis estudios doctorales, en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
-Además, me desempeñé como profesor en la Universidad de Santiago y Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
+Antes de comenzar mis estudios doctorales en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
+Además, me desempeñé como profesor adjunto y docente en la Universidad de Santiago y Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
 
-Mi investigación doctoral es supervisada por la Profesora Petra Schleiter y se enfoca en la estabilidad de los gabinetes en las democracias presidenciales latinoamericanas.
-En mi proyecto doctoral combino elementos de la teoría principal-agente para evaluar los incentivos y estrategias de los actores en los sistemas presidenciales.
-Mi estrategia de recopilación de datos se basa en la revisión de archivos mediante reconocimiento óptico de caracteres (OCR), procesamiento del lenguaje natural (NLP) y técnicas de aprendizaje automático.
-Además, mi estrategia empírica emplea métodos de puntuación de propensión y emparejamiento, modelos de riesgos competitivos y modelos de variables instrumentales.
+Mi investigación doctoral es supervisada por la Profesora Petra Schleiter y se centra en las causas y consecuencias de la rotación ministerial en 12 países presidenciales latinoamericanos desde mediados de los años 70 hasta la fecha.
+Mi proyecto integra elementos de la teoría principal-agente para evaluar los incentivos y las estrategias específicas de los actores en los sistemas presidenciales, considerando las características institucionales del régimen.
+En mi proceso de recopilación de datos, apliqué técnicas de reconocimiento óptico de caracteres (OCR), procesamiento del lenguaje natural (NLP) y aprendizaje automático a casi 50 años de archivos de informes de prensa.
+Además, mi estrategia empírica emplea métodos de emparejamiento de puntuación de propensión, modelos semiparamétricos de riesgos competitivos y regresiones de variables instrumentales.
 
-Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo de Chile, St Hilda's College Muriel Wise Fund y Society for Latin American Studies Postgraduate and Postdoctoral Research Award.
+Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo (ANID) de Chile, el Fondo Muriel Wise de St Hilda's College y el Premio de Postgrado y Postdoctorado de la Sociedad de Estudios Latinoamericanos (SLAS).
 \vspace{1mm}

### 2022-10-17 spanish/sections/papers.tex
Update papers.tex

@@
 \item{González-Bustamante, B.
-(2022, {\itshape próximamente}).
+(2022).
 Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
-{\itshape The British Journal of Politics and International Relations}.}\vspace{1mm}
+{\itshape The British Journal of Politics and International Relations}.
+OnlineFirst.
+{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
 
@@
 {\itshape The International Journal of Press/Politics}.
-Online First.
-{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}}
+OnlineFirst.
+{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}
 
@@
 {\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}
+{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
 
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-\\ {\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}}\vspace{1mm}
+{\scshape doi}: \\ \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., Carvajal, A., \& Gonz\'alez, A.
+\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).
 Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno.
-{\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129.
-\\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}} \vspace{1mm}
+{\itshape Gestión y Política Pública, XXIX}(1), 97--129.
+{\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
 
@@
 {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-\\ {\scshape url}: \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
 
@@
 Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010.
-{\itshape Pol\'itica y Gobierno, XXV}(1), 31--64.
-{\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}}\vspace{1mm}
+{\itshape Política y Gobierno, XXV}(1), 31--64.
+{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
 
@@
 {\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
 
@@
 {\itshape Revista de Gestión Pública, IX}(2), 151--169.
-\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}}\vspace{1mm}
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
 
@@
 {\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
 
@@
 {\itshape Latin American Business Review, 20}(4), 367--387.
-\\ {\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}}\vspace{1mm}
+{\scshape doi}: \\ \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
 
-\item{\small Barr\'ia, D., González-Bustamante, B., \& Cisternas, C.
+\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2019).
@@
 Análisis sobre las dinámicas de producción y citación.
-{\itshape N\'oesis.
+{\itshape Nóesis.
 Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
-{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}}\vspace{1mm}
+{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
 
@@
 Agenda política, periodismo y medios digitales en Chile: Notas de investigación sobre pluralismo informativo.
-{\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291--326.
-{\scshape url}: \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}}\vspace{1mm}
+{\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
+{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
 
@@
 {\itshape Colombia Internacional}, 87, 81--108.
-\\ {\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}}\vspace{1mm}
+{\scshape doi}: \\ \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
 
@@
 Servicio civil en Chile, análisis de los directivos de primer nivel jerárquico (2003-13).
-{\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59--79.
-{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}} \vspace{1mm}
+{\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
+{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
 
@@
 Rotación de subsecretarios en Chile: Una exploración de la segunda línea gubernamental, 1990-2014.
-{\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190.
-\\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}
+{\itshape Revista de Gestión Pública, IV}(2), 151--190.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
 
@@
 Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
-{\itshape Revista Chilena de Derecho y Ciencia Política}.}\vspace{1mm}
+{\itshape Revista Chilena de Derecho y Ciencia Política}.
+{\scshape \footnotesize SocArXiv:} \\  \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
 
@@
 {\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
-\\ {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
+\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
 
@@
 {\itshape Comunifé}, 21, 31--39.
-{\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}}\vspace{1mm}
+{\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
 
@@
 Élites políticas en el poder legislativo chileno: La Cámara de Diputados (1990-2014).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 19--52.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+{\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 Élites políticas, económicas e intelectuales: Una agenda de investigación creciente para la ciencia política.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7--17.
-\\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+{\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
+{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 Éxito electoral y gasto en campaña en las elecciones de senadores y diputados en Chile 2013.
-{\itshape Pol\'iticas P\'ublicas, 8}(1), 21--35.
-{\scshape url}: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}} \vspace{1mm}
+{\itshape Políticas Públicas, 8}(1), 21--35.
+{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
 
@@
 {\itshape Revista SAAP, 9}(1), 119--141.
-{\scshape url}: \href{http://ref.scielo.org/dwzhns}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 Los think tanks en el gabinete: Una exploración del caso chileno (2006-2014).
-{\itshape Revista de Sociolog\'ia,} 29, 37--54.
-{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
-{\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}} \vspace{1mm}
+{\itshape Revista de Sociología,} 29, 37--54.
+{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
 
@@
 Rendimiento del capital político, familiar y económico en una nueva arena electoral en Chile.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49--91.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 {\itshape Intersticios Sociales,} 6, 1--20.
-{\scshape url}: \href{http://ref.scielo.org/zrnp2k}{\textcolor{blue}{http://ref.scielo.org}}} \vspace{1mm}
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+{\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
 
@@
 Campañas digitales: ¿Branding o participación política?
-{\itshape M\'as Poder Local,} 12, 32--39.
-{\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}} \vspace{1mm}
+{\itshape Más Poder Local,} 12, 32--39.
+{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
 

### 2022-10-17 spanish/sections/editor.tex
LPPL v1.3c
Update editor.tex

@@
 
-\item{\small Gonz\'alez-Bustamante, B., \& Luci, F.
-({\itshape próximamente}).
+\item{\small González-Bustamante, B., \& Luci, F.
+(2021).
 Élites políticas en América Latina: Socialización, trayectorias y capitales.
-{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.}\vspace{1mm}
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+{\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/issue/view/30}{\textcolor{blue}{www.revistapleyade.cl}}.}\vspace{1mm}
 
-\item{\small Gonz\'alez-Bustamante, B.
+\item{\small González-Bustamante, B.
 (2016).
 Élites políticas, económicas e intelectuales.
-{\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1).
-{\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}
+{\itshape Política, Revista de Ciencia Política, 54}(1).
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 

### 2022-10-17 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 {\scshape doi}: \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2018).
-Internet, uso de redes sociales digitales y participación en el Cono Sur.
-En P.
-Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras posibilidades de Comprensi\'on e Investigaci\'on}.
-Santiago: Social-Ediciones.
-{\scshape doi}: \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}
 
@@
 Codato \& F.
-Espinoza (eds.), {\itshape Las \'Elites en las Am\'ericas: Diferentes Perspectivas}.
+Espinoza (eds.), {\itshape Las Élites en las Américas: Diferentes Perspectivas}.
 Curitiba: Editora da Universidade Federal do Paraná.
-{\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
@@
 En N.
-Del Valle (ed.), {\itshape Transformaciones de la Esfera p\'ublica en Chile.
-Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}.
+Del Valle (ed.), {\itshape Transformaciones de la Esfera Pública en Chile.
+Luchas Sociales, Espacio Público y Pluralismo Informativo}.
 Santiago: RIL Editores.
-{\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}}\vspace{1mm}
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2018).
+Internet, uso de redes sociales digitales y participación en el Cono Sur.
+En P.
+Cottet (ed.), {\itshape Opinión Pública Contemporánea: Otras posibilidades de Comprensión e Investigación}.
+Santiago: Social-Ediciones.
+{\scshape doi:} \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}.}\vspace{1mm}
 
@@
 C.
-T\'ellez (eds.), {\itshape Tecnolog\'ias de Informaci\'on y Comunicaci\'on en la Administraci\'on P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}.
+Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}.
 Ciudad de México: INFOTEC.
-{\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2016).
-Twitter (su uso en la comunicación política).
-En I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [2da edición]}.}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
@@
 En I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 En I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Madrid: Centro de Estudios Políticos y Constitucionales.
+{\footnotesize \scshape [2da edición]}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+(2016).
+Twitter (su uso en la comunicación política).
+En I.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 Santiago: Fundación Democracia y Desarrollo.
-{\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+{\scshape url:} \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 
@@
 (2014).
-Redes sociales como herramienta para la pr\'actica pol\'itica: Twitter y el concepto de opini\'on p\'ublica.
+Redes sociales como herramienta para la práctica política: Twitter y el concepto de opinión pública.
 En O.
-Avil\'es {\itshape et al.} (eds.), {\itshape Pr\'actica Pol\'itica y Medios Digitales}.
+Avilés {\itshape et al.} (eds.), {\itshape Práctica Política y Medios Digitales}.
 Santiago: Instituto Igualdad.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Henr\'iquez, G.
+\item{\small González-Bustamante, B., \& Henríquez, G.
 (2013).
@@
 Crespo \& J.
-del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}.
+del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina}.
 Buenos Aires: Editorial Biblos.}\vspace{1mm}

### 2022-10-17 spanish/sections/awards.tex
Update awards.tex

@@
 {Premio de investigación de postgrado y postdoctoral SLAS y beca para conferencia} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1,400}
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1 400.}
 {Bath, UK}
@@
 {Fondo Muriel Wise de St Hilda's College y beca para viajes y libros} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2,255} 
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2 255.} 
 {Oxford, UK}
@@
 {Beca Doctorado en el Extranjero Becas Chile} 
-{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
+{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
 {Oxford, UK}
@@
 {Premio Escuela Metodológica ALACIP}
-{Mejor trabajo metodológico en la Escuela de la Asociación Latinoamericana de Ciencia Política (ALACIP)}
+{Mejor trabajo metodológico en la Escuela de la Asociación Latinoamericana de Ciencia Política (ALACIP).}
 {Lima, Perú}
@@
 {Premio Comunicracia}
-{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares)} %% {\pounds} 170
+{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares).} %% {\pounds} 170
 {Paraná, Argentina}
@@
 {Beca para investigación de Mag\'ister FONDECYT}
-{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
+{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
 {Santiago, Chile}

### 2022-11-13 sections/oxf_refs.tex
Create oxf_refs.tex

--- 2020-08-24 sections/references.tex
@@
 
-\cvsection{References}
+\cvsection{Referees}
 
@@
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \pagebreak %% \vspace{1.5mm}
-\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:alfredo.joignant@mail.udp.cl}{\textcolor{blue}{alfredo.joignant@mail.udp.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Jaime Baeza}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:jbaezaf@u.uchile.cl}{\textcolor{blue}{jbaezaf@u.uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Marcel Thez\'a}, Associate Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:marcel.theza@ulagos.cl}{\textcolor{blue}{marcel.theza@ulagos.cl}}}} \vspace{1.5mm}
+\item[]{\small {\bfseries David Doyle}, Professor of Politics, University of Oxford, UK}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
 \end{itemize}

### 2023-03-04 sections/papers.tex
Update papers.tex

@@
 B.
-(2022, {\itshape forthcoming}).
+(2022).
 Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential.
-{\itshape Revista Chilena de Derecho y Ciencia Política}.
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
 {\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv:} \\ \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+{\scshape \footnotesize SocArXiv:} \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
 

### 2023-03-04 spanish/sections/papers.tex
Update papers.tex

@@
 B.
-(2022, {\itshape próximamente}).
+(2022).
 Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
-{\itshape Revista Chilena de Derecho y Ciencia Política}.
-{\scshape \footnotesize SocArXiv:} \\  \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
+{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
 

### 2023-03-04 short/sections/selected-papers.tex
Create selected-papers.tex

--- 2022-10-17 sections/papers.tex
@@
 
-\cvsection{Peer-Reviewed Articles}
-
-\cvsubsection{Social Sciences Citation Index (WoS-ISI/SCCI)}
+\cvsection{Featured Publications}
 
@@
 
-\begin{benumerate}{9}
+\begin{itemize}
 
@@
 
-\item{\small Cuevas, C.
-{\itshape et al.} (2021).
-Public Service Motivation Among Chilean Public Employees.
-{\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
-
 \item{\small González-Bustamante, B.
@@
 
+\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2020).
+Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service.
+{\itshape Revista de Gestión Pública, IX}(2), 151--169.
+{\footnotesize \scshape [in Spanish and English]}.
+{\scshape doi:} \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
+
 \item{\small González-Bustamante, B.
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
+\\ {\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
 
@@
 {\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+\\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
 {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
+
+\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+(2019).
+Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014).
+{\itshape Latin American Business Review, 20}(4), 367--387.
+\\ {\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
 
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+\item{\small González-Bustamante, B.
 (2018).
-Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
-{\itshape Política y Gobierno, XXV}(1), 31--64.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+Civil Service Models in Latin America.
+In A.
+Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}.
+Cham: Springer.
+{\scshape doi:} \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}
 
-\end{benumerate}
-
-\end{publications}
-
-\cvsubsection{Scopus \& Emerging Sources Citation Index (WoS-ISI/ESCI)}
-
-\begin{publications}
-
-\begin{benumerate}{9}
-
-\item{\small Cisternas, C., \& González-Bustamante, B.
-(2022).
-Social Sciences in Repression Contexts: Bibliometric Analysis of the Historical Production of the Corporación de Estudios para Latinoamérica, Chile (1979-1989).
-{\itshape e-Ciencias de la Información, 12}(2), 1--18.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078cr}}.
-{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \\ \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
-
-\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
-(2020).
-Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service.
-{\itshape Revista de Gestión Pública, IX}(2), 151--169.
-{\footnotesize \scshape [in Spanish and English]}.
-{\scshape doi:} \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
-
-\item{\small Olivares, A.
-{\itshape et al.} (2020).
-New Challenges, Approaches, and Perspectives in the Study of Political Elites.
-{\itshape Iberoamericana, XX}(74), 229--259.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
-{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
-
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
-(2019).
-Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014).
-{\itshape Latin American Business Review, 20}(4), 367--387.
-{\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
-
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
-(2019).
-The Literature on Open Government in Spanish.
-Analysis of the Dynamics of Production and Citation.
-{\itshape Nóesis.
-Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
-
-\item{\small Del Valle, N., \& González-Bustamante, B.
-(2018).
-Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism.
-{\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Olivares, A.
-(2016).
-Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010).
-{\itshape Colombia Internacional}, 87, 81--108.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-{\itshape et al.} (2016).
-Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13).
-{\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Olivares, A.
-(2015).
-Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014.
-{\itshape Revista de Gestión Pública, IV}(2), 151--190.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
-
-\end{benumerate}
-
-\end{publications}
-
-\cvsubsection{ SciELO \& Latindex}
-
-\begin{publications}
-
-\begin{benumerate}{14}
-
-\item{\small González-Bustamante.
-B.
-(2022, {\itshape forthcoming}).
-Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential.
-{\itshape Revista Chilena de Derecho y Ciencia Política}.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape \footnotesize SocArXiv:} \\ \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-Sophistication, Participation, and Political Engagement in Latin America.
-{\itshape Tufte Working Papers}, 2, 1--21.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Luci, F.
-(2021).
-Political Elites in Latin America: Socialisation, Trajectories, and Capitals.
-{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28, 21--32.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \\ \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-Digital Hybridization in the Southern Cone: Consumption of Traditional and Digital Media and Use of Social Networks.
-{\itshape Comunifé}, 21, 31--39.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.33539/comunife.2021.n21.2580}{\textcolor{blue}{10.33539/comunife.2021.n21.2580}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}
-
-\item{\small González-Bustamante, B., \& Cisternas, C.
-(2020).
-Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study.
-{\itshape Tufte Working Papers}, 1, 1--15.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Cisternas, C.
-(2016).
-Political Elites in the Chilean Legislative Branch: The Chamber of Deputies (1990-2014).
-{\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2016).
-Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science.
-{\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2015).
-Electoral Success and Campaign Spending in Elections of Senators and Deputies in Chile 2013.
-{\itshape Políticas Públicas, 8}(1), 21--35.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2015).
-Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013.
-{\itshape Revista SAAP, 9}(1), 119--141.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \\ \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
-
-\item{\small Olivares, A.
-{\itshape et al.} (2014).
-Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014).
-{\itshape Revista de Sociología,} 29, 37--54.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
-
-\item{\small González-Bustamante, B.
-(2014).
-Popular Election of Regional Councillors 2013.
-Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile.
-{\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.} \vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-The Study of the Elites in Chile: Theoretical and Methodological Approaches.
-{\itshape Intersticios Sociales,} 6, 1--20.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
-{\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
-
-\item{\small González-Bustamante, B., \& Henríquez, G.
-(2012).
-Digital Campaigns: Branding or Political Participation?
-{\itshape Más Poder Local,} 12, 32--39.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
-
-\end{benumerate}
+\end{itemize}
 

### 2023-05-13 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 
+\item{González-Bustamante, B., \& Aguilar, D.
+(2023).
+Territorial patterns of open e-government: evidence from Chilean municipalities.
+{\itshape Political Research Exchange, 5}(1), 2194369.
+{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+
 \item{González-Bustamante, B.
 (2022).
-Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
+Ministerial stability during presidential approval crises: The moderating effect of ministers' attributes on dismissals in Brazil and Chile.
 {\itshape The British Journal of Politics and International Relations}.
@@
 (2021).
-Evolution and Early Government Responses to COVID-19 in South America.
+Evolution and early government responses to COVID-19 in South America.
 {\itshape World Development, 137}, 105180.
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-\\ {\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
+\\ {\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
 
@@
 
+\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
+{\itshape Política y Gobierno, XXV}(1), 31--64.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+
 \end{itemize}

### 2023-05-13 sections/teaching-ev.tex
Create teaching-ev.tex

--- 2022-03-10 sections/teaching.tex
@@
 \begin{itemize}
-\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021}
+\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021 [no teaching evaluation]}
 \end{itemize}
@@
 \begin{itemize}
-\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
+\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020 [no teaching evaluation]}
 \end{itemize}
@@
 \begin{itemize}
-\item[$\circ$]{\small Political Science I (undergraduate lecture), spring 2014, 2018, fall 2015-2019}
-\item[$\circ$]{\small Political Science II (undergraduate lecture), spring 2015-2018}
-\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), fall 2018}
-\item[$\circ$]{\small Workshop for Research Design (graduate seminar), spring 2017-2018}
-\item[$\circ$]{\small Research Methodology (undergraduate lecture), spring 2014-2015, fall 2015-2017}
-\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), fall 2017}
+\item[$\circ$]{\small Political Science I (undergraduate lecture), spring 2014, 2018, fall 2015-2019 [teaching evaluation 4.4/5.0]}
+\item[$\circ$]{\small Political Science II (undergraduate lecture), spring 2015-2018 [teaching evaluation 4.2/5.0]}
+\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), fall 2018 [no teaching evaluation]}
+\item[$\circ$]{\small Workshop for Research Design (graduate seminar), spring 2017-2018 [teaching evaluation 4.0/5.0]}
+\item[$\circ$]{\small Research Methodology (undergraduate lecture), spring 2014-2015, fall 2015-2017 [teaching evaluation 4.0/5.0]}
+\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), fall 2017 [teaching evaluation 4.2/5.0]}
 \end{itemize}
@@
 \begin{itemize}
-\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), fall 2016}
-\item[$\circ$]{\small Political Analysis (undergraduate lecture), fall 2014}
-\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014}
+\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), fall 2016 [no teaching evaluation]}
+\item[$\circ$]{\small Political Analysis (undergraduate lecture), fall 2014 [no teaching evaluation]}
+\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014 [no teaching evaluation]}
 \end{itemize}
@@
 
+{\footnotesize {\itshape Note}.
+The courses I taught were mainly about politics and research methods.
+Students’ evaluations substantiate my ability to teach: my average evaluation was 4.1/5.0 over five years considering 636 students’ surveys, 21 dimensions and a five-point Likert scale.
+My evaluations, on average, demonstrate that students were satisfied with my teaching performance.}
+
 \vspace{1mm}

### 2023-09-22 sections/papers.tex
Update papers.tex

@@
 (2022).
-Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
+Ministerial stability during presidential approval crises: The moderating effect of ministers’ attributes on dismissals in Brazil and Chile.
 {\itshape The British Journal of Politics and International Relations}.
@@
 Digital Hybridization in the Southern Cone: Consumption of Traditional and Digital Media and Use of Social Networks.
-{\itshape Comunifé}, 21, 31--39.
+{\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
 {\footnotesize \scshape [in Spanish]}.

### 2023-09-22 spanish/sections/papers.tex
Update papers.tex

@@
 (2022).
-Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile.
+Ministerial stability during presidential approval crises: The moderating effect of ministers' attributes on dismissals in Brazil and Chile.
 {\itshape The British Journal of Politics and International Relations}.
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
+
+\item{\small González-Bustamante, B., \& Aguilar, D.
+(2023).
+Territorial patterns of open e-government: evidence from Chilean municipalities.
+{\itshape Political Research Exchange, 5}(1).
+{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
 
@@
 Hibridación digital en el Cono Sur: Consumo de medios tradicionales, digitales y uso de redes sociales.
-{\itshape Comunifé}, 21, 31--39.
-{\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
+{\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
+\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
 
@@
 (2016).
-Élites políticas en el poder legislativo chileno: La Cámara de Diputados (1990-2014).
+Élites políticas en el poder legislativo chileno: la Cámara de Diputados (1990-2014).
 {\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
@@
 (2016).
-Élites políticas, económicas e intelectuales: Una agenda de investigación creciente para la ciencia política.
+Élites políticas, económicas e intelectuales: una agenda de investigación creciente para la ciencia política.
 {\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
@@
 (2015).
-Evaluando Twitter como indicador de opinión pública: Una mirada al arribo de Bachelet a la presidencial chilena 2013.
+Evaluando Twitter como indicador de opinión pública: una mirada al arribo de Bachelet a la presidencial chilena 2013.
 {\itshape Revista SAAP, 9}(1), 119--141.
@@
 {\itshape et al.} (2014).
-Los think tanks en el gabinete: Una exploración del caso chileno (2006-2014).
+Los think tanks en el gabinete: una exploración del caso chileno (2006-2014).
 {\itshape Revista de Sociología,} 29, 37--54.
@@
 (2013).
-El estudio de las élites en Chile: Aproximaciones conceptuales y metodológicas.
+El estudio de las élites en Chile: aproximaciones conceptuales y metodológicas.
 {\itshape Intersticios Sociales,} 6, 1--20.

### 2023-09-22 spanish/sections/papers.tex
Update papers.tex

@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi}: \\ \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
+{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
 

### 2023-09-22 sections/papers.tex
Update papers.tex

@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.}\vspace{1mm}
+{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
 

### 2023-09-22 sections/papers.tex
Update papers.tex

@@
 
-\item{\small Cuevas, C.
+%% \item{\small Cuevas, C.
 {\itshape et al.} (2021).
@@
 {\footnotesize \scshape [in Spanish]}.
+{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
+
+\item{\small Cuevas, C.
+{\itshape et al.} (2021).
+Motivación de servicio público entre funcionarios públicos chilenos.
+{\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
 {\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
@@
 
-\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
+%% \item{\small González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
+(2020).
+Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno.
+{\itshape Gestión y Política Pública, XXIX}(1), 97--129.
+{\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2019).
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+\item{\small González-Bustamante, B.
+(2019).
+Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, 80, 1--27.
+{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
+
+%% \item{\small González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
@@
 {\footnotesize \scshape [in Spanish]}.
+{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010.
+{\itshape Política y Gobierno, XXV}(1), 31--64.
 {\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
 
-\item{\small Cisternas, C., \& González-Bustamante, B.
+\item{\small González-Bustamante, B., \& Aguilar, D.
+(2023).
+Territorial patterns of open e-government: evidence from Chilean municipalities.
+{\itshape Political Research Exchange, 5}(1).
+{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+
+%% \item{\small Cisternas, C., \& González-Bustamante, B.
 (2022).
@@
 
-\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+\item{\small Cisternas, C., \& González-Bustamante, B.
+(2022).
+Ciencias sociales en contextos de represión: Análisis bibliométrico de la producción histórica de la Corporación de Estudios para Latinoamérica, Chile (1979-1989).
+{\itshape e-Ciencias de la Información, 12}(2), 1--18.
+{\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
+
+%% \item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
 (2020).
@@
 
-\item{\small Olivares, A.
+\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2020).
+Altos directivos públicos: Un nuevo conjunto de datos de miembros del servicio civil chileno.
+{\itshape Revista de Gestión Pública, IX}(2), 151--169.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
+
+%% \item{\small Olivares, A.
 {\itshape et al.} (2020).
@@
 
+\item{\small Olivares, A.
+{\itshape et al.} (2020).
+Nuevos desafíos, enfoques y perspectivas para estudiar élites políticas.
+{\itshape Iberoamericana, XX}(74), 229--259.
+{\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
+
 \item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
+%% \item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2019).
@@
 
-\item{\small Del Valle, N., \& González-Bustamante, B.
+\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
+(2019).
+La literatura sobre gobierno abierto en español.
+Análisis sobre las dinámicas de producción y citación.
+{\itshape Nóesis.
+Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
+{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
+
+%% \item{\small Del Valle, N., \& González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{\small Del Valle, N., \& González-Bustamante, B.
+(2018).
+Agenda política, periodismo y medios digitales en Chile: Notas de investigación sobre pluralismo informativo.
+{\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
+{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2016).
+Cambios de gabinete y supervivencia de los ministros en Chile durante los gobiernos de la Concertación (1990-2010).
+{\itshape Colombia Internacional}, 87, 81--108.
+{\scshape doi}: \\ \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 {\itshape et al.} (2016).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{\small González-Bustamante, B.
+{\itshape et al.} (2016).
+Servicio civil en Chile, análisis de los directivos de primer nivel jerárquico (2003-13).
+{\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
+{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Olivares, A.
 (2015).
@@
 {\scshape doi:} \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2015).
+Rotación de subsecretarios en Chile: Una exploración de la segunda línea gubernamental, 1990-2014.
+{\itshape Revista de Gestión Pública, IV}(2), 151--190.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
 
@@
 
-\item{\small González-Bustamante.
+%% \item{\small González-Bustamante.
 B.
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante.
+B.
+(2022).
+Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
+{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., \& Luci, F.
+\item{\small González-Bustamante, B.
+(2021).
+Sofisticación, participación y compromiso político en América Latina.
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Luci, F.
 (2021).
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante, B., \& Luci, F.
+(2021).
+Élites políticas en América Latina: Socialización, trayectorias y capitales.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+21--32.
+{\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
+\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{\small González-Bustamante, B.
+(2021).
+Hibridación digital en el Cono Sur: Consumo de medios tradicionales, digitales y uso de redes sociales.
+{\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
+\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Cisternas, C.
 (2020).
@@
 \item{\small González-Bustamante, B., \& Cisternas, C.
+(2020).
+Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continuo, para el estudio de las élites.
+{\itshape Tufte Working Papers}, 1, 1--15.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Cisternas, C.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante, B., \& Cisternas, C.
+(2016).
+Élites políticas en el poder legislativo chileno: la Cámara de Diputados (1990-2014).
+{\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2016).
@@
 \item{\small González-Bustamante, B.
+(2016).
+Élites políticas, económicas e intelectuales: una agenda de investigación creciente para la ciencia política.
+{\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
+{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2015).
@@
 (2015).
+Éxito electoral y gasto en campaña en las elecciones de senadores y diputados en Chile 2013.
+{\itshape Políticas Públicas, 8}(1), 21--35.
+{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
+(2015).
 Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013.
@@
 
-\item{\small Olivares, A.
+\item{\small González-Bustamante, B.
+(2015).
+Evaluando Twitter como indicador de opinión pública: una mirada al arribo de Bachelet a la presidencial chilena 2013.
+{\itshape Revista SAAP, 9}(1), 119--141.
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+
+%% \item{\small Olivares, A.
 {\itshape et al.} (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{\small Olivares, A.
+{\itshape et al.} (2014).
+Los think tanks en el gabinete: una exploración del caso chileno (2006-2014).
+{\itshape Revista de Sociología,} 29, 37--54.
+{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+
+%% \item{\small González-Bustamante, B.
 (2014).
@@
 \item{\small González-Bustamante, B.
+(2014).
+Elección directa de consejeros regionales 2013.
+Rendimiento del capital político, familiar y económico en una nueva arena electoral en Chile.
+{\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2013).
@@
 (2013).
+El estudio de las élites en Chile: aproximaciones conceptuales y metodológicas.
+{\itshape Intersticios Sociales,} 6, 1--20.
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
+(2013).
 Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010).
@@
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+\item{\small González-Bustamante, B.
+(2013).
+Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
+{\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
+
+%% \item{\small González-Bustamante, B., \& Henríquez, G.
 (2012).
@@
 
+\item{\small González-Bustamante, B., \& Henríquez, G.
+(2012).
+Campañas digitales: ¿Branding o participación política?
+{\itshape Más Poder Local,} 12, 32--39.
+{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
+
 \end{benumerate}

### 2023-09-22 sections/book-chapters.tex
Update book-chapters.tex

@@
 In A.
-Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}.
+Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance} (pp.
+775--783).
 Cham: Springer.
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+%% \item{\small González-Bustamante, B., \& Olivares, A.
 (2018).
@@
 Codato \& F.
-Espinoza (eds.), {\itshape Las Élites en las Américas: Diferentes Perspectivas}.
+Espinoza (eds.), {\itshape Las élites en las Américas: diferentes perspectivas} (pp.
+245--282).
 Curitiba: Editora da Universidade Federal do Paraná.
@@
 
-\item{\small González-Bustamante, B., \& Barría, D.
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2018).
+La élite política gubernamental en Chile: supervivencia de ministros.
+In A.
+Codato \& F.
+Espinoza (eds.), {\itshape Las élites en las Américas: diferentes perspectivas} (pp.
+245--282).
+Curitiba: Editora da Universidade Federal do Paraná.
+{\scshape url:} \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Barría, D.
 (2018).
@@
 In N.
-Del Valle (ed.), {\itshape Transformaciones de la Esfera Pública en Chile.
-Luchas Sociales, Espacio Público y Pluralismo Informativo}.
+Del Valle (ed.), {\itshape Transformaciones de la esfera pública en Chile.
+Luchas sociales, espacio público y pluralismo informativo} (pp.
+99--116).
 Santiago: RIL Editores.
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante, B., \& Barría, D.
+(2018).
+Expansión de la esfera pública en Chile: Redes sociales, campañas electorales y participación digital.
+In N.
+Del Valle (ed.), {\itshape Transformaciones de la esfera pública en Chile.
+Luchas sociales, espacio público y pluralismo informativo} (pp.
+99--116).
+Santiago: RIL Editores.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2018).
@@
 In P.
-Cottet (ed.), {\itshape Opinión Pública Contemporánea: Otras Posibilidades de Comprensión e Investigación}.
+Cottet (ed.), {\itshape Opinión pública contemporánea: otras posibilidades de comprensión e investigación} (pp.
+113--137).
 Santiago: Social-Ediciones.
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Araya, J.
-E.
+\item{\small González-Bustamante, B.
+(2018).
+Internet, uso de redes sociales digitales y participación en el Cono Sur.
+In P.
+Cottet (ed.), {\itshape Opinión pública contemporánea: otras posibilidades de comprensión e investigación} (pp.
+113--137).
+Santiago: Social-Ediciones.
+{\scshape doi:} \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}.}\vspace{1mm}
+
+%% \item{\small Barría, D., González-Bustamante, B., \& Araya, E.
 (2017).
@@
 C.
-Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración Pública: Conceptos, Enfoques, Aplicaciones y Resultados}.
+Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración Pública: Conceptos, Enfoques, Aplicaciones y Resultados} (pp.
+351--380).
 Mexico City: INFOTEC.
@@
 
-\item{\small González-Bustamante, B., \& Sazo, D.
+\item{\small Barría, D., González-Bustamante, B., \& Araya, E.
+(2017).
+Democracia electrónica y participación digital.
+Avances y desafíos.
+In J.
+R.
+Gil-García, J.
+I.
+Criado \&  J.
+C.
+Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados} (pp.
+351--380).
+Mexico City: INFOTEC.
+{\scshape url:} \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Sazo, D.
 (2016).
@@
 In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política} (pp.
+68--70).
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 (2016).
+Campaña viral.
+In I.
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+68--70).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Sazo, D.
+(2016).
 Political Branding.
 In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política} (pp.
+48--50).
+Madrid: Centro de Estudios Políticos y Constitucionales.
+{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Sazo, D.
+(2016).
+Imagen de marca para un candidato o gobierno (branding político).
+In I.
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+48--50).
+Madrid: Centro de Estudios.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
+(2016).
+Twitter Usage in Political Communication.
+In I.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política} (pp.
+378--380).
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 (2016).
-Twitter Usage in Political Communication.
+Twitter (su uso en la comunicación política).
 In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+378--380).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+%% \item{\small González-Bustamante, B.
 (2014).
@@
 In G.
-Sibaja (ed.), {\itshape Nuevos Medios y Comunicación Política Digital}.
+Sibaja (ed.), {\itshape Nuevos medios y comunicación política digital} (pp.
+227--246).
 San Jose: Fundación Educativa San Judas Tadeo.
@@
 (2014).
+Nuevos medios y política digital: El caso de las primarias presidenciales chilenas de 2013.
+In G.
+Sibaja (ed.), {\itshape Nuevos  medios y comunicación política digital} (pp.
+227--246).
+San José: Fundación Educativa San Judas Tadeo.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
+(2014).
 Digital Activism, Social Networks, and Brokerage.
@@
 Millaleo \& P.
-Cárcamo (eds.), {\itshape Mediaciones del Sistema Político frente al Activismo Digital}.
+Cárcamo (eds.), {\itshape Mediaciones del sistema político frente al activismo digital} (pp.
+77--101).
 Santiago: Fundación Democracia y Desarrollo.
@@
 (2014).
+Activismo digital, redes sociales e intermediación.
+In S.
+Millaleo \& P.
+C\'arcamo (eds.), {\itshape Mediaciones del  sistema político frente al activismo digital} (pp.
+77--101).
+Santiago: Fundación Democracia y Desarrollo.
+{\scshape url:} \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
+(2014).
 Social Networks as a Tool for Political Engage: Twitter and the Public Opinion Concept.
 In O.
-Avilés {\itshape et al.} (eds.), {\itshape Práctica Política y Medios Digitales}.
+Avilés {\itshape et al.} (eds.), {\itshape Práctica política y medios digitales} (pp.
+77--98).
 Santiago: Instituto Igualdad.
@@
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+\item{\small González-Bustamante, B.
+(2014).
+Redes sociales como herramienta para la práctica política: Twitter y el concepto de opinión pública.
+In O.
+Avilés et al.
+(eds.), {\itshape Práctica política y medios digitales} (pp.
+77--98).
+Santiago: Instituto Igualdad.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Henríquez, G.
 (2013).
@@
 Crespo \& J.
-del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina}.
+del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina} (pp 285--296).
 Buenos Aires: Editorial Biblos.
 {\footnotesize \scshape [in Spanish].}}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Henríquez, G.
+(2013).
+Chile: la campaña digital 2009-2010.
+In I.
+Crespo \& J.
+del Rey (eds.), {\itshape Comunicación Política \& Campañas Electorales en América Latina} (pp 285--296).
+Buenos Aires: Editorial Biblos.}\vspace{1mm}
 

### 2023-09-22 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 En A.
-Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}.
+Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}  (pp.
+775--783).
 Cham: Springer.
@@
 (2018).
-La élite política gubernamental en Chile: Supervivencia de ministros.
+La élite política gubernamental en Chile: supervivencia de ministros.
 En A.
 Codato \& F.
-Espinoza (eds.), {\itshape Las Élites en las Américas: Diferentes Perspectivas}.
+Espinoza (eds.), {\itshape Las élites en las Américas: diferentes perspectivas} (pp.
+245--282).
 Curitiba: Editora da Universidade Federal do Paraná.
@@
 En N.
-Del Valle (ed.), {\itshape Transformaciones de la Esfera Pública en Chile.
-Luchas Sociales, Espacio Público y Pluralismo Informativo}.
+Del Valle (ed.), {\itshape Transformaciones de la esfera pública en Chile.
+Luchas sociales, espacio público y pluralismo informativo} (pp.
+99--116).
 Santiago: RIL Editores.
@@
 En P.
-Cottet (ed.), {\itshape Opinión Pública Contemporánea: Otras posibilidades de Comprensión e Investigación}.
+Cottet (ed.), {\itshape Opinión pública contemporánea: otras posibilidades de comprensión e investigación} (pp.
+113--137).
 Santiago: Social-Ediciones.
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Araya, J.
-E.
+\item{\small Barría, D., González-Bustamante, B., \& Araya, E.
 (2017).
@@
 C.
-Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}.
+Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados} (pp.
+351--380).
 Ciudad de México: INFOTEC.
@@
 En I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [2da edición]}.}\vspace{1mm}
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
+68--70).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
 
@@
 En I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [2da edición]}.}\vspace{1mm}
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
+48--50).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
 
@@
 En I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
-Madrid: Centro de Estudios Políticos y Constitucionales.
-{\footnotesize \scshape [2da edición]}.}\vspace{1mm}
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
+378--380).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
 
@@
 En G.
-Sibaja (ed.), {\itshape Nuevos Medios y Comunicaci\'on Pol\'itica Digital}.
+Sibaja (ed.), {\itshape Nuevos  medios y comunicación política digital} (pp.
+227--246).
 San José: Fundación Educativa San Judas Tadeo.}\vspace{1mm}
@@
 Millaleo \& P.
-C\'arcamo (eds.), {\itshape Mediaciones del Sistema Pol\'itico frente al Activismo Digital}.
+C\'arcamo (eds.), {\itshape Mediaciones del  sistema político frente al activismo digital} (pp.
+77--101).
 Santiago: Fundación Democracia y Desarrollo.
@@
 En O.
-Avilés {\itshape et al.} (eds.), {\itshape Práctica Política y Medios Digitales}.
+Avilés et al.
+(eds.), {\itshape Práctica política y medios digitales} (pp.
+77--98).
 Santiago: Instituto Igualdad.}\vspace{1mm}
@@
 (2013).
-Chile: La campaña digital 2009-2010.
+Chile: la campaña digital 2009-2010.
 En I.
 Crespo \& J.
-del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina}.
+del Rey (eds.), {\itshape Comunicación Política \& Campañas Electorales en América Latina} (pp 285--296).
 Buenos Aires: Editorial Biblos.}\vspace{1mm}

### 2023-09-22 spanish/sections/working-papers.tex
Update working-papers.tex

@@
 
-\begin{benumerate}{3}
+\begin{benumerate}{6}
 
 \item{\small González-Bustamante, B., \& Aguilar, D.
-(2022).
-Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set].
-Versión previa al lanzamiento bajo acceso restringido.
+(2023).
+Data Set on Local Government Indicators in Chile (Version 0.20.15 -- Late Sky).
+Dataset, versión previa al lanzamiento, University of Oxford, Universidad de Santiago de Chile (USACH) y Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
@@
 \item{\small González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
+(2023).
+Data Set on Chilean Ministers (1990-2014) (Version 3.3.7 -- Soft Dew).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor y Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
 
-\item{González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor y Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor y Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+et al.
+(2023).
+Chilean Political Science Ranking.
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH) y Training Data Lab.
+{\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+et al.
+(2021).
+Survival of the Senior Civil Servants in the Chilean Executive Branch (Version 1.13.19 -- Bold Lab).
+Dataset, versión previa al lanzamiento bajo acceso restringido, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.8115596}{\textcolor{blue}{10.5281/zenodo.8115596}}.}\vspace{1mm}
 
@@
 \end{publications}
-\pagebreak
+%% \pagebreak
 
@@
 A rotatividade de subsecretários dos ministérios no Chile (1990-2014).
-{\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil.
+{\itshape Newsletter.
+Observat\'orio de elites pol\'iticas e sociais do Brasil.
 NUSP/UFPR, 3}(5), 1--19.
@@
 Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave.
-{\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
+{\itshape Serie Política, Gestión y Políticas Públicas}, 2, 1--26.
 {\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}

### 2023-09-22 sections/working-papers.tex
Update working-papers.tex

@@
 
-\begin{benumerate}{3}
+\begin{benumerate}{6}
 
 \item{\small González-Bustamante, B., \& Aguilar, D.
-(2022).
-Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set].
-Pre-release version under restricted access.
+(2023).
+Data Set on Local Government Indicators in Chile (Version 0.20.15 -- Late Sky).
+Dataset, pre-release version, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
@@
 \item{\small González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
+(2023).
+Data Set on Chilean Ministers (1990-2014) (Version 3.3.7 -- Soft Dew).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
 
-\item{González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+et al.
+(2023).
+Chilean Political Science Ranking.
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
+{\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}
+
+\item{\small González-Bustamante, B.
+et al.
+(2021).
+Survival of the Senior Civil Servants in the Chilean Executive Branch (Version 1.13.19 -- Bold Lab).
+Dataset, pre-release version under restricted access, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.8115596}{\textcolor{blue}{10.5281/zenodo.8115596}}.}\vspace{1mm}
 
@@
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+%% \item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+(2016).
+¿Puerta giratoria?
+Análisis de la circulación público-privada en Chile (2000-2014).
+{\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
+{\scshape doi:} \\ \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Olivares, A.
 (2016).
 Undersecretaries Rotation in the Chilean Cabinets (1990-2014).
-{\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil.
+{\itshape Newsletter.
+Observat\'orio de elites pol\'iticas e sociais do Brasil.
 NUSP/UFPR, 3}(5), 1--19.
@@
 
-\item{\small González-Bustamante, B., \& Soto, D.
+\item{\small González-Bustamante, B., \& Olivares, A.
+(2016).
+A rotatividade de subsecretários dos ministérios no Chile (1990-2014).
+{\itshape Newsletter.
+Observat\'orio de elites pol\'iticas e sociais do Brasil.
+NUSP/UFPR, 3}(5), 1--19.
+{\scshape url:} \\ \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B., \& Soto, D.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{\small González-Bustamante, B., \& Soto, D.
+(2016).
+Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave.
+{\itshape Serie Política, Gestión y Políticas Públicas}, 2, 1--26.
+{\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}
+
+%% \item{\small González-Bustamante, B.
 (2015).
@@
 
+\item{\small González-Bustamante, B.
+(2015).
+Programas de Naciones Unidas para el Desarrollo (PNUD).
+(2014).
+Ciudadanía Política: Voz y Participación Ciudadana en América Latina.
+Buenos Aires: Siglo Veintiuno Editores.
+{\itshape Revista de Gestión Pública, IV}(1), 143--149.
+{\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}
+
 \end{benumerate}

### 2023-09-22 sections/experience.tex
Update experience.tex

@@
 {Universidad de Santiago de Chile} 
-{Santiago, Chile} 
+{Santiago, CHL} 
 {2014 - 2019}
@@
 {United Nations Development Programme (UNDP)} 
-{Santiago, Chile} 
+{Santiago, CHL} 
 {2016 - 2017}
@@
 {Universidad de Chile} 
-{Santiago, Chile} 
+{Santiago, CHL} 
 {2013 - 2016}

### 2023-09-22 spanish/sections/experience.tex
Update experience.tex

@@
 
-\begin{cventries}
+%% \begin{cventries}
+%% \cventry
+%% {Profesor Instructor} 
+%% {Universidad de Santiago de Chile} 
+%% {Santiago, CHL} 
+%% {2019 - hoy}
+%% {Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
+
 \cventry
@@
 {Programa de las Naciones Unidas para el Desarrollo (PNUD)} 
-{Santiago, Chile} 
+{Santiago, CHL} 
 {2016 - 2017}

### 2023-09-22 spanish/sections/teaching.tex
Update teaching.tex
LPPL v1.3c

@@
 \begin{itemize}
-\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, UK}
+\item{\small Escuela de Negocios, {\bfseries Universidad Mayor}, Santiago, CHL}
+\begin{itemize}
+\item[$\circ$]{\small Aprendizaje Automático para Políticas Públicas y Economía (taller, Prof. Carla Cisternas), primavera 2021}
+\end{itemize} 
+\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, GBR}
 \begin{itemize}
@@
 \end{itemize} 
-\item{\small Facultad de Administración y Economía, {\bfseries Universidad de Santiago}, Santiago, Chile}
+\item{\small Facultad de Administración y Economía, {\bfseries Universidad de Santiago}, Santiago, CHL}
 \begin{itemize}
@@
 \item[$\circ$]{\small Metodología de la Investigación (curso de pregrado), primavera 2014-2015, otoño 2015-2017}
-%% \item[$\circ$]{\small Introducción a los Métodos Cuantitativos (curso de pregrado), otoño 2017}
+\item[$\circ$]{\small Introducción a los Métodos Cuantitativos (curso de pregrado), otoño 2017}
 \end{itemize}
-\item{\small Escuela de Gobierno y Gestión Pública, {\bfseries Universidad de Chile}, Santiago, Chile}
+\item{\small Escuela de Gobierno y Gestión Pública, {\bfseries Universidad de Chile}, Santiago, CHL}
 \begin{itemize}
@@
 \end{publications}
+ \pagebreak

### 2023-09-22 sections/teaching.tex
LPPL v1.3c
Update teaching.tex

@@
 \begin{itemize}
-\item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, Chile}
+\item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, CHL}
 \begin{itemize}
@@
 \end{itemize}
-\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
+\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, GBR}
 \begin{itemize}
@@
 \end{itemize}
-\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, Chile}
+\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, CHL}
 \begin{itemize}
@@
 \end{itemize}
-\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
+\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, CHL}
 \begin{itemize}

### 2023-09-22 sections/projects.tex
Update projects.tex
LPPL v1.3c

@@
 {Chilean Political Science Impact Ranking} 
-{This research have not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
+{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
 {Coordinator}
@@
 {COVID-19 Pandemic in South America}
-{This research have not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
+{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
 {Coordinator}

### 2023-09-22 sections/oxf_refs.tex
Update oxf_refs.tex

@@
 \begin{itemize}
-\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
+\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, GBR}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries David Doyle}, Professor of Politics, University of Oxford, UK}
+\item[]{\small {\bfseries David Doyle}, Professor of Politics, University of Oxford, GBR}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
+\item[]{\small {\bfseries Ryan E. Carlin}, Professor of Political Science, Georgia State University, USA}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:rcarlin@gsu.edu}{\textcolor{blue}{rcarlin@gsu.edu}}}} \vspace{1.5mm}
 \end{itemize}

### 2023-09-22 sections/languages.tex
LPPL v1.3c
Update languages.tex

@@
 {Languages} 
-{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), French}
+{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}
 
@@
 {} 
-{(elemental reading skills)} \\
+{(elemental reading skills), French (elemental reading skills)} \\
 

### 2023-09-22 spanish/sections/summary.tex
Update summary.tex

@@
 
-Estoy completando mi tesis doctoral en el Departamento de Ciencia Política y Relaciones Internacionales y en St Hilda’s College en la Universidad de Oxford, Reino Unido.
+\textcolor{black}{Estoy completando mi tesis doctoral en el Departamento de Ciencia Política y Relaciones Internacionales y en St Hilda’s College en la Universidad de Oxford, Reino Unido.
 Antes de comenzar mis estudios doctorales en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
-Además, me desempeñé como profesor adjunto y docente en la Universidad de Santiago y Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
+Además, me desempeñé como profesor adjunto y docente en la Universidad de Santiago y Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).}
 
-Mi investigación doctoral es supervisada por la Profesora Petra Schleiter y se centra en las causas y consecuencias de la rotación ministerial en 12 países presidenciales latinoamericanos desde mediados de los años 70 hasta la fecha.
+\textcolor{black}{Mi investigación doctoral es supervisada por la Profesora Petra Schleiter y se centra en las causas y consecuencias de la rotación ministerial en 12 países presidenciales latinoamericanos desde mediados de los años 70 hasta la fecha.
 Mi proyecto integra elementos de la teoría principal-agente para evaluar los incentivos y las estrategias específicas de los actores en los sistemas presidenciales, considerando las características institucionales del régimen.
 En mi proceso de recopilación de datos, apliqué técnicas de reconocimiento óptico de caracteres (OCR), procesamiento del lenguaje natural (NLP) y aprendizaje automático a casi 50 años de archivos de informes de prensa.
-Además, mi estrategia empírica emplea métodos de emparejamiento de puntuación de propensión, modelos semiparamétricos de riesgos competitivos y regresiones de variables instrumentales.
+Además, mi estrategia empírica emplea métodos de emparejamiento de puntuación de propensión, modelos semiparamétricos de riesgos competitivos y regresiones de variables instrumentales.}
 
-Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo (ANID) de Chile, el Fondo Muriel Wise de St Hilda's College y el Premio de Postgrado y Postdoctorado de la Sociedad de Estudios Latinoamericanos (SLAS).
+\textcolor{black}{Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo (ANID) de Chile, el Fondo Muriel Wise de St Hilda's College y el Premio de Postgrado y Postdoctorado de la Sociedad de Estudios Latinoamericanos (SLAS).}
 \vspace{1mm}

### 2023-09-22 sections/summary.tex
Update summary.tex

@@
 
-I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
+\textcolor{black}{I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
 Before starting the DPhil in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
-Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).
+Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).}
 
-My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date.
+\textcolor{black}{My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date.
 My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features.
 In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives.
-In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.
+In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.}
 
-My research is funded by the Chilean National Agency for Research and Development (ANID), the St Hilda’s College Muriel Wise Fund and the Postgraduate and Postdoctoral Award of the Society for Latin American Studies (SLAS).
+\textcolor{black}{My research is funded by the Chilean National Agency for Research and Development (ANID), the St Hilda’s College Muriel Wise Fund and the Postgraduate and Postdoctoral Award of the Society for Latin American Studies (SLAS).}
 \vspace{1mm}

### 2023-09-22 spanish/sections/summary.tex
Update summary.tex

@@
 En mi proceso de recopilación de datos, apliqué técnicas de reconocimiento óptico de caracteres (OCR), procesamiento del lenguaje natural (NLP) y aprendizaje automático a casi 50 años de archivos de informes de prensa.
-Además, mi estrategia empírica emplea métodos de emparejamiento de puntuación de propensión, modelos semiparamétricos de riesgos competitivos y regresiones de variables instrumentales.}
+Además, mi estrategia empírica emplea métodos de emparejamiento de puntuación de propensión, modelos semiparamétricos de riesgos competitivos y regresiones de variables instrumentales (IV).}
 

### 2023-09-22 sections/summary.tex
Update summary.tex

@@
 In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives.
-In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.}
+In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental variables (IV) regressions.}
 

### 2023-09-22 spanish/sections/recent-awards.tex
Create recent-awards.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in Spanish
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% LaTeX Project Public License v1.3c
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Honores \& premios recientes}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Premio para las Sesiones Conjuntas de Talleres de ECPR} 
{Ayuda de viaje para las Sesiones Conjuntas de Talleres del Consorcio Europeo de Investigación Política (ECPR), {\pounds} 1 350.}
{Toulouse, FRA}
{2023}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Premio de investigación de postgrado y postdoctoral SLAS y beca para conferencia} 
{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1 400.}
{Bath, GBR}
{2022}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Fondo Muriel Wise de St Hilda's College y beca para viajes y libros} 
{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2 255.} 
{Oxford, GBR}
{2022}
\end{cvhonors}

\vspace{1mm}

\begin{cvhonors}
\cvhonor
{Beca Doctorado en el Extranjero Becas Chile} 
{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
{Oxford, GBR}
{2019}
\end{cvhonors}

\vspace{1mm}

### 2023-09-23 sections/awards.tex
Update awards.tex

--- 2022-07-11 sections/awards.tex
@@
 \cvhonor
+{ECPR Joint Sessions of Workshops Grant}
+{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, {\pounds} 1 350.}
+{Toulouse, FRA}
+{2023}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
 {SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
-{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1,400}
-{Bath, UK}
+{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1 400.}
+{Bath, GBR}
 {2022}
@@
 {St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
-{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2,255} 
-{Oxford, UK}
+{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2 255.} 
+{Oxford, GBR}
 {2022}
@@
 {Becas Chile Doctoral Scholarship Abroad} 
-{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
-{Oxford, UK}
+{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
+{Oxford, GBR}
 {2019}
@@
 %% {Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
-%% {Santiago, Chile}
+%% {Santiago, CHL}
 %% {2016}
@@
 {ALACIP Methodological School Prize}
-{Best methodological work at the Latin American Political Association (ALACIP) School}
-{Lima, Peru}
+{Best methodological work at the Latin American Political Association (ALACIP) School.}
+{Lima, PER}
 {2015}
@@
 %% {Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
-%% {Santiago, Chile}
+%% {Santiago, CHL}
 %% {2014} 
@@
 {Comunicracia Prize}
-{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review)} %% {\pounds} 170
-{Parana, Argentina}
+{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review).} %% {\pounds} 170
+{Parana, ARG}
 {2013}
@@
 {FONDECYT Thesis Writing Grant}
-{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
-{Santiago, Chile}
+{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
+{Santiago, CHL}
 {2012}

### 2023-09-23 spanish/sections/awards.tex
Update awards.tex

--- 2022-07-11 spanish/sections/awards.tex
@@
 \cvhonor
+{Premio para las Sesiones Conjuntas de Talleres de ECPR} 
+{Ayuda de viaje para las Sesiones Conjuntas de Talleres del Consorcio Europeo de Investigación Política (ECPR), {\pounds} 1 350.}
+{Toulouse, FRA}
+{2023}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
 {Premio de investigación de postgrado y postdoctoral SLAS y beca para conferencia} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1,400}
-{Bath, UK}
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1 400.}
+{Bath, GBR}
 {2022}
@@
 {Fondo Muriel Wise de St Hilda's College y beca para viajes y libros} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2,255} 
-{Oxford, UK}
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2 255.} 
+{Oxford, GBR}
 {2022}
@@
 {Beca Doctorado en el Extranjero Becas Chile} 
-{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
-{Oxford, UK}
+{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
+{Oxford, GBR}
 {2019}
@@
 %% {Apoyo financiero para participar en la Escuela de Verano en Métodos en Experimentales del Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
-%% {Santiago, Chile}
+%% {Santiago, CHL}
 %% {2016}
@@
 {Premio Escuela Metodológica ALACIP}
-{Mejor trabajo metodológico en la Escuela de la Asociación Latinoamericana de Ciencia Política (ALACIP)}
-{Lima, Perú}
+{Mejor trabajo metodológico en la Escuela de la Asociación Latinoamericana de Ciencia Política (ALACIP).}
+{Lima, PER}
 {2015}
@@
 %% {Apoyo financiero para participar en la Escuela de Verano en Métodos Mixtos en la Pontifica Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
-%% {Santiago, Chile}
+%% {Santiago, CHL}
 %% {2014} 
@@
 {Premio Comunicracia}
-{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares)} %% {\pounds} 170
-{Paraná, Argentina}
+{Mejor trabajo en el área de comunicación política en el XI Congreso Argentino de Ciencia Política (doble evaluación ciega de pares).} %% {\pounds} 170
+{Paraná, ARG}
 {2013}
@@
 %% {La más alta calificación y las felicitaciones del jurado en la Universidad de Chile}
-%% {Santiago, Chile}
+%% {Santiago, CHL}
 %% {2013}
@@
 \cvhonor
-{Beca para investigación de Mag\'ister FONDECYT}
-{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
-{Santiago, Chile}
+{Beca para investigación de Magíster FONDECYT}
+{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
+{Santiago, CHL}
 {2012}

### 2023-09-23 spanish/sections/papers.tex
Update papers.tex

@@
 
-\cvsubsection{Social Sciences Citation Index (WoS-ISI/SCCI)}
+\cvsubsection{Social Sciences Citation Index (WoS-SSCI, ex ISI)}
 
@@
 \item{\small Cuevas, C.
-{\itshape et al.} (2021).
+et al.
+(2021).
 Motivación de servicio público entre funcionarios públicos chilenos.
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+{\scshape doi}: \\ \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
 {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
@@
 
-\cvsubsection{Scopus \& Emerging Sources Citation Index (WoS-ISI/ESCI)}
+\cvsubsection{Scopus \& Emerging Sources Citation Index (WoS-ESCI)}
 
@@
 \item{\small Olivares, A.
-{\itshape et al.} (2020).
+et al.
+(2020).
 Nuevos desafíos, enfoques y perspectivas para estudiar élites políticas.
@@
 \item{\small González-Bustamante, B.
-{\itshape et al.} (2016).
+et al.
+(2016).
 Servicio civil en Chile, análisis de los directivos de primer nivel jerárquico (2003-13).
@@
 \item{\small Olivares, A.
-{\itshape et al.} (2014).
+et al.
+(2014).
 Los think tanks en el gabinete: una exploración del caso chileno (2006-2014).

### 2023-09-23 sections/reviewer.tex
Update reviewer.tex
LPPL v1.3c

@@
 
-\cvsection{Peer Reviewer \& Expert}
+\cvsection{Peer Reviewer, Expert \& Committees}
 
@@
 \begin{itemize}
-\item{\small Varieties of Democracy Project, University of Gothenburg, Sweden, 2014, 2018-2020}
+\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
+\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
+\item{\small Moderator in {\itshape SocArXiv}, University of Maryland, USA, {\itshape since} 2023}
+\item{\small Experts Network for Transparency, Pan American Development Foundation, ECU, {\itshape since} 2022}
+\item{\small Master in Management and Public Policy, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2022}
+\item{\small Reviewer in {\scshape WoS-SSCI}, {\scshape Scopus}, \& {\scshape WoS-ESCI} journals, {\itshape since} 2013}
+\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, {\itshape since} 2013}
+\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018, 2019, 2022-2023}
+\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020}
 \item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
-\item{\small Sectoral Commission for Research, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
-\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, 
-Netherlands, 2018-2019, 2022}
-\item{\small Reviewer in {\scshape WoS-ISI/SSCI/ESCI} \& {\scshape Scopus} journals, since 2013}
-\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, since 2013}
+\item{\small Sectoral Commission for Research, Universidad de la República, URY, 2016, 2018}
 \end{itemize}
@@
 \vspace{1mm}
+%% \pagebreak
 \end{publications}

### 2023-09-23 spanish/sections/reviewer.tex
Update reviewer.tex
LPPL v1.3c

@@
 
-\cvsection{Revisiones como árbitro \& experto}
+\cvsection{Revisiones como árbitro, experto \& comités}
 
@@
 \begin{itemize}
-\item{\small Proyecto V-Dem, Universidad de Gotemburgo, Suecia, 2014, 2018-2020}
-\item{\small Encuesta de Reputación Académica Global, Clarivate Analytics, EUA, 2020}
-\item{\small Comisión Sectorial de Investigación, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
-\item{\small Times Higher Education Ranking, {\scshape Elsevier}, Países Bajos, 2018-2019, 2022}
-\item{\small Revisor en revistas {\scshape WoS-ISI/SSCI/ESCI} \& {\scshape Scopus}, desde 2013}
-\item{\small Revisor en revistas {\scshape SciELO} \& {\scshape Latindex}, desde 2013}
+\item{\small Editor Asociado en {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape desde} 2016}
+\item{\small Editor en {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape desde} 2020}
+\item{\small Moderador en {\itshape SocArXiv}, University of Maryland, USA, {\itshape desde} 2023}
+\item{\small Red de Expertos por la Transparencia, Fundación Panamericana para el Desarrollo, ECU, {\itshape desde} 2022}
+\item{\small Magíster en Gerencia y Políticas Públicas, Universidad de Santiago de Chile (USACH), CHL, {\itshape desde} 2022}
+\item{\small Revisor en revistas {\scshape WoS-SSCI}, {\scshape Scopus} \& {\scshape WoS-ESC}, {\itshape desde} 2013}
+\item{\small Revisor en revistas {\scshape SciELO} \& {\scshape Latindex}, {\itshape desde} 2013}
+\item{\small Times Higher Education Ranking, {\scshape Elsevier}, NLD, 2018, 2019, 2022-2023}
+\item{\small Proyecto V-Dem, Universidad de Gotemburgo, SWE, 2014, 2018-2020}
+\item{\small Encuesta de Reputación Académica Global, Clarivate Analytics, USA, 2020}
+\item{\small Comisión Sectorial de Investigación, Universidad de la República, URY, 2016, 2018}
 \end{itemize}

### 2023-09-23 sections/selected-training.tex
Update selected-training.tex
LPPL v1.3c

@@
 {Research Data Workshop IT Centre at the University of Oxford} 
-{Oxford, UK}
+{Oxford, GBR}
 {2019}
@@
 {Longitudinal Networks with RSiena Workshop at the P Universidad Cat\'olica}
-{Santiago, Chile}
+{Santiago, CHL}
 {2018}
@@
 {Universidad de Santiago Winter School for Academics}
-{Santiago, Chile}
+{Santiago, CHL}
 {2016}
@@
 {Nuffield-USACH CEES Experimental Summer School}
-{Santiago, Chile}
+{Santiago, CHL}
 {2016}
@@
 {Universidad de Santiago Winter School for Academics}
-{Santiago, Chile}
+{Santiago, CHL}
 {2015}
@@
 {Latin American Political Science Association Methodological School}
-{Lima, Peru}
+{Lima, PER}
 {2015}
@@
 \cvconf
-{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
-{MVD, Uruguay}
+{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
+{Montevideo, URY}
 {2015}
@@
 \cvconf
-{P Universidad Ca\'olica Summer School in Mixed Methods}
-{Santiago, Chile}
+{P Universidad Caólica Summer School in Mixed Methods}
+{Santiago, CHL}
 {2014}

### 2023-09-23 sections/deprecated/training.tex
Create training.tex
Update training.tex

--- 2020-08-21 spanish/sections/training.tex
@@
 {Training in geospatial modelling} 
-{Oxford, UK}
+{Oxford, GBR}
 {2020}
@@
 {Training in formal analysis and game theory, randomised trials, regression and matching, instrumental variables, regression discontinuity, differences-in-differences, and placebo tests} 
-{Oxford, UK}
+{Oxford, GBR}
 {2020}
@@
 {Training in managing research data} 
-{Oxford, UK}
+{Oxford, GBR}
 {2019}
@@
 {Training in research design, logit and OLS models, multinomial models, ordinal logistic regressions,  OLS regularisation and cross-validation procedures, shrinkage methods, regression tree, random forest algorithm, principal component analysis based on unsupervised learning, and count models}
-{Oxford, UK}
+{Oxford, GBR}
 {2019}
@@
 {Training in stochastic actor oriented models in R}
-{Santiago, Chile}
+{Santiago, CHL}
 {2018}
@@
 {Training in evaluation techniques and teaching strategies for academic writing}
-{Santiago, Chile}
+{Santiago, CHL}
 {2016}
@@
 {Training in experiments in social sciences}
-{Santiago, Chile}
+{Santiago, CHL}
 {2016}
@@
 {Training in qualitative data analysis in {\scshape atlas}.ti}
-{Santiago, Chile}
+{Santiago, CHL}
 {2015}
@@
 {Training in programming in Python, social network analysis in R and Python, and qualitative comparative analysis in R}
-{Lima, Peru}
+{Lima, PER}
 {2015}
@@
 \cvhonor
-{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
+{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
 {Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
@@
 \cvhonor
-{Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
+{Pontificia Universidad Católica Summer School in Mixed Methods}
 {Training in set theory and logic, case studies and multi-methods, process tracing, and experiments in social sciences}
-{Santiago, Chile}
+{Santiago, CHL}
 {2014}

### 2023-09-23 sections/deprecated/training.tex
Update training.tex

@@
 {Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
-{Montevideo, Uruguay}
+{Montevideo, URY}
 {2015}

### 2023-09-23 spanish/sections/deprecated/training.tex
Create training.tex

--- 2023-09-23 sections/deprecated/training.tex
@@
 \cvhonor
-{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
+{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
 {Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
@@
 \cvhonor
-{Pontificia Universidad Católica Summer School in Mixed Methods}
+{Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
 {Training in set theory and logic, case studies and multi-methods, process tracing, and experiments in social sciences}

### 2023-09-23 spanish/sections/languages.tex
LPPL v1.3c
Update languages.tex

@@
 {Idiomas} 
-{Español (hablante nativo), inglés (fluido), portugués (habilidades de lectura avanzadas),}
+{\textcolor{black}{Español (hablante nativo), inglés (fluido), portugués (habilidades de lectura avanzadas),}}
 
@@
 {} 
-{francés (habilidades de lectura elementales)} \\
+{\textcolor{black}{italiano (habilidades de lectura elementales), francés (habilidades de lectura elementales)}} \\
 
@@
 {Programación \&} 
-{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}
+{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}
 
@@
 {software} 
-{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}} \\
+{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
 

### 2023-09-23 sections/languages.tex
Update languages.tex

@@
 {Languages} 
-{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}
+{\textcolor{black}{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}}
 
@@
 {} 
-{(elemental reading skills), French (elemental reading skills)} \\
+{\textcolor{black}{(elemental reading skills), French (elemental reading skills)}} \\
 
@@
 {Programming \&} 
-{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}
+{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}
 
@@
 {Software} 
-{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}} \\
+{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
 

### 2023-09-23 sections/papers.tex
Update papers.tex

--- 2023-09-22 sections/papers.tex
@@
 
-\item{\small Cuevas, C.
+%% \item{Cuevas, C.
 {\itshape et al.} (2021).
@@
 
-\item{\small González-Bustamante, B.
+\item{Cuevas, C.
+et al.
+(2021).
+Motivación de servicio público entre funcionarios públicos chilenos.
+{\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
+{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2020).
@@
 
-\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
+%% \item{González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., Carvajal, A., \& González, A.
+(2020).
+Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno.
+{\itshape Gestión y Política Pública, XXIX}(1), 97--129.
+{\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2019).
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+\item{González-Bustamante, B.
+(2019).
+Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, 80, 1--27.
+{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
+
+%% \item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
@@
 
+\item{González-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010.
+{\itshape Política y Gobierno, XXV}(1), 31--64.
+{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+
 \end{benumerate}
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
 
-\item{\small Cisternas, C., \& González-Bustamante, B.
+\item{González-Bustamante, B., \& Aguilar, D.
+(2023).
+Territorial patterns of open e-government: evidence from Chilean municipalities.
+{\itshape Political Research Exchange, 5}(1).
+{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+
+%% \item{Cisternas, C., \& González-Bustamante, B.
 (2022).
@@
 
-\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+\item{Cisternas, C., \& González-Bustamante, B.
+(2022).
+Ciencias sociales en contextos de represión: Análisis bibliométrico de la producción histórica de la Corporación de Estudios para Latinoamérica, Chile (1979-1989).
+{\itshape e-Ciencias de la Información, 12}(2), 1--18.
+{\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
+
+%% \item{González-Bustamante, B., Astete, M., \& Orvenes, B.
 (2020).
@@
 
-\item{\small Olivares, A.
+\item{González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2020).
+Altos directivos públicos: Un nuevo conjunto de datos de miembros del servicio civil chileno.
+{\itshape Revista de Gestión Pública, IX}(2), 151--169.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
+
+%% \item{Olivares, A.
 {\itshape et al.} (2020).
@@
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{Olivares, A.
+et al.
+(2020).
+Nuevos desafíos, enfoques y perspectivas para estudiar élites políticas.
+{\itshape Iberoamericana, XX}(74), 229--259.
+{\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
+
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2019).
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
+%% \item{Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2019).
@@
 
-\item{\small Del Valle, N., \& González-Bustamante, B.
+\item{Barría, D., González-Bustamante, B., \& Cisternas, C.
+(2019).
+La literatura sobre gobierno abierto en español.
+Análisis sobre las dinámicas de producción y citación.
+{\itshape Nóesis.
+Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
+{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
+
+%% \item{Del Valle, N., \& González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{Del Valle, N., \& González-Bustamante, B.
+(2018).
+Agenda política, periodismo y medios digitales en Chile: Notas de investigación sobre pluralismo informativo.
+{\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
+{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Olivares, A.
+(2016).
+Cambios de gabinete y supervivencia de los ministros en Chile durante los gobiernos de la Concertación (1990-2010).
+{\itshape Colombia Internacional}, 87, 81--108.
+{\scshape doi}: \\ \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 {\itshape et al.} (2016).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B.
+et al.
+(2016).
+Servicio civil en Chile, análisis de los directivos de primer nivel jerárquico (2003-13).
+{\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
+{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Olivares, A.
 (2015).
@@
 {\scshape doi:} \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
+
+\item{González-Bustamante, B., \& Olivares, A.
+(2015).
+Rotación de subsecretarios en Chile: Una exploración de la segunda línea gubernamental, 1990-2014.
+{\itshape Revista de Gestión Pública, IV}(2), 151--190.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
 
@@
 
-\item{\small González-Bustamante.
+%% \item{González-Bustamante.
 B.
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante.
+B.
+(2022).
+Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
+{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., \& Luci, F.
+\item{González-Bustamante, B.
+(2021).
+Sofisticación, participación y compromiso político en América Latina.
+{\itshape Tufte Working Papers}, 2, 1--21.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Luci, F.
 (2021).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Luci, F.
+(2021).
+Élites políticas en América Latina: Socialización, trayectorias y capitales.
+{\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28.
+21--32.
+{\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
+\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B.
+(2021).
+Hibridación digital en el Cono Sur: Consumo de medios tradicionales, digitales y uso de redes sociales.
+{\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
+\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Cisternas, C.
 (2020).
@@
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B., \& Cisternas, C.
+(2020).
+Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continuo, para el estudio de las élites.
+{\itshape Tufte Working Papers}, 1, 1--15.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Cisternas, C.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Cisternas, C.
+(2016).
+Élites políticas en el poder legislativo chileno: la Cámara de Diputados (1990-2014).
+{\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2016).
+Élites políticas, económicas e intelectuales: una agenda de investigación creciente para la ciencia política.
+{\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
+{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2015).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2015).
+Éxito electoral y gasto en campaña en las elecciones de senadores y diputados en Chile 2013.
+{\itshape Políticas Públicas, 8}(1), 21--35.
+{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2015).
@@
 
-\item{\small Olivares, A.
+\item{González-Bustamante, B.
+(2015).
+Evaluando Twitter como indicador de opinión pública: una mirada al arribo de Bachelet a la presidencial chilena 2013.
+{\itshape Revista SAAP, 9}(1), 119--141.
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+
+%% \item{Olivares, A.
 {\itshape et al.} (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{Olivares, A.
+et al.
+(2014).
+Los think tanks en el gabinete: una exploración del caso chileno (2006-2014).
+{\itshape Revista de Sociología,} 29, 37--54.
+{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2014).
+Elección directa de consejeros regionales 2013.
+Rendimiento del capital político, familiar y económico en una nueva arena electoral en Chile.
+{\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2013).
+El estudio de las élites en Chile: aproximaciones conceptuales y metodológicas.
+{\itshape Intersticios Sociales,} 6, 1--20.
+{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+\item{González-Bustamante, B.
+(2013).
+Factores de acceso y permanencia de la élite política gubernamental en Chile (1990-2010).
+{\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
+{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
+
+%% \item{González-Bustamante, B., \& Henríquez, G.
 (2012).
@@
 
+\item{González-Bustamante, B., \& Henríquez, G.
+(2012).
+Campañas digitales: ¿Branding o participación política?
+{\itshape Más Poder Local,} 12, 32--39.
+{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
+
 \end{benumerate}

### 2023-09-23 sections/book-chapters.tex
Update book-chapters.tex

--- 2022-10-17 sections/book-chapters.tex
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+%% \item{González-Bustamante, B., \& Olivares, A.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Barría, D.
+\item{González-Bustamante, B., \& Olivares, A.
+(2018).
+La élite política gubernamental en Chile: supervivencia de ministros.
+In A.
+Codato \& F.
+Espinoza (eds.), {\itshape Las élites en las Américas: diferentes perspectivas} (pp.
+245--282).
+Curitiba: Editora da Universidade Federal do Paraná.
+{\scshape url:} \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Barría, D.
 (2018).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Barría, D.
+(2018).
+Expansión de la esfera pública en Chile: Redes sociales, campañas electorales y participación digital.
+In N.
+Del Valle (ed.), {\itshape Transformaciones de la esfera pública en Chile.
+Luchas sociales, espacio público y pluralismo informativo} (pp.
+99--116).
+Santiago: RIL Editores.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Araya, J.
-E.
+\item{González-Bustamante, B.
+(2018).
+Internet, uso de redes sociales digitales y participación en el Cono Sur.
+In P.
+Cottet (ed.), {\itshape Opinión pública contemporánea: otras posibilidades de comprensión e investigación} (pp.
+113--137).
+Santiago: Social-Ediciones.
+{\scshape doi:} \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}.}\vspace{1mm}
+
+%% \item{Barría, D., González-Bustamante, B., \& Araya, E.
 (2017).
@@
 
-\item{\small González-Bustamante, B., \& Sazo, D.
+\item{Barría, D., González-Bustamante, B., \& Araya, E.
+(2017).
+Democracia electrónica y participación digital.
+Avances y desafíos.
+In J.
+R.
+Gil-García, J.
+I.
+Criado \&  J.
+C.
+Téllez (eds.), {\itshape Tecnologías de Información y Comunicación en la Administración P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados} (pp.
+351--380).
+Mexico City: INFOTEC.
+{\scshape url:} \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Sazo, D.
 (2016).
@@
 
-\item{\small González-Bustamante, B., \& Sazo, D.
+\item{González-Bustamante, B., \& Sazo, D.
+(2016).
+Campaña viral.
+In I.
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+68--70).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Sazo, D.
 (2016).
@@
 In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política} (pp.
+48--50).
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Sazo, D.
+(2016).
+Imagen de marca para un candidato o gobierno (branding político).
+In I.
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+48--50).
+Madrid: Centro de Estudios.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2016).
@@
 In I.
-Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política}.
+Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política} (pp.
+378--380).
 Madrid: Centro de Estudios Políticos y Constitucionales.
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2016).
+Twitter (su uso en la comunicación política).
+In I.
+Crespo et al.
+(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+378--380).
+Madrid: Centro de Estudios Políticos y Constitucionales.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2014).
+Nuevos medios y política digital: El caso de las primarias presidenciales chilenas de 2013.
+In G.
+Sibaja (ed.), {\itshape Nuevos  medios y comunicación política digital} (pp.
+227--246).
+San José: Fundación Educativa San Judas Tadeo.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2014).
+Activismo digital, redes sociales e intermediación.
+In S.
+Millaleo \& P.
+C\'arcamo (eds.), {\itshape Mediaciones del  sistema político frente al activismo digital} (pp.
+77--101).
+Santiago: Fundación Democracia y Desarrollo.
+{\scshape url:} \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 In O.
-Avilés {\itshape et al.} (eds.), {\itshape Práctica Política y Medios Digitales}.
+Avilés {\itshape et al.} (eds.), {\itshape Práctica política y medios digitales} (pp.
+77--98).
 Santiago: Instituto Igualdad.
@@
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+\item{González-Bustamante, B.
+(2014).
+Redes sociales como herramienta para la práctica política: Twitter y el concepto de opinión pública.
+In O.
+Avilés et al.
+(eds.), {\itshape Práctica política y medios digitales} (pp.
+77--98).
+Santiago: Instituto Igualdad.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Henríquez, G.
 (2013).
@@
 Crespo \& J.
-del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina}.
+del Rey (eds.), {\itshape Comunicación Política \& Campa\~nas Electorales en América Latina} (pp 285--296).
 Buenos Aires: Editorial Biblos.
 {\footnotesize \scshape [in Spanish].}}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Henríquez, G.
+(2013).
+Chile: la campaña digital 2009-2010.
+In I.
+Crespo \& J.
+del Rey (eds.), {\itshape Comunicación Política \& Campañas Electorales en América Latina} (pp 285--296).
+Buenos Aires: Editorial Biblos.}\vspace{1mm}
 

### 2023-09-23 sections/book-chapters.tex
Update book-chapters.tex

@@
 In I.
-Crespo et al.
-(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+Crespo, O.
+D'Adamo, V.
+García Beaudoux \& A.
+Mora (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
 68--70).
@@
 In I.
-Crespo et al.
-(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+Crespo, O.
+D'Adamo, V.
+García Beaudoux \& A.
+Mora (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
 48--50).
@@
 In I.
-Crespo et al.
-(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
+Crespo, O.
+D'Adamo, V.
+García Beaudoux \& A.
+Mora (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2nd edition} (pp.
 378--380).
@@
 In O.
-Avilés et al.
-(eds.), {\itshape Práctica política y medios digitales} (pp.
+Avilés, R.
+Cárcamo, J.
+Illanes, B.
+Jul \& T.
+Laibe (eds.), {\itshape Práctica política y medios digitales} (pp.
 77--98).
@@
 \end{publications}
-%% \pagebreak
+\pagebreak

### 2023-09-23 sections/papers.tex
Update papers.tex

@@
 
-\item{Cuevas, C.
-et al.
+\item{Cuevas, C., González-Bustamante, B., Calderón-Orellana, M., \& Barría, D.
 (2021).
@@
 
-\item{Olivares, A.
-et al.
+\item{ Olivares, A., González-Bustamante, B., Toro, S., Arellano, J.
+C., Yanes-Rojas, A., Zurita-Tapia, J., Lopes, A.
+V., Robledo Guzmán, C., \& Canavesi Sosa, J.
+B.
 (2020).
@@
 
-\item{González-Bustamante, B.
-et al.
+\item{González-Bustamante, B., Olivares, A., Abarca, P., \& Molina, E.
 (2016).
@@
 
-\item{Olivares, A.
-et al.
+\item{Olivares, A., González-Bustamante, B., Meneses, J., \& Rodríguez, M.
 (2014).
@@
 {\itshape Revista de Sociología,} 29, 37--54.
-{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+{\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
 

### 2023-09-23 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 Territorial patterns of open e-government: evidence from Chilean municipalities.
-{\itshape Political Research Exchange, 5}(1), 2194369.
+{\itshape Political Research Exchange, 5}(1).
 {\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+%% \item{González-Bustamante, B., Astete, M., \& Orvenes, B.
 (2020).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2020).
+Altos directivos públicos: Un nuevo conjunto de datos de miembros del servicio civil chileno.
+{\itshape Revista de Gestión Pública, IX}(2), 151--169.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
 (2020).
@@
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., Carvajal, A., \& González, A.
+(2020).
+Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno.
+{\itshape Gestión y Política Pública, XXIX}(1), 97--129.
+{\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
+
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2019).
@@
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2019).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2019).
+Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
+{\itshape Convergencia.
+Revista de Ciencias Sociales}, 80, 1--27.
+{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
+
+\item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+%% \item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
@@
 
+\item{González-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010.
+{\itshape Política y Gobierno, XXV}(1), 31--64.
+{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+
 \end{itemize}

### 2023-09-23 spanish/sections/book-chapters.tex
Update book-chapters.tex

@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Barría, D.
+\item{González-Bustamante, B., \& Barría, D.
 (2018).
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Araya, E.
+\item{Barría, D., González-Bustamante, B., \& Araya, E.
 (2017).
@@
 
-\item{\small González-Bustamante, B., \& Sazo, D.
+\item{González-Bustamante, B., \& Sazo, D.
 (2016).
@@
 En I.
-Crespo et al.
-(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
+Crespo, O.
+D`Adamo, V.
+García Beaudoux \& A.
+Mora (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
 68--70).
@@
 En I.
-Crespo et al.
-(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
+Crespo, O.
+D`Adamo, V.
+García Beaudoux \& A.
+Mora (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
 48--50).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2016).
@@
 En I.
-Crespo et al.
-(eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
+Crespo, O.
+D`Adamo, V.
+García Beaudoux \& A.
+Mora (eds.), {\itshape Diccionario Enciclopédico de Comunicación Política, 2da edición} (pp.
 378--380).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2014).
@@
 En O.
-Avilés et al.
-(eds.), {\itshape Práctica política y medios digitales} (pp.
+Avilés, R.
+Cárcamo, J.
+Illanes, B.
+Jul \& T.
+Laibe (eds.), {\itshape Práctica política y medios digitales} (pp.
 77--98).
@@
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+\item{González-Bustamante, B., \& Henríquez, G.
 (2013).

### 2023-09-23 spanish/sections/papers.tex
Update papers.tex

@@
 
-\item{\small Cuevas, C.
-et al.
+\item{Cuevas, C., González-Bustamante, B., Calderón-Orellana, M., \& Barría, D.
 (2021).
@@
 {\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
-{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+{\scshape url:} \\ \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
 {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
+\item{González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2019).
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+\item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Aguilar, D.
+\item{González-Bustamante, B., \& Aguilar, D.
 (2023).
@@
 
-\item{\small Cisternas, C., \& González-Bustamante, B.
+\item{Cisternas, C., \& González-Bustamante, B.
 (2022).
@@
 
-\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+\item{González-Bustamante, B., Astete, M., \& Orvenes, B.
 (2020).
@@
 
-\item{\small Olivares, A.
-et al.
+\item{Olivares, A., González-Bustamante, B., Toro, S., Arellano, J.
+C., Yanes-Rojas, A., Zurita-Tapia, J., Lopes, A.
+V., Robledo Guzmán, C., \& Canavesi Sosa, J.
+B.
 (2020).
@@
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2019).
@@
 
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
+\item{Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2019).
@@
 
-\item{\small Del Valle, N., \& González-Bustamante, B.
+\item{Del Valle, N., \& González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
-et al.
+\item{González-Bustamante, B., Olivares, A., Abarca, P., \& Molina, E.
 (2016).
@@
 {\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
-{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
+{\scshape doi}: \\ \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2015).
@@
 
-\item{\small González-Bustamante.
+\item{González-Bustamante.
 B.
@@
 
-\item{\small González-Bustamante, B., \& Luci, F.
+\item{González-Bustamante, B., \& Luci, F.
 (2021).
@@
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B., \& Cisternas, C.
 (2020).
@@
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B., \& Cisternas, C.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2015).
@@
 
-\item{\small Olivares, A.
-et al.
+\item{Olivares, A., González-Bustamante, B., Meneses, J., \& Rodríguez, M.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+\item{González-Bustamante, B., \& Henríquez, G.
 (2012).

### 2023-09-23 sections/conferences-full.tex
Update conferences-full.tex

--- 2022-07-19 sections/conferences-full.tex
@@
 
-\begin{benumerate}{74}
+\begin{benumerate}{87}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Corrective Effect of Ministerial Terminations on Presidential Approval}.
+Presentation delivered at the ECPR General Conference (ECPR), Charles University, Prague, Czech Republic.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Data Mining and Machine Learning for Political Events: An Application to Produce Indicators for Presidential Systems}.
+Presentation delivered at the ECPR General Conference (ECPR), Charles University, Prague, Czech Republic.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape The Impact of Ministers' Profiles on Cabinet Turnover during Presidential Crises}.
+Presentation delivered at the XXVII World Congress of Political Science (IPSA), Buenos Aires, Argentina.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Corrective Effect of Ministerial Terminations on Presidential Approval}.
+Presentation delivered at the Political Studies Association Early Career Network Annual Conference ``Political Worlds'' (PSA-ECN), Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Propensity score matching para datos observacionales}.
+Presentation delivered at the Doctorate in Social Complexity Sciences, Universidad del Desarrollo, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Quantitative Methods for Studying Elites: Ministers' Profiles and Cabinet Turnover in Presidential Crises}.
+Presentation delivered at the Workshop Elites and Class -- Interrogating the Rich and Powerful in Latin America and Beyond, University of Kassel, Kassel, Alemania.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Técnicas de propensión y algoritmos de emparejamiento para datos observacionales}.
+Presentation delivered at the Fundación Analítica's Monthly Workshops, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Resignation Calls and Ministerial Turnover in Presidential Systems}.
+Presentation delivered at the European Consortium for Political Research Joint Sessions of Workshops (ECPR), Institut d'Études Politiques de Toulouse, Toulouse, France.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Resignation Calls, Reallocations and Individual Ministerial Terminations in Latin America}.
+Presentation delivered at the 73rd Political Studies Association Annual International Conference (PSA), Liverpool, United Kingdom.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+{\itshape Resignation Calls, Reallocations and Individual Ministerial Terminations in Latin America}.
+Presentation delivered at the Society for Latin American Studies Annual Conference (SLAS), Belfast, United Kingdom.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
+(2022).
+{\itshape Machine Learning and Political Events: Application of Semisupervised Approach to Produce a Data Set on Latin American Cabinets}.
+Presentation delivered at the II Training Data Lab Workshop, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2022).
+{\itshape Aprendizaje automático y eventos políticos: Aplicación de un enfoque semisupervisado para producir un conjunto de datos sobre gabinetes latinoamericanos}.
+Presentation delivered at the II Training Data Lab Workshop, Virtual.}\vspace{1mm}
 
@@
 {\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}.
-Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}
+Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich, Switzerland.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
+(2022).
+{\itshape Machine Learning for the Study of Political Events: Application of Semisupervised Models on Latin American Archives}.
+Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2022).
+{\itshape Aprendizaje automático para el estudio de eventos políticos: Aplicación de modelos semisupervisados en archivos de América Latina}.
+Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Aguilar, D.
+(2022).
+{\itshape Integrated Repository on Local Government Indicators in Chile}.
+Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}
 
@@
 (2022).
-{\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Local Governments}.
-Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid.}\vspace{1mm}
+{\itshape Repositorio integrado de indicadores de gobiernos locales en Chile}.
+Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Aguilar, D.
+(2022).
+{\itshape Territorial Patterns of Open E-Government: Evidence from Chilean Municipalities}.
+Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid, Spain}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2022).
@@
 
-\item{\small González-Bustamante, B., \& Aguilar, D.
+\item{González-Bustamante, B.
+(2022).
+{\itshape Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades}.
+Presentation delivered at the XI Latin American Congress of Political Science (ALACIP), Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Aguilar, D.
 (2022).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Aguilar, D.
+(2022).
+{\itshape Patrones territoriales en el desarrollo digital y el gobierno abierto: Evidencia de los municipios chilenos}.
+Presentation delivered at the XI Latin American Congress of Political Science (ALACIP), Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
 (2022).
 {\itshape Ministerial Stability During Presidential Approval Crises: Evidence from Brazil and Chile}.
-Presentation delivered at the Political Studies Association Early Career Network Annual Conference, Sheffield, UK.}\vspace{1mm}
+Presentation delivered at the Political Studies Association Early Career Network Annual Conference ``The Time is Now'' (PSA-ECN), Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2022).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2022).
 {\itshape Resignation Calls and Dismissals of Ministers in Latin America: Data Gathering using NLP and Machine Learning}.
-Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
+Presentation delivered at the XXXIX International Congress of the Latin American Studies Association (LASA), Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2022).
 {\itshape Insights of a Number of Ongoing Research on Elites in Latin America: Topics, Methods and Possibilities for Comparison}.
-Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
+Presentation delivered at the XXXIX International Congress of the Latin American Studies Association (LASA), Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2022).
 {\itshape Resignation Calls and Ministerial Turnover in Latin America: Notes on Data Gathering using Machine Learning}.
-Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}
+Presentation delivered at the Society for Latin American Studies Annual Conference (SLAS), Bath, United Kingdom.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B., \& Cisternas, C.
 (2022).
 {\itshape Seniority and Cosponsorship in the Chilean Lower House 2006-2018}.
-Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}
+Presentation delivered at the Society for Latin American Studies Annual Conference (SLAS), Bath, United Kingdom.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2021).
+{\itshape El uso de machine learning para la investigación en asuntos públicos}.
+Presentation delivered the XII Chilean Congress of Public Administration, Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small Fleming, T.
+\item{González-Bustamante, B.
+(2021).
+{\itshape Desafíos metodológicos e innovaciones en el estudio de las élites}.
+Presentation delivered at the XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences (ANPOCS), Virtual.}\vspace{1mm}
+
+\item{Fleming, T.
 G., González-Bustamante, B., \& Schleiter, P.
@@
 {\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}.
-Presentation delivered at the Otto-Friedrich-Universität Bamberg Workshop, Virtual.}\vspace{1mm}
+Presentation delivered at the Workshop on Coalition Politics and Portfolio Design, University of Bamberg, Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2021).
 {\itshape R Applications in Social Sciences: Data Mining and Econometric Modelling}.
-Presentation delivered at the Political Science Method Lecture at the Universidad de Chile, Virtual.}\vspace{1mm}
+Presentation delivered at the Political Science Method Lecture, Universidad de Chile, Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2021).
+{\itshape Aplicaciones de R en ciencias sociales: Minería de datos y modelamiento econométrico}.
+Presentation delivered at the Political Science Method Lecture, Universidad de Chile, Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2021).
 {\itshape Vertically Integrated Project: Machine Learning Applications in Public Policy and Economics}.
-Presentation delivered at the VIP Project Workshop at the Universidad Mayor, Virtual.}\vspace{1mm}
+Presentation delivered at the VIP Project Workshop, Universidad Mayor, Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2021).
+{\itshape Aplicaciones de Machine Learning en políticas públicas y economía}.
+Presentation delivered at the VIP Project Workshop, Universidad Mayor, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
 (2021).
 {\itshape Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile}.
-Presentation delivered at the XXVI World Congress of Political Science, Virtual.}\vspace{1mm}
+Presentation delivered at the XXVI World Congress of Political Science (IPSA), Virtual.}\vspace{1mm}
 
-\item{\small Cisternas, C., \& González-Bustamante, B.
+\item{Cisternas, C., \& González-Bustamante, B.
 (2021).
 {\itshape Political Careers and Co-Sponsorship in the Chilean Lower House 2010-2018}.
-Presentation delivered at the XXVI World Congress of Political Science, Virtual.}\vspace{1mm}
+Presentation delivered at the XXVI World Congress of Political Science (IPSA), Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2021).
+{\itshape Aplicaciones de data mining, modelamiento y machine learning para ciencias sociales}.
+Presentation delivered at the I Training Data Lab Workshop, Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2020).
 {\itshape Evolution and Early Governmental Responses to COVID-19 in South America}.
-Presentation delivered at the Workshop of the School of Political Science and Public Administration at the Universidad de Talca, Virtual.}\vspace{1mm}
+Presentation delivered at the Workshop of the School of Political Science and Public Administration, Universidad de Talca, Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2020).
+{\itshape Evolución y respuestas gubernamentales tempranas al COVID-19 en América del Sur}.
+Presentation delivered at the Workshop of the School of Political Science and Public Administration, Universidad de Talca, Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
+(2020).
+{\itshape New Approaches to Studying Political Elites}.
+Presentation delivered at the Colloquium of the Observatório de Elites, Universidade Federal do Paraná, Virtual.}\vspace{1mm}
 
@@
 (2020).
-{\itshape New Approaches to Studying Political Elites}.
-Presentation delivered at the Colloquium of the Observatório de Elites at the Universidade Federal do Paraná, Virtual.}\vspace{1mm}
+{\itshape Nuevos enfoques para estudiar élites políticas}.
+Presentation delivered at the Colloquium of the Observatório de Elites, Universidade Federal do Paraná, Virtual.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2020).
 {\itshape Protest and Social Unrest in Latin America: Determinants and Critical Junctures}.
-Presentation delivered at the Seminar Cycle on Human Rights in Latin America at the Universidade Tiradentes, Virtual.}\vspace{1mm} %% Sergipe, Brazil
+Presentation delivered at the Seminar Cycle on Human Rights in Latin America, Universidade Tiradentes, Virtual.}\vspace{1mm} %% Sergipe, Brazil
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2020).
+{\itshape Protesta y malestar social en América Latina: Determinantes y coyunturas críticas}.
+Presentation delivered at the Seminar Cycle on Human Rights in Latin America, Universidade Tiradentes, Virtual.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2020).
 {\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}.
-Presentation delivered at the PRS DPhil in Politics Workshop in Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}
+Presentation delivered at the Pembroke College PRS DPhil in Politics Workshop, University of Oxford, Oxford, UK.}\vspace{1mm}
 
-\item{\small Orchard, X., \& González-Bustamante, B.
+\item{González-Bustamante, B.
+(2020).
+{\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}.
+Presentation delivered at the Pembroke College Workshop, University of Oxford, Oxford, United Kingdom.}\vspace{1mm}
+
+%% \item{Orchard, X., \& González-Bustamante, B.
 (2020).
@@
 
-\item{\small González-Bustamante, B.
+\item{Orchard, X., \& González-Bustamante, B.
+(2020).
+{\itshape Una exploración de perfiles y percepciones en el diagnóstico sobre la práctica periodística en Chile}.
+Presentation delivered at the VI Chilean Association of Communication Researchers Congress (INCOM), Virtual.}\vspace{1mm}
+
+\item{González-Bustamante, B.
 (2019).
 {\itshape Presidential Stability and Minister Turnover in Argentina, Brazil, and Chile}.
-Presentation delivered at the XXXVII International Congress of the Latin American Studies Association, Boston, USA.}\vspace{1mm}
+Presentation delivered at the XXXVII International Congress of the Latin American Studies Association (LASA), Boston, United States.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2018).
 {\itshape Cabinet Stability and Turnover from a Multilevel Approach}.
-Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B.
+(2018).
+{\itshape Supervivencia de ministros y viceministros en Chile: Estabilidad y rotación en una lógica multinivel}.
+Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Cisternas, C.
 (2018).
 {\itshape Social Network Analysis: Application for Elites Study}.
-Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Cisternas, C.
+(2018).
+{\itshape ForceAtlas2, un algoritmo de diseño gráfico continuo: Aplicación para el estudio de las élites}.
+Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2018).
+{\itshape Análisis geoespacial de la densidad partidista y la participación electoral: Evidencia del caso chileno}.
+Presentation delivered at the XIII Chilean Congress of Political Science (ACCP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2018).
+{\itshape Sofisticación, participación y compromiso político en América Latina}.
+Presentation delivered at the VII International Congress of Political Communication (ALICE), Murcia, Spain.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+\item{González-Bustamante, B.
+(2018).
+{\itshape Supervivencia de ministros y viceministros en Chile: Estabilidad y rotación en una lógica multinivel}.
+Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics, Universidade Federal do Paraná, Curitiba, Brazil.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
 {\itshape Trajectories and Post-Career of Ministers in Chile}.
-Presentation delivered at the Research Seminar of the Institute of Public Affairs at the Universidad de Chile, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Research Seminar of the Institute of Public Affairs, Universidad de Chile, Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Del Valle, N.
+\item{González-Bustamante, B., \& Garrido-Vergara, L.
+(2018).
+{\itshape Trayectorias y poscarrera de ministros en Chile}.
+Presentation delivered at the Research Seminar of the Institute of Public Affairs, Universidad de Chile, Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Del Valle, N.
 (2017).
 {\itshape Media Pluralism and Digital Media Public Opinion}.
-Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile at the Universidad Alberto Hurtado, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile, Universidad Alberto Hurtado, Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A.
+\item{González-Bustamante, B., \& Del Valle, N.
+(2017).
+{\itshape Pluralismo informativo y opinión pública en los medios digitales escritos}.
+Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile: Challenges for the Democratisation of Communications, Universidad Alberto Hurtado, Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., Maillet, A., \& Olivares, A.
 (2017).
@@
 Analysis of Public-Private Circulation in Chile}.
-Presentation delivered at the II Foreign Affairs Meeting at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the II Foreign Affairs Meeting, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+\item{González-Bustamante, B., Maillet, A., \& Olivares, A.
+(2017).
+{\itshape ?`Puerta giratoria?
+Análisis de la circulación público-privada en Chile}.
+Presentation delivered at the II Foreign Affairs Meeting, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2017).
@@
 
-\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A.
+\item{González-Bustamante, B., \& Garrido-Vergara, L.
+(2017).
+{\itshape Espacios de socialización, carrera y postcarrera ministerial en la transición y post-transición chilena}.
+Presentation delivered at the IX Chilean Congress of Public Administration, Concepcion, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., Maillet, A., \& Olivares, A.
 (2017).
@@
 
-\item{\small González-Bustamante, B., \& Joignant, A.
+\item{González-Bustamante, B., Maillet, A., \& Olivares, A.
+(2017).
+{\itshape Público-privado: una frontera muy porosa.
+Trayectorias político-profesionales de autoridades en Chile (2000-2014)}.
+Presentation delivered at the IX Latin American Congress of Political Science (ALACIP), Montevideo, Uruguay.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Joignant, A.
 (2016).
 {\itshape Gaps and Elite-Mass Congruence in Chile and Uruguay}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small Joignant, A., \& González-Bustamante, B.
+\item{González-Bustamante, B., \& Joignant, A.
+(2016).
+{\itshape Brechas y congruencia élite-ciudadanía en Chile y Uruguay}.
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{Joignant, A., \& González-Bustamante, B.
 (2016).
 {\itshape Family Ties in the Senate and the Chamber of Deputies, Chile from 1989 to 2014}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
+\item{Joignant, A., \& González-Bustamante, B.
+(2016).
+{\itshape Lazos familiares en el Senado y la Cámara de Diputados, Chile 1989-2014}.
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2016).
 {\itshape Analysis of the Academic Production on Open Government in Spanish}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{Barría, D., González-Bustamante, B., \& Cisternas, C.
+(2016).
+{\itshape Análisis de la producción académica en español sobre gobierno abierto}.
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2016).
 {\itshape Revolving Door and Public-Private Circulation in Chile}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
 
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
+(2016).
+{\itshape Puerta giratoria y circulación público-privada en Chile}.
+Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Universidad de Santiago de Chile (USACH), Santiago, Chile.}\vspace{1mm}
+
+%% \item{Barría, D., González-Bustamante, B., \& Cisternas, C.
 (2016).
@@
 
-\item{\small Joignant, A., \& González-Bustamante, B.
+\item{Barría, D., González-Bustamante, B., \& Cisternas, C.
+(2016).
+{\itshape Gobierno abierto en América Latina y España: Análisis de la producción en español sobre el tema}.
+Presentation delivered at the XXI CLAD International Congress on the State Reform and Public Administration, Santiago, Chile.}\vspace{1mm}
+
+%% \item{Joignant, A., \& González-Bustamante, B.
 (2016).
@@
 
-\item{\small Olivares, A., \& González-Bustamante, B.
+\item{Joignant, A., \& González-Bustamante, B.
+(2016).
+{\itshape Rendimiento del capital político familiar en el Chile postautoritario}.
+Presentation delivered at the XII Chilean Congress of Political Science, Pucon, Chile.}\vspace{1mm}
+
+%% \item{Olivares, A., \& González-Bustamante, B.
 (2016).
@@
 
-\item{\small González-Bustamante, B., \& Barría, D.
+\item{Olivares, A., \& González-Bustamante, B.
+(2016).
+{\itshape Rotación y supervivencia ministerial antes del quiebre democrático en Chile}.
+Presentation delivered at the XII Chilean Congress of Political Science (ACCP), Pucon, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Barría, D.
 (2016).
 {\itshape Production Patterns of the Contemporary Knowledge in Social Sciences}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
+Presentation delivered at the IX Chilean Congress of Sociology, PreALAS Meeting, Talca, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Cisternas, C.
+\item{González-Bustamante, B., \& Barría, D.
+(2016).
+{\itshape Lógicas de producción del conocimiento en las ciencias sociales contemporáneas}.
+Presentation delivered at the IX Chilean Congress of Sociology, PreALAS Meeting, Talca, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Cisternas, C.
 (2016).
 {\itshape Co-Authorship Networks of the Political Science in Spanish (2010-2015)}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
+Presentation delivered at the IX Chilean Congress of Sociology, PreALAS Meeting, Talca, Chile.}\vspace{1mm}
 
-\item{\small Cisternas, C., González-Bustamante, B., \& Barría, D.
+\item{González-Bustamante, B., \& Cisternas, C.
+(2016).
+{\itshape Redes de co-citación en la ciencia política en español (2010-2015)}.
+Presentation delivered at the IX Chilean Congress of Sociology, PreALAS Meeting, Talca, Chile.}\vspace{1mm}
+
+%% \item{Cisternas, C., González-Bustamante, B., \& Barría, D.
 (2016).
 {\itshape Analysis of the Scientific Production in Spanish on Public Administration and Public Policies (2010-2012)}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
+Presentation delivered at the IX Chilean Congress of Sociology, PreALAS Meeting, Talca, Chile.}\vspace{1mm}
 
-\item{\small Cisternas, C., \& González-Bustamante, B.
+\item{Cisternas, C., González-Bustamante, B., \& Barría, D.
+(2016).
+{\itshape Análisis de la producción científica en español sobre administración pública y políticas públicas (2010-2012)}.
+Presentation delivered at the IX Chilean Congress of Sociology, PreALAS Meeting, Talca, Chile.}\vspace{1mm}
+
+%% \item{Cisternas, C., \& González-Bustamante, B.
 (2016).
 {\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}.
-Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times at the Universidad Bernardo O'Higgins, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times (1969-1990), Universidad Bernardo O'Higgins, Santiago, Chile.}\vspace{1mm}
 
-\item{\small Alenda, S., \& González-Bustamante, B.
+\item{Cisternas, C., \& González-Bustamante, B.
+(2016).
+{\itshape Los monjes de CIEPLAN: producción intelectual y redes de citación durante los años ochenta}.
+Presentation delivered at the International Seminar on Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times (1969-1990), Universidad Bernardo O'Higgins, Santiago, Chile.}\vspace{1mm}
+
+\item{Alenda, S., \& González-Bustamante, B.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2016).
 {\itshape Representation and Elite-Mass Congruence in Chile and Uruguay}.
-Presentation delivered at the XXXIV International Congress of the Latin American Studies Association, New York, USA.}\vspace{1mm}
+Presentation delivered at the XXXIV International Congress of the Latin American Studies Association (LASA), New York, United States.}\vspace{1mm}
 
-\item{\small Alenda, S., González-Bustamante, B., \& Gartenlaub, A.
+\item{Alenda, S., González-Bustamante, B., \& Gartenlaub, A.
 (2016).
 {\itshape The Reshaping of the Political Right in Chile}.
-Presentation delivered at the XXXIV International Congress of the Latin American Studies Association, New York, USA.}\vspace{1mm}
+Presentation delivered at the XXXIV International Congress of the Latin American Studies Association (LASA), New York, United States.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Barría, D.
+%% \item{González-Bustamante, B., \& Barría, D.
 (2015).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Barría, D.
+(2015).
+{\itshape Demandas por más intervención estatal en el Chile postransicional}.
+Presentation delivered at the VIII Chilean Congress of Public Administration, Rancagua, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2015).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B.
+(2015).
+{\itshape Consumo de medios y formas de participación política en Argentina, Chile y Uruguay}.
+Presentation delivered at the XII Argentine Congress of Political Science (SAAP), Mendoza, Argentina.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Olivares, A.
 (2015).
@@
 
-\item{\small González-Bustamante, B., \& Barría, D.
+\item{González-Bustamante, B., \& Olivares, A.
+(2015).
+{\itshape Trayectorias de ministros y subsecretarios en Chile durante los gobiernos de la Concertación (1990-2010)}.
+Presentation delivered at the VIII Latin American Congress of Political Science (ALACIP), Lima, Peru.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Barría, D.
 (2015).
@@
 
-\item{\small Olivares, A., \& González-Bustamante, B.
+\item{González-Bustamante, B., \& Barría, D.
+(2015).
+{\itshape Estatalidad y tendencias estatistas en Chile (2007-2014)}.
+Presentation delivered at the VIII Latin American Congress of Political Science (ALACIP), Lima, Peru.}\vspace{1mm}
+
+%% \item{Olivares, A., \& González-Bustamante, B.
 (2015).
 {\itshape Survival of Ministers and Undersecretaries in Chile (1990-2014)}.
-Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
+Presentation delivered at the International Congress of Elites and Leadership, Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
 
-\item{\small Garrido-Vergara, L., \& González-Bustamante, B.
+\item{Olivares, A., \& González-Bustamante, B.
+(2015).
+{\itshape Supervivencia de ministros y subsecretarios en Chile (1990-2014)}.
+Presentation delivered at the International Congress of Elites and Leadership in Times of Change, Universidad de Salamanca, Salamanca, Spain.}\vspace{1mm}
+
+%% \item{Garrido-Vergara, L., \& González-Bustamante, B.
 (2015).
 {\itshape Elites and Political Reforms: The Chilean Case}.
-Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
+Presentation delivered at the International Congress of Elites and Leadership, Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Ruiz, I.
+\item{Garrido-Vergara, L., \& González-Bustamante, B.
+(2015).
+{\itshape Las élites y las reformas políticas.
+El caso chileno}.
+Presentation delivered at the International Congress of Elites and Leadership in Times of Change, Universidad de Salamanca, Salamanca, Spain.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Ruiz, I.
 (2014).
@@
 
-\item{\small Thezá, M., \& González-Bustamante, B.
+\item{González-Bustamante, B., \& Ruiz, I.
+(2014).
+{\itshape Radiografía de la elección de consejeros regionales 2013}.
+Presentation delivered at the XI Chilean Congress of Political Science (ACCP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{Thezá, M., \& González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{Thezá, M., \& González-Bustamante, B.
+(2014).
+{\itshape Dimensiones de la participación multi-asociativa de los jóvenes en Chile}.
+Presentation delivered at the XI Chilean Congress of Political Science (ACCP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2014).
+{\itshape Medios sociales y malestar con la democracia en Argentina y Uruguay}.
+Presentation delivered at the VI Latin American Congress of Public Opinion (WAPOR), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2014).
+{\itshape Consumo de medios y participación política en el Cono Sur}.
+Presentation delivered at the VI Latin American Congress of Public Opinion (WAPOR), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2014).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2014).
+{\itshape Las elecciones chilenas 2013: Incumbencia, gasto y eficiencia electoral en la competencia al Congreso}.
+Presentation delivered at the Centre for Political Analysis and Research Colloquium (CAIP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
 {\itshape Digital Independent Media in Chile}.
-Presentation delivered at the Seminar of Mass Media Pluralism in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Mass Media Pluralism in Chile, Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2013).
+{\itshape Medios independientes y digitales en Chile}.
+Presentation delivered at the Seminar of Mass Media Pluralism in Chile, Centre for Political Analysis and Research (CAIP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
 {\itshape The Governmental Political Elite in Chile}.
-Presentation delivered at the Seminar of Elites Studies in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
+Presentation delivered at the Seminar of Elites Studies in Chile, Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2013).
+{\itshape La élite política gubernamental (1990-2010)}.
+Presentation delivered at the Seminar of Elites Studies in Chile, Centre for Political Analysis and Research (CAIP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2013).
+{\itshape Barómetro Regional 2013, opinión pública regional en Biobío, Los Lagos y Los Ríos}.
+Presentation delivered at the VI Chilean Congress of Public Administration, Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small Chávez, D., \& González-Bustamante, B.
+\item{González-Bustamante, B.
+(2013).
+{\itshape Redes sociales y comportamiento político en Chile: Twitter como indicador de opinión pública en las primarias presidenciales de 2013}.
+Presentation delivered at the II International Congress of Political Communication (ALICE), Toluca, Mexico.}\vspace{1mm}
+
+%% \item{Chávez, D., \& González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B., \& Soto, D.
+\item{Chávez, D., \& González-Bustamante, B.
+(2013).
+{\itshape Identificación y desafección partidaria en el Ecuador de hoy}.
+Presentation delivered at the XXIX Latin American Congress of Sociology (ALAS), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Soto, D.
 (2013).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Soto, D.
+(2013).
+{\itshape Medios independientes y digitales en Chile: ?`Democratización para el sistema de medios de comunicación?} Presentation delivered at the VII Latin American Congress of Political Science (ALACIP), Bogota, Colombia.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
+(2013).
+{\itshape Trayectorias y patrones de carreras políticas de ministros en Chile (1990-2010)}.
+Presentation delivered at the XI Argentine Congress of Political Science (SAAP), Parana, Argentina.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2013).
@@
 
-\item{\small González-Bustamante, B., \& Valenzuela, P.
+\item{González-Bustamante, B.
+(2013).
+{\itshape Twitter como indicador de opinión pública: El arribo de Bachelet a la presidencial chilena 2013}.
+Presentation delivered at the XI Argentine Congress of Political Science (SAAP), Parana, Argentina.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Valenzuela, P.
 (2012).
 {\itshape Representation Gaps and Incorporated Capital: The Case of the Concertacion's Political Youths}.
-Presentation delivered at the VII Chilean Congress of Sociology, Pucon, Chile.}\vspace{1mm}
+Presentation delivered at the VII Chilean Congress of Sociology, PreALAS Meeting, Pucon, Chile.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Valenzuela, P.
+(2012).
+{\itshape Brechas de representación y capital incorporado: El caso de las juventudes concertacionistas}.
+Presentation delivered at the VII Chilean Congress of Sociology, PreALAS Meeting, Pucon, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2012) {\itshape The Transversal Political Party Thesis: Beyond the Myth}.
@@
 
-\item{\small González-Bustamante, B., \& Chávez, D.
+\item{González-Bustamante, B.
+(2012) {\itshape La tesis del partido transversal: Más allá del mito}.
+Presentation delivered at the X Chilean Congress of Political Science (ACCP), Santiago, Chile.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Chávez, D.
 (2012).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Chávez, D.
+(2012).
+{\itshape Democracia intercultural boliviana: Avances y desafíos}.
+Presentation delivered at the X Chilean Congress of Political Science (ACCP), Santiago, Chile.}\vspace{1mm}
+
+\item{González-Bustamante, B.
 (2012).
 {\itshape Lights and Shadows of the Public Management Professionalisation in the Chilean Case}.
-Presentation delivered at the XXII World Congress of Political Science, Madrid, Spain.}\vspace{1mm}
+Presentation delivered at the XXII World Congress of Political Science (IPSA), Madrid, Spain.}\vspace{1mm}
 
-\item{\small Ríos, T.
+\item{Ríos, T.
 E., \& González-Bustamante, B.
@@
 {\itshape Media System and Democratisation in the Chilean Case}.
-Presentation delivered at the XXII World Congress of Political Science, Madrid, Spain.}\vspace{1mm}
+Presentation delivered at the XXII World Congress of Political Science (IPSA), Madrid, Spain.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Henríquez, G.
+%% \item{González-Bustamante, B., \& Henríquez, G.
 (2012).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Henríquez, G.
+(2012).
+{\itshape El rol de las redes sociales en la última campaña presidencial chilena}.
+Presentation delivered at the I International Congress of Political Communication (ALICE), Madrid, Spain.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2012).
@@
 
+\item{González-Bustamante, B.
+(2012).
+{\itshape Notas y reflexiones sobre el estudio de las élites en Chile}.
+Presentation delivered at the VI Latin American Congress of Political Science (ALACIP), Quito, Ecuador.}
+
 \end{benumerate}

### 2023-09-23 sections/papers.tex
Update papers.tex

@@
 {\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
-\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
+{\scshape doi:} \\ \href{https://doi.org/10.33539/comunife.2021.n21.2580}{\textcolor{blue}{10.33539/comunife.2021.n21.2580}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}
 
@@
 {\itshape Revista de Sociología,} 29, 37--54.
-{\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+{\scshape url:} \\ \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
 
@@
 {\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
+{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
 

### 2023-09-23 spanish/sections/papers.tex
Update papers.tex

@@
 {\itshape Revista de Sociología,} 29, 37--54.
-{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+{\scshape url:} \\ \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
 

### 2023-09-23 spanish/sections/working-papers.tex
Update working-papers.tex

@@
 
-\begin{benumerate}{6}
+\begin{benumerate}{5}
 
-\item{\small González-Bustamante, B., \& Aguilar, D.
+\item{González-Bustamante, B., \& Aguilar, D.
 (2023).
@@
 Dataset, versión previa al lanzamiento, University of Oxford, Universidad de Santiago de Chile (USACH) y Training Data Lab.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.7568387}{\textcolor{blue}{10.5281/zenodo.7568387}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2023).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2023).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
-(2023).
-Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass).
-Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor y Training Data Lab.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-et al.
+\item{González-Bustamante, B., Olivares, A., Cisternas, C., \& Cuevas, R.
 (2023).
@@
 Dataset, University of Oxford, Universidad de Santiago de Chile (USACH) y Training Data Lab.
-{\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}
+{\scshape doi:} \\ \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
-et al.
+\item{González-Bustamante, B., Astete, M., \& Orvenes, B.
 (2021).
@@
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small González-Bustamante, B., \& Soto, D.
+\item{González-Bustamante, B., \& Soto, D.
 (2016).

### 2023-11-03 spanish/sections/reviewer.tex
Update reviewer.tex

@@
 \begin{itemize}
-\item{\small Editor Asociado en {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape desde} 2016}
-\item{\small Editor en {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape desde} 2020}
-\item{\small Moderador en {\itshape SocArXiv}, University of Maryland, USA, {\itshape desde} 2023}
+\item{\small Moderador en {\itshape SocArXiv}, Universidad de Maryland, USA, {\itshape desde} 2023}
+\item{\small Magíster en Historia Económica, Universidad de Santiago de Chile (USACH), CHL, {\itshape desde} 2023}
 \item{\small Red de Expertos por la Transparencia, Fundación Panamericana para el Desarrollo, ECU, {\itshape desde} 2022}
 \item{\small Magíster en Gerencia y Políticas Públicas, Universidad de Santiago de Chile (USACH), CHL, {\itshape desde} 2022}
+\item{\small Editor en {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape desde} 2020}
+\item{\small Editor Asociado en {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape desde} 2016}
 \item{\small Revisor en revistas {\scshape WoS-SSCI}, {\scshape Scopus} \& {\scshape WoS-ESC}, {\itshape desde} 2013}

### 2023-11-03 spanish/sections/experience.tex
Update experience.tex

@@
 
+\cvsection{Posiciones actuales}
+
+\begin{cventries}
+\cventry
+{Investigador Post-Doctoral en Ciencias Sociales Computacionales} 
+{Universidad de Leiden} 
+{La Haya, NLD} 
+{comienza 1 dic. 2023 - 2026}
+{Instituto de Administración Pública, Facultad de Gobernanza y Asuntos Globales} \vspace{1.5mm}
+
+\cventry
+{Profesor Instructor} 
+{Universidad de Santiago de Chile (USACH)} 
+{Santiago, CHL} 
+{2019 - en comisión}
+{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
+\end{cventries}
+\pagebreak
+
 \cvsection{Experiencia profesional relevante}
 
-%% \begin{cventries}
-%% \cventry
-%% {Profesor Instructor} 
-%% {Universidad de Santiago de Chile} 
-%% {Santiago, CHL} 
-%% {2019 - hoy}
-%% {Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
-
+\begin{cventries}
 \cventry
 {Profesor Adjunto} 
-{Universidad de Santiago de Chile} 
+{Universidad de Santiago de Chile (USACH)} 
 {Santiago, CHL} 

### 2023-11-03 sections/experience.tex
Update experience.tex

@@
 
+\cvsection{Current Positions}
+
+\begin{cventries}
+\cventry
+{Post-Doctoral Researcher in Computational Social Sciences} 
+{Leiden University} 
+{The Hague, NLD} 
+{starting Dec. 1, 2023 - 2026}
+{Institute of Public Administration, Faculty of Governance and Global Affairs} \vspace{1.5mm}
+
+\cventry
+{Instructor Professor} 
+{Universidad de Santiago de Chile (USACH)} 
+{Santiago, CHL} 
+{2019 - on leave}
+{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
+\end{cventries}
+
 \cvsection{Relevant Employment}
@@
 \cventry
-{Lecturer} 
-{Universidad de Santiago de Chile} 
+{Adjunt Professor} 
+{Universidad de Santiago de Chile (USACH)} 
 {Santiago, CHL} 
@@
 \end{cventries}
-\pagebreak
+%% \pagebreak

### 2024-02-27 short/sections/selected-papers.tex
Update selected-papers.tex

--- 2023-05-13 short/sections/selected-papers.tex
@@
 %% Bastián González-Bustamante
-%% University of Oxford
+%% Leiden University
 %% https://github.com/bgonzalezbustamante/CV-XeLaTeX
@@
 
+\item{Orchard, X., \& González-Bustamante, B.
+(2024).
+Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
+{\itshape The International Journal of Press/Politics, 29}(1), 100--123.
+{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+Ministerial stability during presidential approval crises: The moderating effect of ministers' attributes on dismissals in Brazil and Chile.
+{\itshape The British Journal of Politics and International Relations, 25}(4), 655--675.
+{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
+
 \item{González-Bustamante, B., \& Aguilar, D.
@@
 Territorial patterns of open e-government: evidence from Chilean municipalities.
-{\itshape Political Research Exchange, 5}(1), 2194369.
+{\itshape Political Research Exchange, 5}(1).
 {\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
 {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
-
-\item{González-Bustamante, B.
-(2022).
-Ministerial stability during presidential approval crises: The moderating effect of ministers' attributes on dismissals in Brazil and Chile.
-{\itshape The British Journal of Politics and International Relations}.
-OnlineFirst.
-{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
 
@@
 
-\item{Orchard, X., \& González-Bustamante, B.
-(2022).
-Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
-{\itshape The International Journal of Press/Politics}.
-OnlineFirst.
-{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2021).
@@
 
-\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B.
+%% \item{González-Bustamante, B., Astete, M., \& Orvenes, B.
 (2020).
-Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service.
+Altos directivos públicos: Un nuevo conjunto de datos de miembros del servicio civil chileno.
 {\itshape Revista de Gestión Pública, IX}(2), 151--169.
-{\footnotesize \scshape [in Spanish and English]}.
-{\scshape doi:} \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
 {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2020).
@@
 
-\item{\small González-Bustamante, B., Carvajal, A., \& González, A.
+%% \item{González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).
-Determinants of E-Government in the Municipalities: Evidence from the Chilean Case.
+Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno.
 {\itshape Gestión y Política Pública, XXIX}(1), 97--129.
-{\footnotesize \scshape [in Spanish]}.
-\\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+{\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
 {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2019).
@@
 
-\item{\small González-Bustamante, B.
+%% \item{González-Bustamante, B.
 (2019).
-Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay.
+Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay.
 {\itshape Convergencia.
 Revista de Ciencias Sociales}, 80, 1--27.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:}  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
+{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2018).
@@
 
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
+%% \item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
-Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010.
+Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010.
 {\itshape Política y Gobierno, XXV}(1), 31--64.
-{\footnotesize \scshape [in Spanish]}.
 {\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
@@
 \end{publications}
+
 %% \pagebreak

### 2024-02-27 short/sections/summary.tex
Create summary.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-XeLaTeX in English
%% Bastián González-Bustamante
%% University of Oxford
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX

%% Based on the following repositories:
%% Awesome CV LaTeX Template for CV/Resume
%% https://github.com/posquit0/Awesome-CV
%% Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX
%% Carla Cisternas' CV-LuaLaTeX Template
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% LaTeX Project Public License v1.3c
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{3mm}
\cvsection{Summary}

\begin{cvparagraph}

\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Security and Global Affairs (ISGA) at the Faculty of Governance and Global Affairs at Leiden University, Netherlands. I hold a DPhil (PhD) in Politics from the University of Oxford, United Kingdom. Before my DPhil, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.}

\textcolor{black}{My research interests lie in the intersection of comparative politics and government, focusing mainly on cabinets, political regimes and civil services. Methodologically, my interests rely on the application of quantitative text analysis, machine learning methods and causal inference strategies in the comparative politics field. In the last few years, my work has been published in {\itshape The International Journal of Press/Politics}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The British Journal of Politics and International Relations}, {\itshape Bulletin of Latin American Research} and elsewhere.}

\textcolor{black}{During my post-doctorate, I will be working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments. Specifically, I will employ Natural Language Processing (NLP) and text-as-data techniques to find patterns and topics within big text data.}
\vspace{1mm}
\end{cvparagraph}

### 2024-06-24 sections/reviewer.tex
Update reviewer.tex

@@
 \begin{itemize}
-\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
-\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
 \item{\small Moderator in {\itshape SocArXiv}, University of Maryland, USA, {\itshape since} 2023}
+\item{\small Master in Economic History, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2023}
 \item{\small Experts Network for Transparency, Pan American Development Foundation, ECU, {\itshape since} 2022}
 \item{\small Master in Management and Public Policy, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2022}
+\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
+\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
 \item{\small Reviewer in {\scshape WoS-SSCI}, {\scshape Scopus}, \& {\scshape WoS-ESCI} journals, {\itshape since} 2013}
 \item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, {\itshape since} 2013}
-\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018, 2019, 2022-2023}
-\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020}
+\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020, 2024}
+\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018-2019, 2022-2023}
 \item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}

### 2024-06-24 sections/teaching.tex
Update teaching.tex

@@
 \begin{itemize}
-\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021}
+%% \item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), spring 2021}
+\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop), spring 2021}
 \end{itemize}
@@
 \begin{itemize}
-\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
+%% \item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
+\item[$\circ$]{\small Comparative Government (undergraduate tutorial), Hilary 2020}
 \end{itemize}
-\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, CHL}
+\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago de Chile}, Santiago, CHL}
 \begin{itemize}
@@
 \item[$\circ$]{\small Political Analysis (undergraduate lecture), fall 2014}
-\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014}
+%% \item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), spring 2013-2014}
+\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture), spring 2013-2014}
 \end{itemize}

### 2024-06-24 short/sections/future-papers.tex
Create future-papers.tex

--- 2022-07-19 sections/conferences-full.tex
@@
 
-\cvsection{List of Conference and Seminar Presentations}
+\cvsection{Working Papers}
 
@@
 
-\begin{benumerate}{74}
+\begin{itemize}
 
-\item{González-Bustamante, B., \& Aguilar, D.
-(2022).
-{\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}.
-Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}
+\item{Kantorowicz, J., \& González-Bustamamante, B.
+(2024, {\itshape forthcoming}).
+{\itshape The Changing Concepts of the Rule of Law}.
+Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
 
-\item{González-Bustamante, B., \& Aguilar, D.
-(2022).
-{\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Local Governments}.
-Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid.}\vspace{1mm}
+\item{González-Bustamamante, B., \& Kantorowicz, J.
+(2024, {\itshape forthcoming}).
+{\itshape Multilingual Word Embeddings for Unravelling the Rule of Law in European Countries}.
+Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
-(2022).
-{\itshape Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential}.
-Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}
+\item{González-Bustamante, B.
+(2023).
+{\itshape Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets}.
+Doctoral thesis chapter, University of Oxford.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Aguilar, D.
-(2022).
-{\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Municipalities}.
-Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}
+\item{González-Bustamante, B.
+(2023).
+{\itshape Resignation Calls, Reallocations and Individual Ministerial Terminations in Presidential Democracies}.
+Doctoral thesis chapter, University of Oxford.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
-(2022).
-{\itshape Ministerial Stability During Presidential Approval Crises: Evidence from Brazil and Chile}.
-Presentation delivered at the Political Studies Association Early Career Network Annual Conference, Sheffield, UK.}\vspace{1mm}
+\item{González-Bustamante, B. (2023). {\itshape Corrective Effect of Ministerial Terminations on Presidential Approval}. Doctoral thesis chapter, University of Oxford.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
-(2022).
-{\itshape Time-Dependent Data Encoding and Time-Varying Exposure Survival Models to Study Presidential Crises}.
-Presentation delivered at the R User Annual Conference, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2022).
-{\itshape Resignation Calls and Dismissals of Ministers in Latin America: Data Gathering using NLP and Machine Learning}.
-Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2022).
-{\itshape Insights of a Number of Ongoing Research on Elites in Latin America: Topics, Methods and Possibilities for Comparison}.
-Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2022).
-{\itshape Resignation Calls and Ministerial Turnover in Latin America: Notes on Data Gathering using Machine Learning}.
-Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Cisternas, C.
-(2022).
-{\itshape Seniority and Cosponsorship in the Chilean Lower House 2006-2018}.
-Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-{\itshape The Use of Machine Learning for Public Affairs Research}.
-Presentation delivered the XII Chilean Congress of Public Administration, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-{\itshape Methodological Challenges and Innovations in the Study of Elites}.
-Presentation delivered at the XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences, Virtual.}\vspace{1mm}
-
-\item{\small Fleming, T.
-G., González-Bustamante, B., \& Schleiter, P.
-(2021).
-{\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}.
-Presentation delivered at the Otto-Friedrich-Universität Bamberg Workshop, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-{\itshape R Applications in Social Sciences: Data Mining and Econometric Modelling}.
-Presentation delivered at the Political Science Method Lecture at the Universidad de Chile, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-{\itshape Vertically Integrated Project: Machine Learning Applications in Public Policy and Economics}.
-Presentation delivered at the VIP Project Workshop at the Universidad Mayor, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-{\itshape Ministerial Stability During Presidential Approval Crises: The Moderating Effect of Ministers' Attributes on Dismissals in Brazil and Chile}.
-Presentation delivered at the XXVI World Congress of Political Science, Virtual.}\vspace{1mm}
-
-\item{\small Cisternas, C., \& González-Bustamante, B.
-(2021).
-{\itshape Political Careers and Co-Sponsorship in the Chilean Lower House 2010-2018}.
-Presentation delivered at the XXVI World Congress of Political Science, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2021).
-{\itshape Data Mining, Modelling and Machine Learning Applications for Social Sciences}.
-Presentation delivered at the I Training Data Lab Workshop, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2020).
-{\itshape Evolution and Early Governmental Responses to COVID-19 in South America}.
-Presentation delivered at the Workshop of the School of Political Science and Public Administration at the Universidad de Talca, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2020).
-{\itshape New Approaches to Studying Political Elites}.
-Presentation delivered at the Colloquium of the Observatório de Elites at the Universidade Federal do Paraná, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2020).
-{\itshape Protest and Social Unrest in Latin America: Determinants and Critical Junctures}.
-Presentation delivered at the Seminar Cycle on Human Rights in Latin America at the Universidade Tiradentes, Virtual.}\vspace{1mm} %% Sergipe, Brazil
-
-\item{\small González-Bustamante, B.
-(2020).
-{\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}.
-Presentation delivered at the PRS DPhil in Politics Workshop in Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}
-
-\item{\small Orchard, X., \& González-Bustamante, B.
-(2020).
-{\itshape An Exploration of Profiles and Perceptions in the Diagnosis of Journalistic Practice in Chile}.
-Presentation delivered at the VI Chilean Association of Communication Researchers Congress, Virtual.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2019).
-{\itshape Presidential Stability and Minister Turnover in Argentina, Brazil, and Chile}.
-Presentation delivered at the XXXVII International Congress of the Latin American Studies Association, Boston, USA.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2018).
-{\itshape Cabinet Stability and Turnover from a Multilevel Approach}.
-Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Cisternas, C.
-(2018).
-{\itshape Social Network Analysis: Application for Elites Study}.
-Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2018).
-{\itshape Geospatial Analysis of Partisanship Density and Electoral Turnout: Evidence from the Chilean Case}.
-Presentation delivered at the XIII Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2018).
-{\itshape Sophistication, Participation, and Political Engagement in Latin America}.
-Presentation delivered at the VII International Congress of Political Communication, Murcia, Spain.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2018).
-{\itshape Survival of Ministers and Vice-Ministers in Chile: Stability and Turnover from a Multilevel Approach}.
-Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics at the Universidade Federal do Paraná, Curitiba, Brazil.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
-(2018).
-{\itshape Trajectories and Post-Career of Ministers in Chile}.
-Presentation delivered at the Research Seminar of the Institute of Public Affairs at the Universidad de Chile, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Del Valle, N.
-(2017).
-{\itshape Media Pluralism and Digital Media Public Opinion}.
-Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile at the Universidad Alberto Hurtado, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A.
-(2017).
-{\itshape Revolving Door?
-Analysis of Public-Private Circulation in Chile}.
-Presentation delivered at the II Foreign Affairs Meeting at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Garrido-Vergara, L.
-(2017).
-{\itshape Socialisation Spaces and Ministerial Post-Career in the Chilean Transition and Post-Transition}.
-Presentation delivered at the IX Chilean Congress of Public Administration, Concepcion, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A.
-(2017).
-{\itshape Public-Private: An Especially Tenuous Frontier.
-Political-Professional Trajectories of the Chilean Authorities (2000-2014)}.
-Presentation delivered at the IX Latin American Congress of Political Science, Montevideo, Uruguay.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Joignant, A.
-(2016).
-{\itshape Gaps and Elite-Mass Congruence in Chile and Uruguay}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Joignant, A., \& González-Bustamante, B.
-(2016).
-{\itshape Family Ties in the Senate and the Chamber of Deputies, Chile from 1989 to 2014}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
-(2016).
-{\itshape Analysis of the Academic Production on Open Government in Spanish}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
-(2016).
-{\itshape Revolving Door and Public-Private Circulation in Chile}.
-Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C.
-(2016).
-{\itshape Open Government in Latin America and Spain: Analysis of the Scientific Production in Spanish}.
-Presentation delivered at the XXI CLAD International Congress on the State Reform and Public Administration, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Joignant, A., \& González-Bustamante, B.
-(2016).
-{\itshape Performance of Family Political Capital in the Chilean Post-Authoritarianism}.
-Presentation delivered at the XII Chilean Congress of Political Science, Pucon, Chile.}\vspace{1mm}
-
-\item{\small Olivares, A., \& González-Bustamante, B.
-(2016).
-{\itshape Turnover and Ministerial Survival Before the Chilean Democratic Breakdown}.
-Presentation delivered at the XII Chilean Congress of Political Science, Pucon, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Barría, D.
-(2016).
-{\itshape Production Patterns of the Contemporary Knowledge in Social Sciences}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Cisternas, C.
-(2016).
-{\itshape Co-Authorship Networks of the Political Science in Spanish (2010-2015)}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
-
-\item{\small Cisternas, C., González-Bustamante, B., \& Barría, D.
-(2016).
-{\itshape Analysis of the Scientific Production in Spanish on Public Administration and Public Policies (2010-2012)}.
-Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}
-
-\item{\small Cisternas, C., \& González-Bustamante, B.
-(2016).
-{\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}.
-Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times at the Universidad Bernardo O'Higgins, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Alenda, S., \& González-Bustamante, B.
-(2016).
-{\itshape The Reshaping of the Political Right in Chile: Change and Continuity in the Perceptions of Social Inequalities}.
-Presentation delivered at the III ISA Forum of Sociology, Vienna, Austria.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2016).
-{\itshape Representation and Elite-Mass Congruence in Chile and Uruguay}.
-Presentation delivered at the XXXIV International Congress of the Latin American Studies Association, New York, USA.}\vspace{1mm}
-
-\item{\small Alenda, S., González-Bustamante, B., \& Gartenlaub, A.
-(2016).
-{\itshape The Reshaping of the Political Right in Chile}.
-Presentation delivered at the XXXIV International Congress of the Latin American Studies Association, New York, USA.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Barría, D.
-(2015).
-{\itshape Stateness in the Chilean Post-Transition}.
-Presentation delivered at the VIII Chilean Congress of Public Administration, Rancagua, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2015).
-{\itshape Media Consumption and Political Participation in Argentina, Chile, and Uruguay}.
-Presentation delivered at the XII Argentine Congress of Political Science, Mendoza, Argentina.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Olivares, A.
-(2015).
-{\itshape Trajectories of Ministers and Undersecretaries in Chile During Concertacion Governments (1990-2010)}.
-Presentation delivered at the VIII Latin American Congress of Political Science, Lima, Peru.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Barría, D.
-(2015).
-{\itshape Stateness' Support in Chile from 2007 to 2014}.
-Presentation delivered at the VIII Latin American Congress of Political Science, Lima, Peru.}\vspace{1mm}
-
-\item{\small Olivares, A., \& González-Bustamante, B.
-(2015).
-{\itshape Survival of Ministers and Undersecretaries in Chile (1990-2014)}.
-Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
-
-\item{\small Garrido-Vergara, L., \& González-Bustamante, B.
-(2015).
-{\itshape Elites and Political Reforms: The Chilean Case}.
-Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Ruiz, I.
-(2014).
-{\itshape Radiography to the Popular Election of Regional Councillors 2013}.
-Presentation delivered at the XI Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}
-
-\item{\small Thezá, M., \& González-Bustamante, B.
-(2014).
-{\itshape Dimensions of the Young People Multi-Associative Participation in Chile}.
-Presentation delivered at the XI Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2014).
-{\itshape Social Media and Malaise with Democracy in Argentina and Uruguay}.
-Presentation delivered at the VI Latin American Congress of Public Opinion, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2014).
-{\itshape Media Consumption and Political Participation in the Southern Cone}.
-Presentation delivered at the VI Latin American Congress of Public Opinion, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2014).
-{\itshape Chilean Elections 2013: Incumbency, Campaign Spending, and Electoral Success in the Congress}.
-Presentation delivered at the Centre for Political Analysis and Research Colloquium, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-{\itshape Digital Independent Media in Chile}.
-Presentation delivered at the Seminar of Mass Media Pluralism in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-{\itshape The Governmental Political Elite in Chile}.
-Presentation delivered at the Seminar of Elites Studies in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-{\itshape Regional Barometer 2013: Regional Public Opinion in Bio-Bio, Los Lagos, and Los Rios}.
-Presentation delivered at the VI Chilean Congress of Public Administration, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-{\itshape Online Social Networks and Political Behaviour in Chile: Twitter as a Measure of Public Opinion During the Primary Presidential Elections in 2013}.
-Presentation delivered at the II International Congress of Political Communication, Toluca, Mexico.}\vspace{1mm}
-
-\item{\small Chávez, D., \& González-Bustamante, B.
-(2013).
-{\itshape Partisanship Identification and Disaffection in Ecuador}.
-Presentation delivered at the XXIX Latin American Congress of Sociology, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Soto, D.
-(2013).
-{\itshape Digital Independent Media in Chile: Democratisation in the Media System?} Presentation delivered at the VII Latin American Congress of Political Science, Bogota, Colombia.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-{\itshape Trajectories and Patterns of the Ministers' Political Careers in Chile}.
-Presentation delivered at the XI Argentine Congress of Political Science, Parana, Argentina.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2013).
-{\itshape Twitter as Public Opinion Measure: The Bachelet's Arrival to the Chilean Presidential Campaign 2013}.
-Presentation delivered at the XI Argentine Congress of Political Science, Parana, Argentina.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Valenzuela, P.
-(2012).
-{\itshape Representation Gaps and Incorporated Capital: The Case of the Concertacion's Political Youths}.
-Presentation delivered at the VII Chilean Congress of Sociology, Pucon, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2012) {\itshape The Transversal Political Party Thesis: Beyond the Myth}.
-Presentation delivered at the X Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Chávez, D.
-(2012).
-{\itshape Bolivian Inter-Cultural Democracy: Advances and Challenges}.
-Presentation delivered at the X Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2012).
-{\itshape Lights and Shadows of the Public Management Professionalisation in the Chilean Case}.
-Presentation delivered at the XXII World Congress of Political Science, Madrid, Spain.}\vspace{1mm}
-
-\item{\small Ríos, T.
-E., \& González-Bustamante, B.
-(2012).
-{\itshape Media System and Democratisation in the Chilean Case}.
-Presentation delivered at the XXII World Congress of Political Science, Madrid, Spain.}\vspace{1mm}
-
-\item{\small González-Bustamante, B., \& Henríquez, G.
-(2012).
-{\itshape The Role of the Online Social Networks in the Last Chilean Presidential Campaign}.
-Presentation delivered at the I International Congress of Political Communication, Madrid, Spain.}\vspace{1mm}
-
-\item{\small González-Bustamante, B.
-(2012).
-{\itshape Research Notes and Reflections on the Study of Elites in Chile}.
-Presentation delivered at the VI Latin American Congress of Political Science, Quito, Ecuador.}
-
-\end{benumerate}
+\end{itemize}
 
 \end{publications}
+
+%% \pagebreak

### 2024-06-24 spanish/sections/reviewer.tex
Update reviewer.tex

@@
 \item{\small Revisor en revistas {\scshape SciELO} \& {\scshape Latindex}, {\itshape desde} 2013}
-\item{\small Times Higher Education Ranking, {\scshape Elsevier}, NLD, 2018, 2019, 2022-2023}
-\item{\small Proyecto V-Dem, Universidad de Gotemburgo, SWE, 2014, 2018-2020}
+\item{\small Proyecto V-Dem, Universidad de Gotemburgo, SWE, 2014, 2018-2020, 2024}
+\item{\small Times Higher Education Ranking, {\scshape Elsevier}, NLD, 2018-2019, 2022-2023}
 \item{\small Encuesta de Reputación Académica Global, Clarivate Analytics, USA, 2020}

### 2024-07-29 sections/languages.tex
Update languages.tex

@@
 {Programming \&} 
-{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}
+{\textcolor{black}{Python, R, Git, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, ArcGIS, {\scshape atlas}.ti}, {\scshape HPoP},}
 
@@
 {Software} 
-{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
+{\textcolor{black}{Zotero, JabRef, {\LaTeX}, Bib{\TeX}, MS Office, WordPress, Moodle, {\scshape java}, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
 

### 2024-07-29 short/sections/future-papers.tex
Update future-papers.tex

@@
 
+\item{González-Bustamante, B., \& Rivera, S.
+(2024, {\itshape forthcoming}).
+Toxicity and Digital Incivility during Political Deliberation: The Case of the Constitutional Convention in Chile.
+Paper delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich, Switzerland.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2024, {\itshape forthcoming}).
+Benchmarking Open-Source Large Language Models in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data.
+Preprint.}\vspace{1mm}
+
 \item{Kantorowicz, J., \& González-Bustamamante, B.
-(2024, {\itshape forthcoming}).
+(2024).
 {\itshape The Changing Concepts of the Rule of Law}.
-Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
+Paper delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
 
 \item{González-Bustamamante, B., \& Kantorowicz, J.
-(2024, {\itshape forthcoming}).
+(2024).
 {\itshape Multilingual Word Embeddings for Unravelling the Rule of Law in European Countries}.
-Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
+Paper delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
 

### 2024-07-29 short/sections/summary.tex
Update summary.tex

@@
 
-\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Security and Global Affairs (ISGA) at the Faculty of Governance and Global Affairs at Leiden University, Netherlands.
+\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration at the Faculty of Governance and Global Affairs at Leiden University, Netherlands.
 I hold a DPhil (PhD) in Politics from the University of Oxford, United Kingdom.
@@
 Methodologically, my interests rely on the application of quantitative text analysis, machine learning methods and causal inference strategies in the comparative politics field.
-In the last few years, my work has been published in {\itshape The International Journal of Press/Politics}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The British Journal of Politics and International Relations}, {\itshape Bulletin of Latin American Research} and elsewhere.}
+In the last years, my work has been published in {\itshape The International Journal of Press/Politics}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The British Journal of Politics and International Relations}, {\itshape Bulletin of Latin American Research} and elsewhere.}
 
-\textcolor{black}{During my post-doctorate, I will be working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments.
-Specifically, I will employ Natural Language Processing (NLP) and text-as-data techniques to find patterns and topics within big text data.}
+\textcolor{black}{During my post-doctorate at Leiden, I am working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments.
+Specifically, I employ Natural Language Processing (NLP) and text-as-data techniques to find patterns and topics within big text data.}
 \vspace{1mm}

### 2024-09-24 sections/awards.tex
Update awards.tex

@@
 \cvhonor
+{Early Career Scholar Award}
+{Best early career work and travel support for the BigSurv23 Conference, about {\pounds} 525.}
+{Quito, ECU}
+{2023}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
 {ECPR Joint Sessions of Workshops Grant}
-{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, {\pounds} 1 350.}
+{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, about {\pounds} 1 350.}
 {Toulouse, FRA}
@@
 {SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
-{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1 400.}
+{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, about {\pounds} 1 400.}
 {Bath, GBR}
@@
 {St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
-{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2 255.} 
+{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, about {\pounds} 2 255.} 
 {Oxford, GBR}
@@
 {Becas Chile Doctoral Scholarship Abroad} 
-{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
+{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), about {\pounds} 160 000.}
 {Oxford, GBR}
@@
 %% {LASA Travel Grant} 
-%% {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
+%% {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400.}
 %% {New York, USA}
@@
 {FONDECYT Thesis Writing Grant}
-{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
+{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), about {\pounds} 1 150.}
 {Santiago, CHL}

### 2024-09-24 sections/book-chapters.tex
Update book-chapters.tex

@@
 Cham: Springer.
-{\scshape doi:} \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}
 
@@
 Curitiba: Editora da Universidade Federal do Paraná.
-{\scshape url:} \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+Available at \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
@@
 Santiago: RIL Editores.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}.}\vspace{1mm}
+SocArXiv: \href{https://doi.org/10.31235/osf.io/nkftb}{\textcolor{blue}{10.31235/osf.io/nkftb}}.}\vspace{1mm}
 
@@
 Santiago: Social-Ediciones.
-{\scshape doi:} \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.34720/2nd0-8t73}{\textcolor{blue}{10.34720/2nd0-8t73}}.}\vspace{1mm}
 
@@
 Mexico City: INFOTEC.
-{\scshape url:} \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+Available at \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
@@
 Santiago: Fundación Democracia y Desarrollo.
-{\scshape url:} \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
+Available at \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{\textcolor{blue}{www.researchgate.net}}}\vspace{1mm}
 

### 2024-09-24 sections/experience.tex
Update experience.tex

--- 2023-09-22 sections/experience.tex
@@
 
-\cvsection{Relevant Employment}
+\cvsection{Current Positions}
 
@@
 \cventry
-{Lecturer} 
-{Universidad de Santiago de Chile} 
+{Post-Doctoral Researcher in Computational Social Science} 
+{Leiden University} 
+{The Hague, NLD} 
+{2023 - 2026}
+{Institute of Public Administration, Faculty of Governance and Global Affairs} \vspace{1.5mm}
+
+\cventry
+{Faculty Member (to be hierarchically ranked)} 
+{Universidad Diego Portales} 
+{Santiago, CHL} 
+{2024 - today}
+{School of Public Administration, Faculty of Administration and Economics} \vspace{1.5mm}
+
+\cvsection{Relevant Employment}
+
+\cventry
+{Instructor Professor} 
+{Universidad de Santiago de Chile (USACH)} 
+{Santiago, CHL} 
+{2019 - 2024}
+{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
+\end{cventries}
+
+\begin{cventries}
+\cventry
+{Adjunt Professor} 
+{Universidad de Santiago de Chile (USACH)} 
 {Santiago, CHL} 

### 2024-09-24 sections/papers.tex
Update papers.tex

--- 2023-09-23 sections/papers.tex
@@
 
+\item{Orchard, X., \& González-Bustamante, B.
+(2024).
+Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
+{\itshape The International Journal of Press/Politics, 29}(1), 100--123.
+DOI: \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
+
 \item{González-Bustamante, B.
@@
 Ministerial stability during presidential approval crises: The moderating effect of ministers’ attributes on dismissals in Brazil and Chile.
-{\itshape The British Journal of Politics and International Relations}.
-OnlineFirst.
-{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
+{\itshape The British Journal of Politics and International Relations, 25}(4), 655-675.
+DOI: \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
 
@@
 FirstView.
-{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
-
-\item{Orchard, X., \& González-Bustamante, B.
-(2022).
-Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
-{\itshape The International Journal of Press/Politics}.
-OnlineFirst.
-{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 
@@
 {\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
-{\scshape url:} \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
+Available at \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{https://doi.org/10.31235/osf.io/p963q}}.}\vspace{1mm}
 
@@
 {\itshape World Development, 137}, 105180.
-{\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}.}\vspace{1mm}
 
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
 
@@
 {\itshape Gestión y Política Pública, XXIX}(1), 97--129.
-{\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
+DOI: \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}
 
@@
 Revista de Ciencias Sociales}, 80, 1--27.
-{\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
-{\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
+DOI: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}.
+SocArXiv: \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}
 
@@
 {\itshape Política y Gobierno, XXV}(1), 31--64.
-{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+Available at \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
 
@@
 
-\begin{benumerate}{10}
+\begin{benumerate}{11}
 
@@
 {\itshape Political Research Exchange, 5}(1).
-{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+
+%% \item{González-Bustamante.
+B.
+(2022).
+Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential.
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
+{\footnotesize \scshape [in Spanish]}.
+{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+{\scshape \footnotesize SocArXiv:} \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+
+\item{González-Bustamante.
+B.
+(2022).
+Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
+DOI: \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
 
@@
 {\itshape e-Ciencias de la Información, 12}(2), 1--18.
-{\scshape doi:} \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
+DOI: \href{https://doi.org/10.15517/eci.v12i2.50078}{\textcolor{blue}{10.15517/eci.v12i2.50078}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/2jrvm}{\textcolor{blue}{10.31235/osf.io/2jrvm}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.ucr.ac.cr/index.php/eciencias/article/view/50078}{\textcolor{blue}{https://revistas.ucr.ac.cr}}
 
@@
 {\itshape Revista de Gestión Pública, IX}(2), 151--169.
-{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
+DOI: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}
 
@@
 {\itshape Iberoamericana, XX}(74), 229--259.
-{\scshape doi}: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.18441/ibam.20.2020.74.229-259}{\textcolor{blue}{10.18441/ibam.20.2020.74.229-259}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}.}\vspace{1mm}
 
@@
 {\itshape Latin American Business Review, 20}(4), 367--387.
-{\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
 
@@
 Revista de Ciencias Sociales y Humanidades, 28}(56), 22--42.
-{\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
+DOI: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{\textcolor{blue}{10.20983/noesis.2019.2.3}}.}\vspace{1mm}
 
@@
 {\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
-{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
+Available at \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
 
@@
 {\itshape Colombia Internacional}, 87, 81--108.
-{\scshape doi}: \\ \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
+DOI: \\ \href{https://doi.org/10.7440/colombiaint87.2016.04}{\textcolor{blue}{10.7440/colombiaint87.2016.04}}.}\vspace{1mm}
 
@@
 {\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
-{\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
+DOI: \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
 
@@
 {\itshape Revista de Gestión Pública, IV}(2), 151--190.
-{\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
+DOI: \\ \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}.} \vspace{1mm}
 
@@
 
-%% \item{González-Bustamante.
-B.
-(2022).
-Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential.
-{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
-{\footnotesize \scshape [in Spanish]}.
-{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
-{\scshape \footnotesize SocArXiv:} \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
-
-\item{González-Bustamante.
-B.
-(2022).
-Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
-{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
-{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+\item{González-Bustamante, B.
+(2023).
+Análisis de Componentes Principales con correlaciones policóricas: Aplicación en consumo de medios.
+{\itshape Tufte Working Papers}.
+OnlineFirst.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/npc9e}{\textcolor{blue}{10.31235/osf.io/npc9e}}.}\vspace{1mm}
 
@@
 {\itshape Tufte Working Papers}, 2, 1--21.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.5281/zenodo.6739833}{\textcolor{blue}{10.5281/zenodo.6739833}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}.}\vspace{1mm}
 
@@
 21--32.
-{\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
-\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
+Available at \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
 
@@
 {\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
-\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.33539/comunife.2021.n21.2580}{\textcolor{blue}{10.33539/comunife.2021.n21.2580}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}
 
@@
 {\itshape Tufte Working Papers}, 1, 1--15.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.5281/zenodo.6739266}{\textcolor{blue}{10.5281/zenodo.6739266}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}.}\vspace{1mm}
 
@@
 {\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
-{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+Available at \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 {\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
-{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+Available at \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 {\itshape Políticas Públicas, 8}(1), 21--35.
-{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
+Available at \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
 
@@
 {\itshape Revista SAAP, 9}(1), 119--141.
-{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+Available at \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 {\itshape Revista de Sociología,} 29, 37--54.
-{\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+Available at \\ \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
 
@@
 {\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
-{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+Available at \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 {\itshape Intersticios Sociales,} 6, 1--20.
-{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+Available at \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 {\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
+Available at \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
 
@@
 {\itshape Más Poder Local,} 12, 32--39.
-{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
+Available at \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
 

### 2024-09-24 sections/projects.tex
Create projects.tex

@@
 
-%% DEPRECATED
-
-\cvsection{Funding \& Research Projects}
+\cvsection{Relevant Research Projects}
 
@@
 \cvhonor
-{Chilean Political Science Impact Ranking} 
-{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
-{Coordinator}
-{2020}
+{Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
+{NWO VIDI SWG Project VI.Vidi.211.226, Research Associate (Natascha van der Zwan, Principal Investigator), about {\pounds} 800 000. Period: 2024-2026.}
+{Dutch Research Agency}
+{2024}
 \end{cvhonors}
@@
 \cvhonor
-{COVID-19 Pandemic in South America}
-{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
-{Coordinator}
-{2020}
+{Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
+{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), Principal Investigator, about {\pounds} 1 500. Period: 2024-2025.}
+{UDP}
+{2024}
 \end{cvhonors}
@@
 \cvhonor
-{Gender Turnout and Elected Representatives in Iceland Municipal Elections}
-{Prof. Petra Schleiter, Department of Politics and International Relations and St Hilda's College, University of Oxford}
-{Research Assistant}
-{2020}
+{Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
+{OpenAI Academic Programme, Principal Investigator, about {\pounds} 5 000. Period: 2024.}
+{OpenAI}
+{2024}
 \end{cvhonors}
@@
 \cvhonor
-{Survival of the Senior Civil Servants in the Chilean Executive Branch}
-{Funded by the Universidad de Santiago de Chile (Academic Performance Agreement). {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/WBF6M}{10.17605/OSF.IO/WBF6M}}
-{Researcher}
-{2018}
+{Unravelling the Rule of Law: A Machine Learning Approach}
+{NWO XS Project 406.XS.01.013, Research Associate (Jaroslaw Kantorowicz, Principal Investigator), about {\pounds} 45 000. Period: 2023-2024.}
+{Dutch Research Agency}
+{2023}
 \end{cvhonors}
@@
 \cvhonor
-{Political System and Visibility of Actors in the Public Debate Articulated by the Elite Press, 1990-2018}
-{Funded by the Universidad Alberto Hurtado (XVI Promotion of Research Fund, Ximena Orchard, Principal Investigator)}
-{Researcher}
-{2019}
+{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
+{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), Principal Investigator, about {\pounds} 1 700. Period: 2022.}
+{USACH}
+{2022}
 \end{cvhonors}
@@
 \cvhonor
-{Transparency and Publication Dynamics on the Latin American Public Administration}
-{Funded by the Universidad de Santiago (USA1498.57, Diego Barría, Principal Investigator)}
-{Researcher}
-{2017}
+{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
+{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about {\pounds} 3 000. Period: 2019.}
+{UAH}
+{2019}
 \end{cvhonors}
@@
 \vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{Public Service Motivation, Open Government and Preferences on Public Services}
-{Funded by the Universidad de Santiago (USA1498.37, Diego Barría, Principal Investigator)}
-{Researcher}
-{2016}
-\end{cvhonors}
-
-\vspace{1mm}
-
-%% PENDING PROJECTS

### 2024-09-24 sections/reviewer.tex
Update reviewer.tex

--- 2023-09-23 sections/reviewer.tex
@@
 \begin{itemize}
-\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
-\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
+\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020, 2024-2025}
 \item{\small Moderator in {\itshape SocArXiv}, University of Maryland, USA, {\itshape since} 2023}
 \item{\small Experts Network for Transparency, Pan American Development Foundation, ECU, {\itshape since} 2022}
-\item{\small Master in Management and Public Policy, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2022}
+\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
+\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
 \item{\small Reviewer in {\scshape WoS-SSCI}, {\scshape Scopus}, \& {\scshape WoS-ESCI} journals, {\itshape since} 2013}
 \item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, {\itshape since} 2013}
-\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018, 2019, 2022-2023}
-\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020}
+\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018-2019, 2022-2024}
+\item{\small Master in Economic History, Universidad de Santiago de Chile (USACH), CHL, 2023-2024}
+\item{\small Master in Management and Public Policy, Universidad de Santiago de Chile (USACH), CHL, 2022-2024}
 \item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}

### 2024-09-24 sections/summary.tex
Update summary.tex

--- 2022-10-17 sections/summary.tex
@@
 
-I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom.
-Before starting the DPhil in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.
-Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).
+\textcolor{black}{I am a post-doctoral researcher in Computational Social Science and a lecturer in Governance and Development at the Institute of Public Administration at the Faculty of Governance and Global Affairs at Leiden University, Netherlands.
+I hold a DPhil (PhD) in Politics from the University of Oxford, United Kingdom.
+Before my DPhil, I earned an MA (1st) in Political Science and a BA (2:1) in Public Administration, both from the Universidad de Chile.}
 
-My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date.
-My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features.
-In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives.
-In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.
+\textcolor{black}{In addition, in Chile, I am a faculty member at the Faculty of Administration and Economics at the Universidad Diego Portales and a research associate at the Training Data Lab, a research group focused on data mining, econometric modelling and AI machine learning in social sciences.}
 
-My research is funded by the Chilean National Agency for Research and Development (ANID), the St Hilda’s College Muriel Wise Fund and the Postgraduate and Postdoctoral Award of the Society for Latin American Studies (SLAS).
+\textcolor{black}{My research interests lie in the intersection of comparative politics and government, focusing mainly on cabinets, political regimes and civil services.
+Methodologically, my interests rely on the application of quantitative text analysis, machine learning methods and causal inference strategies in the comparative politics field.
+In the last years, my work has been published in {\itshape The International Journal of Press/Politics}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The British Journal of Politics and International Relations}, {\itshape Bulletin of Latin American Research} and elsewhere.}
 \vspace{1mm}

### 2024-09-24 sections/working-papers.tex
Update working-papers.tex

--- 2022-10-17 sections/working-papers.tex
@@
 
-\cvsection{Data Collection Projects}
+\cvsection{Preprints, Working Papers and Reviews}
 
@@
 
-\begin{benumerate}{3}
+\begin{benumerate}{8}
 
-\item{\small González-Bustamante, B., \& Aguilar, D.
-(2022).
-Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set].
-Pre-release version under restricted access.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
+\item{González-Bustamante, B.
+(2024).
+Benchmarking LLMs in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data.
+arXiv preprint.
+DOI: \href{https://doi.org/10.48550/arXiv.2409.09741}{\textcolor{blue}{10.48550/arXiv.2409.09741}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
+\item{González-Bustamante, B., \& Kantorowicz, J.
+(2024).
+Cross-Lingual Word Embeddings for Unravelling the Rule of Law in European Countries.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/m65re}{\textcolor{blue}{10.31219/osf.io/m65re}}.}\vspace{1mm}
 
-\item{González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2024).
+Changing Meaning of the Rule of Law.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
 
-\end{benumerate}
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2024).
+Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/sgf8y}{\textcolor{blue}{10.31219/osf.io/sgf8y}}.}\vspace{1mm}
 
-\end{publications}
-
-\cvsection{Working Papers and Reviews}
-
-\begin{publications}
-
-\begin{benumerate}{4}
-
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+%% \item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
+(2016).
+¿Puerta giratoria?
+Análisis de la circulación público-privada en Chile (2000-2014).
+{\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
+DOI: \\ \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Olivares, A.
 (2016).
 Undersecretaries Rotation in the Chilean Cabinets (1990-2014).
-{\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil.
+{\itshape Newsletter.
+Observat\'orio de elites pol\'iticas e sociais do Brasil.
 NUSP/UFPR, 3}(5), 1--19.
@@
 
-\item{\small González-Bustamante, B., \& Soto, D.
+\item{González-Bustamante, B., \& Olivares, A.
+(2016).
+A rotatividade de subsecretários dos ministérios no Chile (1990-2014).
+{\itshape Newsletter.
+Observat\'orio de elites pol\'iticas e sociais do Brasil.
+NUSP/UFPR, 3}(5), 1--19.
+Available at \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Soto, D.
 (2016).
@@
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B., \& Soto, D.
+(2016).
+Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave.
+{\itshape Serie Política, Gestión y Políticas Públicas}, 2, 1--26.
+DOI: \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B.
 (2015).
@@
 
+\item{González-Bustamante, B.
+(2015).
+Programas de Naciones Unidas para el Desarrollo (PNUD).
+(2014).
+Ciudadanía Política: Voz y Participación Ciudadana en América Latina.
+Buenos Aires: Siglo Veintiuno Editores.
+{\itshape Revista de Gestión Pública, IV}(1), 143--149.
+DOI: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}
+
 \end{benumerate}
@@
 \end{publications}
+\cvsection{Data Collection Projects}
+
+\begin{publications}
+
+\begin{benumerate}{6}
+
+\item{González-Bustamante, B., \& Rivera, S.
+(2024).
+Annotated Data in Spanish for Toxicity and Insults in Digital Social Networks.
+Dataset, pre-release version 0.3.3 -- Purple Butterfly, Leiden University, Universidad Diego Portales, University of California Irvine and Training Data Lab.
+DOI: \href{https://zenodo.org/doi/10.5281/zenodo.12574288}{\textcolor{blue}{10.5281/zenodo.12574288}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., Olivares, A., Cisternas, C., \& Cuevas, R.
+(2023).
+Chilean Political Science Ranking.
+Dataset, Leiden University, Universidad Diego Portales and Training Data Lab.
+DOI: \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Aguilar, D.
+(2023).
+Data Set on Local Government Indicators in Chile.
+Dataset, pre-release version 0.21.15 -- Late Sky, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.7568387}{\textcolor{blue}{10.5281/zenodo.7568387}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Ministers (1990-2014).
+Dataset, version 3.3.7 -- Soft Dew, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Undersecretaries (1990-2022).
+Dataset, version 2.1.4 -- Wandering Grass, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2021).
+Survival of the Senior Civil Servants in the Chilean Executive Branch.
+Dataset, pre-release version under restricted access 1.13.19 -- Bold Lab, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.8115596}{\textcolor{blue}{10.5281/zenodo.8115596}}.}\vspace{1mm}
+
+\end{benumerate}
+
+\end{publications}

### 2024-09-24 sections/awards.tex
Update awards.tex

@@
 
+%% Zurich 2024
+
 \vspace{1mm}
@@
 {Early Career Scholar Award}
-{Best early career work and travel support for the BigSurv23 Conference, about {\pounds} 525.}
+{Best early career work and travel support for the BigSurv23 Conference, about USD\$700.} %% {\pounds} 525
 {Quito, ECU}
@@
 {ECPR Joint Sessions of Workshops Grant}
-{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, about {\pounds} 1 350.}
+{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, about USD\$1 800.} %% {\pounds} 1 350
 {Toulouse, FRA}
@@
 
+%% Kassel
+
+%% Zurich 2022
+
+%% IPSA Seminar in Madrid
+
 \begin{cvhonors}
@@
 {SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
-{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, about {\pounds} 1 400.}
+{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, about USD\$1 850.} %% {\pounds} 1 400
 {Bath, GBR}
@@
 \cvhonor
-{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
-{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, about {\pounds} 2 255.} 
+{St Hilda's College Muriel Wise Fund and Travel and Book Grants} %% Re-check
+{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, about USD\$3 000.}  %% {\pounds} 2 255
 {Oxford, GBR}
@@
 {Becas Chile Doctoral Scholarship Abroad} 
-{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), about {\pounds} 160 000.}
+{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), about USD\$215 000.} %% {\pounds} 160 000
 {Oxford, GBR}
@@
 {FONDECYT Thesis Writing Grant}
-{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), about {\pounds} 1 150.}
+{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), about USD\$1 500.} %% {\pounds} 1 150
 {Santiago, CHL}

### 2024-09-24 sections/projects.tex
Update projects.tex

@@
 {Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
-{NWO VIDI SWG Project VI.Vidi.211.226, Research Associate (Natascha van der Zwan, Principal Investigator), about {\pounds} 800 000. Period: 2024-2026.}
+{NWO VIDI SWG Project VI.Vidi.211.226, Research Associate (Natascha van der Zwan, Principal Investigator), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
 {Dutch Research Agency}
@@
 {Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
-{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), Principal Investigator, about {\pounds} 1 500. Period: 2024-2025.}
+{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), Principal Investigator, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
 {UDP}
@@
 {Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
-{OpenAI Academic Programme, Principal Investigator, about {\pounds} 5 000. Period: 2024.}
+{OpenAI Academic Programme, Principal Investigator, about USD\$5 000. Period: 2024.}
 {OpenAI}
@@
 {Unravelling the Rule of Law: A Machine Learning Approach}
-{NWO XS Project 406.XS.01.013, Research Associate (Jaroslaw Kantorowicz, Principal Investigator), about {\pounds} 45 000. Period: 2023-2024.}
+{NWO XS Project 406.XS.01.013, Research Associate (Jaroslaw Kantorowicz, Principal Investigator), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
 {Dutch Research Agency}
@@
 {Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
-{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), Principal Investigator, about {\pounds} 1 700. Period: 2022.}
+{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), Principal Investigator, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
 {USACH}
@@
 {Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
-{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about {\pounds} 3 000. Period: 2019.}
+{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about USD\$4 000.
+Period: 2019.} %% {\pounds} 3 000
 {UAH}

### 2024-10-08 sections/projects.tex
Update projects.tex

@@
 {Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
-{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about USD\$4 000.
+{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Research Associate (Ximena Orchard, Principal Investigator), about USD\$4 000.
 Period: 2019.} %% {\pounds} 3 000

### 2024-10-08 short/sections/future-papers.tex
Update future-papers.tex

--- 2024-06-24 short/sections/future-papers.tex
@@
 
+\hspace{2.25mm}{\footnotesize $^\star$ {\itshape These manuscripts are in the first round of peer review or R\&R}}
+
 \begin{publications}
 
-\begin{itemize}
-
-\item{Kantorowicz, J., \& González-Bustamamante, B.
-(2024, {\itshape forthcoming}).
-{\itshape The Changing Concepts of the Rule of Law}.
-Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
-
-\item{González-Bustamamante, B., \& Kantorowicz, J.
-(2024, {\itshape forthcoming}).
-{\itshape Multilingual Word Embeddings for Unravelling the Rule of Law in European Countries}.
-Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
+\begin{benumerate}{9}
 
 \item{González-Bustamante, B.
-(2023).
-{\itshape Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets}.
-Doctoral thesis chapter, University of Oxford.}\vspace{1mm}
+(2024, {\itshape second round of review}).
+Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets.
+Preprint upon request.}\vspace{1mm}
 
 \item{González-Bustamante, B.
-(2023).
-{\itshape Resignation Calls, Reallocations and Individual Ministerial Terminations in Presidential Democracies}.
-Doctoral thesis chapter, University of Oxford.}\vspace{1mm}
+(2024, {\itshape first round of review}).
+Resignation Calls, Reallocations and Individual Ministerial Terminations in Presidential Democracies.
+{\bfseries Job market paper}.}\vspace{1mm}
 
-\item{González-Bustamante, B. (2023). {\itshape Corrective Effect of Ministerial Terminations on Presidential Approval}. Doctoral thesis chapter, University of Oxford.}\vspace{1mm}
+\item{González-Bustamante, B.
+(2024, {\itshape first round of review}).
+Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval.
+Preprint upon request.}\vspace{1mm}
 
-\end{itemize}
+\item{González-Bustamante, B.
+(2024, {\itshape first round of review}).
+Benchmarking LLMs in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data.
+arXiv preprint.
+DOI: \href{https://doi.org/10.48550/arXiv.2409.09741}{\textcolor{blue}{10.48550/arXiv.2409.09741}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Kantorowicz, J.
+(2024, {\itshape first round of review}).
+Cross-Lingual Word Embeddings for Unravelling the Rule of Law in European Countries.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/m65re}{\textcolor{blue}{10.31219/osf.io/m65re}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Rivera, S.
+(2024, {\itshape first round of review}).
+Toxicity and Digital Incivility during Political Deliberation: The Case of the Constitutional Convention in Chile.
+Preprint upon request.}\vspace{1mm}
+
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2024, {\itshape first round of review}).
+Changing Meaning of the Rule of Law.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
+
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2024, {\itshape first round of review}).
+Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/sgf8y}{\textcolor{blue}{10.31219/osf.io/sgf8y}}.}\vspace{1mm}
+
+\item{Orchard, X., González-Bustamante, B., \& Cisternas.
+C.
+(2024, {\itshape first round of review}).
+Amplification, Contestation, and Toxic Interactions with News: Testing the Effect of a Protest Cycle in Digital News Participation.
+Preprint upon request.}\vspace{1mm}
+
+\end{benumerate}
 

### 2024-10-08 short/sections/projects.tex
Create projects.tex

--- 2024-09-24 sections/projects.tex
@@
 {Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
-{NWO VIDI SWG Project VI.Vidi.211.226, Research Associate (Natascha van der Zwan, Principal Investigator), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
+{NWO VIDI SWG Project VI.Vidi.211.226, {\bfseries PostDoc} (Natascha van der Zwan, PI), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
 {Dutch Research Agency}
@@
 {Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
-{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), Principal Investigator, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
+{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), {\bfseries PI}, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
 {UDP}
@@
 {Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
-{OpenAI Academic Programme, Principal Investigator, about USD\$5 000. Period: 2024.}
+{OpenAI Academic Programme, {\bfseries PI}, about USD\$5 000. Period: 2024.}
 {OpenAI}
@@
 {Unravelling the Rule of Law: A Machine Learning Approach}
-{NWO XS Project 406.XS.01.013, Research Associate (Jaroslaw Kantorowicz, Principal Investigator), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
+{NWO XS Project 406.XS.01.013, {\bfseries PostDoc} (Jaroslaw Kantorowicz, PI), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
 {Dutch Research Agency}
@@
 {Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
-{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), Principal Investigator, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
+{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), {\bfseries PI}, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
 {USACH}
@@
 {Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
-{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about USD\$4 000.
+{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), {\bfseries Research Associate} (Ximena Orchard, PI), about USD\$4 000.
 Period: 2019.} %% {\pounds} 3 000

### 2024-10-08 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 
-\begin{itemize}
+\begin{benumerate}{8}
 
@@
 {\itshape The International Journal of Press/Politics, 29}(1), 100--123.
-{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
 
@@
 {\itshape The British Journal of Politics and International Relations, 25}(4), 655--675.
-{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
 
@@
 {\itshape Political Research Exchange, 5}(1).
-{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
 
@@
 FirstView.
-{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-\\ {\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
 
@@
 {\itshape Latin American Business Review, 20}(4), 367--387.
-\\ {\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
 
@@
 
-\end{itemize}
+\end{benumerate}
 

### 2024-10-13 short/sections/summary.tex
Update summary.tex

@@
 
-\textcolor{black}{During my post-doctorate at Leiden, I am working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments.
+\textcolor{black}{During my post-doctorate at Leiden, I am working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments in Europe.
 Specifically, I employ Natural Language Processing (NLP) and text-as-data techniques to find patterns and topics within big text data.}

### 2025-01-15 sections/references.tex
Update references.tex

@@
 \begin{itemize}
-\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
+\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, GBR}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \pagebreak %% \vspace{1.5mm}
-\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:alfredo.joignant@mail.udp.cl}{\textcolor{blue}{alfredo.joignant@mail.udp.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Jaime Baeza}, Assistant Professor, Universidad de Chile, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:jbaezaf@u.uchile.cl}{\textcolor{blue}{jbaezaf@u.uchile.cl}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Marcel Thez\'a}, Associate Professor, Universidad de Los Lagos, Chile}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:marcel.theza@ulagos.cl}{\textcolor{blue}{marcel.theza@ulagos.cl}}}} \vspace{1.5mm}
+\item[]{\small {\bfseries David Doyle}, Professor of Politics, University of Oxford, GBR}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
+%% \item[]{\small {\bfseries Ryan E. Carlin}, Professor of Political Science, Georgia State University, USA}
+%% \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small %% \href{mailto:rcarlin@gsu.edu}{\textcolor{blue}{rcarlin@gsu.edu}}}} \vspace{1.5mm}
+\item[]{\small {\bfseries Jaroslaw Kantorowicz}, Associate Professor, Leiden University, NLD}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:j.j.kantorowicz@fgga.leidenuniv.nl}{\textcolor{blue}{j.j.kantorowicz@fgga.leidenuniv.nl}}}} \vspace{1.5mm}
 \end{itemize}

### 2025-01-15 sections/teaching.tex
Update teaching.tex
LUCDH grant

@@
 \begin{itemize}
+\item{\small Leiden University College, {\bfseries Leiden University}, The Hague, NLD}
+\begin{itemize}
+\item[$\circ$]{\small Governance and Development (undergraduate lecture), spring 2025}
+\end{itemize}
+\item{\small Faculty of Administration and Economics, {\bfseries Universidad Diego Portales}, Santiago, CHL}
+\begin{itemize}
+\item[$\circ$]{\small Data Mining (PhD lecture), spring 2024}
+\item[$\circ$]{\small Political Economy (MPP lecture), fall 2024}
+\end{itemize}
 \item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, CHL}
@@
 \end{itemize}
-\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago de Chile}, Santiago, CHL}
+\item{\small Faculty of Administration and Economics, {\bfseries Universidad de Santiago de Chile}, Santiago, CHL}
 \begin{itemize}

### 2025-01-15 short/sections/future-papers.tex
Update future-papers.tex
LUCDH grant

@@
 
-\cvsection{Working Papers}
+\cvsection{Papers Under Review}
 
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{8}
 
-\item{González-Bustamante, B.
-(2024, {\itshape second round of review}).
-Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets.
-Preprint upon request.}\vspace{1mm}
-
-\item{González-Bustamante, B.
-(2024, {\itshape first round of review}).
-Resignation Calls, Reallocations and Individual Ministerial Terminations in Presidential Democracies.
-{\bfseries Job market paper}.}\vspace{1mm}
-
-\item{González-Bustamante, B.
-(2024, {\itshape first round of review}).
-Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval.
-Preprint upon request.}\vspace{1mm}
-
-\item{González-Bustamante, B.
-(2024, {\itshape first round of review}).
-Benchmarking LLMs in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data.
-arXiv preprint.
-DOI: \href{https://doi.org/10.48550/arXiv.2409.09741}{\textcolor{blue}{10.48550/arXiv.2409.09741}}.}\vspace{1mm}
-
-\item{González-Bustamante, B., \& Kantorowicz, J.
-(2024, {\itshape first round of review}).
-Cross-Lingual Word Embeddings for Unravelling the Rule of Law in European Countries.
-OSF preprint.
-DOI: \href{https://doi.org/10.31219/osf.io/m65re}{\textcolor{blue}{10.31219/osf.io/m65re}}.}\vspace{1mm}
-
-\item{González-Bustamante, B., \& Rivera, S.
-(2024, {\itshape first round of review}).
-Toxicity and Digital Incivility during Political Deliberation: The Case of the Constitutional Convention in Chile.
-Preprint upon request.}\vspace{1mm}
+\item{González-Bustamante, B. (2025, {\itshape second round}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. Preprint upon request.}\vspace{1mm}
 
 \item{Kantorowicz, J., \& González-Bustamante, B.
-(2024, {\itshape first round of review}).
+(2025, {\itshape second round}).
 Changing Meaning of the Rule of Law.
@@
 \item{Kantorowicz, J., \& González-Bustamante, B.
-(2024, {\itshape first round of review}).
+(2025, {\itshape second round}).
 Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis.
@@
 
+\item{DiGiuseppe, M., Aspide, A., Kantorowicz, J.
+\& González-Bustamante, B.
+(2025, {\itshape first round}).
+Putting the Public Back in Public Debt: Citizen Narratives on Public Debt Burdens.Preprint upon request.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2024, {\itshape first round}).
+Benchmarking LLMs in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data.
+arXiv preprint.
+DOI: \href{https://doi.org/10.48550/arXiv.2409.09741}{\textcolor{blue}{10.48550/arXiv.2409.09741}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2024, {\itshape first round}).
+Resignation Calls, Reallocations and Individual Ministerial Terminations in Presidential Democracies.
+Preprint upon request.}\vspace{1mm} %% \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Kantorowicz, J.
+(2024, {\itshape first round}).
+Cross-Lingual Word Embeddings for Unravelling the Rule of Law in European Countries.
+OSF preprint.
+DOI: \href{https://doi.org/10.31219/osf.io/m65re}{\textcolor{blue}{10.31219/osf.io/m65re}}.}\vspace{1mm}
+
+%% \item{González-Bustamante, B., \& Rivera, S.
+(2024, {\itshape first round}).
+Toxicity and Digital Incivility during Political Deliberation: The Case of the Constitutional Convention in Chile.
+Preprint upon request.}\vspace{1mm}
+
 \item{Orchard, X., González-Bustamante, B., \& Cisternas.
 C.
-(2024, {\itshape first round of review}).
+(2024, {\itshape first round}).
 Amplification, Contestation, and Toxic Interactions with News: Testing the Effect of a Protest Cycle in Digital News Participation.

### 2025-01-15 short/sections/summary.tex
Update summary.tex

--- 2024-07-29 short/sections/summary.tex
@@
 
-\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration at the Faculty of Governance and Global Affairs at Leiden University, Netherlands.
-I hold a DPhil (PhD) in Politics from the University of Oxford, United Kingdom.
-Before my DPhil, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.}
+\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration, Faculty of Governance and Global Affairs, Leiden University, the Netherlands.
+I hold a DPhil (PhD) in Politics from the University of Oxford, UK, and prior to that, I completed an MA (1st) in Political Science and a BA (2:1) in Government at the Universidad de Chile.}
 
-\textcolor{black}{My research interests lie in the intersection of comparative politics and government, focusing mainly on cabinets, political regimes and civil services.
-Methodologically, my interests rely on the application of quantitative text analysis, machine learning methods and causal inference strategies in the comparative politics field.
-In the last years, my work has been published in {\itshape The International Journal of Press/Politics}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The British Journal of Politics and International Relations}, {\itshape Bulletin of Latin American Research} and elsewhere.}
+\textcolor{black}{My research, which initially focused on comparative politics and government, particularly cabinets, political regimes and civil services, has now expanded to explore the emerging field of digital governance and other policy domains.
+My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics} and elsewhere.}
 
-\textcolor{black}{During my post-doctorate at Leiden, I am working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments.
-Specifically, I employ Natural Language Processing (NLP) and text-as-data techniques to find patterns and topics within big text data.}
+\textcolor{black}{During my current postdoctoral appointment, I am mainly contributing to an NWO-funded project on automated text analysis of investment data, investigating how governance structures shape sustainable investments.
+Specifically, I use Natural Language Processing (NLP) and text-as-data methods to identify patterns and topics within large-scale textual corpora.
+In addition, I teach the Institutions of Governance and Development course at Leiden University College.}
 \vspace{1mm}

### 2025-01-28 sections/papers.tex
Update papers.tex

@@
 
-\cvsubsection{Social Sciences Citation Index (WoS-SSCI, ex ISI)}
+\cvsubsection{Social Sciences Citation Index (WoS-SSCI)}
 
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
+
+\item{González-Bustamante, B.
+(2025).
+Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets.
+{\itshape Social Science Computer Review}.
+\\ DOI :\href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
+
+\item{Fleming, T.
+G., González-Bustamante, B., \& Schleiter, P.
+(2024).
+Cabinet Reshuffles and Parliamentary No-Confidence Motions.
+{\itshape Government and Opposition, 59}(4), 1274--1288.
+DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 
@@
 \item{González-Bustamante, B.
-(2022).
+(2023).
 Ministerial stability during presidential approval crises: The moderating effect of ministers’ attributes on dismissals in Brazil and Chile.
@@
 DOI: \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
-
-\item{Fleming, T.
-G., González-Bustamante, B., \& Schleiter, P.
-(2022).
-Cabinet Reshuffles and Parliamentary No-Confidence Motions.
-{\itshape Government and Opposition}.
-FirstView.
-DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 

### 2025-01-28 short/sections/selected-papers.tex
LUCDH grant
Update selected-papers.tex

@@
 
-\begin{benumerate}{8}
+\begin{benumerate}{9}
+
+\item{González-Bustamante, B.
+(2025).
+Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets.
+{\itshape Social Science Computer Review}.
+\\ DOI :\href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
+
+\item{Fleming, T.
+G., González-Bustamante, B., \& Schleiter, P.
+(2024).
+Cabinet Reshuffles and Parliamentary No-Confidence Motions.
+{\itshape Government and Opposition, 59}(4), 1274--1288.
+DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 
@@
 SocArXiv: \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
-
-\item{Fleming, T.
-G., González-Bustamante, B., \& Schleiter, P.
-(2022).
-Cabinet Reshuffles and Parliamentary No-Confidence Motions.
-{\itshape Government and Opposition}.
-FirstView.
-DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 

### 2025-01-28 short/sections/summary.tex
Update summary.tex

@@
 \textcolor{black}{My research, which initially focused on comparative politics and government, particularly cabinets, political regimes and civil services, has now expanded to explore the emerging field of digital governance and other policy domains.
-My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics} and elsewhere.}
+My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics and International Relations} and elsewhere.}
 

### 2025-02-08 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{10}
 
@@
 {\itshape Social Science Computer Review}.
-\\ DOI :\href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
+\\ DOI :\href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.
+\faBriefcase\ $\,$ {\bfseries Writing sample}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
 
@@
 
-%% \item{González-Bustamante, B., Carvajal, A., \& González, A.
+\item{González-Bustamante, B., Carvajal, A., \& González, A.
 (2020).

### 2025-02-08 short/sections/training.tex
Create training.tex

--- 2024-10-08 short/sections/projects.tex
@@
 
-\cvsection{Relevant Research Projects}
+\cvsection{Relevant Certification \& Training}
 
@@
 \cvhonor
-{Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
-{NWO VIDI SWG Project VI.Vidi.211.226, {\bfseries PostDoc} (Natascha van der Zwan, PI), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
-{Dutch Research Agency}
+{KODAQS Data Quality Academy Certificate Program, University of Mannheim} 
+{Data quality dimensions, indicators and metrics to assess data quality, tools and data quality, data management procedures, reproducibility} 
+{Mannheim, DEU}
+{2025}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
+{ODISSEI Summer Institute in Computational Social Science} 
+{Network analysis, machine learning, benchmarking and ethics} 
+{Rotterdam, NLD}
 {2024}
@@
 \cvhonor
-{Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
-{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), {\bfseries PI}, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
-{UDP}
-{2024}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
-{OpenAI Academic Programme, {\bfseries PI}, about USD\$5 000. Period: 2024.}
-{OpenAI}
-{2024}
-\end{cvhonors}
-
-\vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{Unravelling the Rule of Law: A Machine Learning Approach}
-{NWO XS Project 406.XS.01.013, {\bfseries PostDoc} (Jaroslaw Kantorowicz, PI), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
-{Dutch Research Agency}
+{Introduction to Learning and Teaching at Oxford} 
+{Foundations for inclusive teaching and strategies to support efficient and effective preparation for teaching} 
+{Oxford, GBR}
 {2023}
@@
 \cvhonor
-{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
-{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), {\bfseries PI}, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
-{USACH}
-{2022}
+{Oxford|Berlin Summer School on Open Research} 
+{Training in biases in research, reproducibility, publishing, open data, open materials, meta-research and ethical conduct of research} 
+{Oxford, GBR}
+{2021}
 \end{cvhonors}
@@
 \vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
-{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), {\bfseries Research Associate} (Ximena Orchard, PI), about USD\$4 000.
-Period: 2019.} %% {\pounds} 3 000
-{UAH}
-{2019}
-\end{cvhonors}
-
-\vspace{1mm}
+%% \pagebreak

### 2025-02-08 sections/references.tex
Update references.tex

@@
 \begin{itemize}
+\item[]{\small {\bfseries Natascha van der Zwan}, Associate Professor, Leiden University, NLD}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:n.a.j.van.der.zwan@fgga.leidenuniv.nl}{\textcolor{blue}{n.a.j.van.der.zwan@fgga.leidenuniv.nl}}}} \vspace{1.5mm}
 \item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, GBR}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries David Doyle}, Professor of Politics, University of Oxford, GBR}
+\item[]{\small {\bfseries David Doyle}, Head of Department and Professor of Politics, University of Oxford, GBR}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
@@
 %% \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small %% \href{mailto:rcarlin@gsu.edu}{\textcolor{blue}{rcarlin@gsu.edu}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries Jaroslaw Kantorowicz}, Associate Professor, Leiden University, NLD}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:j.j.kantorowicz@fgga.leidenuniv.nl}{\textcolor{blue}{j.j.kantorowicz@fgga.leidenuniv.nl}}}} \vspace{1.5mm}
+%% \item[]{\small {\bfseries Jaroslaw Kantorowicz}, Associate Professor, Leiden University, NLD}
+%% \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:j.j.kantorowicz@fgga.leidenuniv.nl}{\textcolor{blue}{j.j.kantorowicz@fgga.leidenuniv.nl}}}} \vspace{1.5mm}
 \end{itemize}

### 2025-02-08 sections/references.tex
Update references.tex

@@
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:n.a.j.van.der.zwan@fgga.leidenuniv.nl}{\textcolor{blue}{n.a.j.van.der.zwan@fgga.leidenuniv.nl}}}} \vspace{1.5mm}
+\item[]{\small {\bfseries Jaroslaw Kantorowicz}, Associate Professor, Leiden University, NLD}
+\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:j.j.kantorowicz@fgga.leidenuniv.nl}{\textcolor{blue}{j.j.kantorowicz@fgga.leidenuniv.nl}}}} \vspace{1.5mm}
 \item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, GBR}
 \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
-\item[]{\small {\bfseries David Doyle}, Head of Department and Professor of Politics, University of Oxford, GBR}
-\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
+%% \item[]{\small {\bfseries David Doyle}, Head of Department and Professor of Politics, University of Oxford, GBR}
+%% \item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
 %% \item[]{\small {\bfseries Ryan E. Carlin}, Professor of Political Science, Georgia State University, USA}

### 2025-02-08 short/sections/training.tex
Update training.tex

@@
 {KODAQS Data Quality Academy Certificate Program, University of Mannheim} 
-{Data quality dimensions, indicators and metrics to assess data quality, tools and data quality, data management procedures, reproducibility} 
+{Data quality dimensions, indicators and metrics to assess data quality, tools and data quality, data management procedures and reproducibility} 
 {Mannheim, DEU}

### 2025-02-12 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 {\itshape Social Science Computer Review}.
-\\ DOI :\href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.
-\faBriefcase\ $\,$ {\bfseries Writing sample}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
+\faBriefcase\ {\bfseries Writing sample}.
+DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
 
@@
 
-%% \item{González-Bustamante, B.
+\item{González-Bustamante, B.
 (2019).
@@
 
-%% \pagebreak
+ \pagebreak

### 2025-02-12 short/sections/summary.tex
Update summary.tex

@@
 
-\textcolor{black}{My research, which initially focused on comparative politics and government, particularly cabinets, political regimes and civil services, has now expanded to explore the emerging field of digital governance and other policy domains.
+\textcolor{black}{From an earlier focus on cabinets and civil service, I have developed an active research agenda on how emerging technologies ---including AI--- shape policymaking and the organisation of bureaucracies.
 My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics and International Relations} and elsewhere.}

### 2025-04-16 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 
-\begin{benumerate}{11}
+\begin{benumerate}{13}
+
+\item{González-Bustamante, B.
+(2025, {\itshape forthcoming}).
+Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval.
+{\itshape Public Opinion Quarterly}.
+Preprint upon request.}\vspace{1mm}
 
@@
 {\itshape Social Science Computer Review}.
-\faBriefcase\ {\bfseries Writing sample}.
-DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}
+\\ DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper / Writing sample}.}\vspace{1mm}
 
@@
 
-%% \item{González-Bustamante, B., \& Garrido-Vergara, L.
+\item{González-Bustamante, B., \& Garrido-Vergara, L.
 (2018).
@@
 
- \pagebreak
+ %% \pagebreak

### 2025-06-06 sections/languages.tex
Update languages.tex

@@
 {Languages} 
-{\textcolor{black}{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}}
+{\textcolor{black}{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Dutch,}}
 
@@
 {} 
-{\textcolor{black}{(elemental reading skills), French (elemental reading skills)}} \\
+{\textcolor{black}{French and Italian (elemental reading skills)}} \\
 

### 2025-06-06 short/sections/future-papers.tex
Update future-papers.tex

@@
 
-\begin{benumerate}{8}
+\begin{benumerate}{6}
 
-\item{González-Bustamante, B. (2025, {\itshape second round}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. Preprint upon request.}\vspace{1mm}
+\item{Orchard, X., González-Bustamante, B., \& Cisternas, C.
+(2025, {\itshape second round}).
+Amplification, Contestation, and Toxic Interactions with News: Testing the Effect of a Protest Cycle in Digital News Participation.
+Preprint upon request.}\vspace{1mm}
+
+\item{DiGiuseppe, M., Aspide, A., Kantorowicz, J., \& González-Bustamante, B.
+(2025, {\itshape second round}).
+Putting the Public Back in Public Debt: Citizen Narratives on Public Debt Burdens.
+Preprint upon request.}\vspace{1mm}
 
 \item{Kantorowicz, J., \& González-Bustamante, B.
-(2025, {\itshape second round}).
-Changing Meaning of the Rule of Law.
-OSF preprint.
-DOI: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
-
-\item{Kantorowicz, J., \& González-Bustamante, B.
-(2025, {\itshape second round}).
+(2024, {\itshape first round}).
 Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis.
@@
 DOI: \href{https://doi.org/10.31219/osf.io/sgf8y}{\textcolor{blue}{10.31219/osf.io/sgf8y}}.}\vspace{1mm}
-
-\item{DiGiuseppe, M., Aspide, A., Kantorowicz, J.
-\& González-Bustamante, B.
-(2025, {\itshape first round}).
-Putting the Public Back in Public Debt: Citizen Narratives on Public Debt Burdens.Preprint upon request.}\vspace{1mm}
 
@@
 
-\item{Orchard, X., González-Bustamante, B., \& Cisternas.
-C.
-(2024, {\itshape first round}).
-Amplification, Contestation, and Toxic Interactions with News: Testing the Effect of a Protest Cycle in Digital News Participation.
-Preprint upon request.}\vspace{1mm}
-
 \end{benumerate}

### 2025-06-06 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 
-\begin{benumerate}{13}
+\begin{benumerate}{14}
+
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2025, {\itshape forthcoming}).
+Changing Meaning of the Rule of Law.
+OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
 
@@
 {\itshape Public Opinion Quarterly}.
-Preprint upon request.}\vspace{1mm}
+SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v1}{\textcolor{blue}{10.31235/osf.io/37ruy\_v1}}.}\vspace{1mm}
 
@@
 {\itshape Política y Gobierno, XXV}(1), 31--64.
-{\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
+URL: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
 

### 2025-06-06 short/sections/summary.tex
Update summary.tex

@@
 
-\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration, Faculty of Governance and Global Affairs, Leiden University, the Netherlands.
-I hold a DPhil (PhD) in Politics from the University of Oxford, UK, and prior to that, I completed an MA (1st) in Political Science and a BA (2:1) in Government at the Universidad de Chile.}
+\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at Leiden University’s Institute of Public Administration, Faculty of Governance and Global Affairs, in the Netherlands.
+I hold a DPhil (PhD) in Politics from the University of Oxford and previously earned an MA in Political Science and a BA in Public Administration and Government from the Universidad de Chile.}
 
-\textcolor{black}{From an earlier focus on cabinets and civil service, I have developed an active research agenda on how emerging technologies ---including AI--- shape policymaking and the organisation of bureaucracies.
-My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics and International Relations} and elsewhere.}
+\textcolor{black}{My work bridges the fields of comparative politics, public administration, and computational social science.
+I build large-scale text-as-data pipelines, deploy AI and machine learning models, and apply causal inference strategies to gain insights into executive politics and elite behaviour.
+This agenda centres on cabinet reshuffles, ministerial survival, civil service dynamics, and blame-shifting, while also engaging with broader debates on policy agendas, bureaucratic careers, and digital governance.}
 
-\textcolor{black}{During my current postdoctoral appointment, I am mainly contributing to an NWO-funded project on automated text analysis of investment data, investigating how governance structures shape sustainable investments.
-Specifically, I use Natural Language Processing (NLP) and text-as-data methods to identify patterns and topics within large-scale textual corpora.
-In addition, I teach the Institutions of Governance and Development course at Leiden University College.}
+\textcolor{black}{My recent peer-reviewed articles have appeared in {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, among others.
+I regularly present at IPSA, ECPR, EPSA and COMPTEXT.
+I am currently working on an NWO-funded project that uses Large Language Models (LLMs) to analyse global investment prospectuses and reveal how governance arrangements shape sustainable finance flows.
+In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers and lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies.”}
+
+\textcolor{black}{In addition to research, I convene the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
 \vspace{1mm}

### 2025-07-09 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 
-\item{Kantorowicz, J., \& González-Bustamante, B.
-(2025, {\itshape forthcoming}).
-Changing Meaning of the Rule of Law.
-OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
-
 \item{González-Bustamante, B.
@@
 
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2025).
+Changing Meaning of the Rule of Law.
+{\itshape Artificial Intelligence and Law}.
+OnlineFirst.
+DOI: \href{https://doi.org/10.1007/s10506-025-09468-4}{\textcolor{blue}{https://doi.org/10.1007/s10506-025-09468-4}}.
+OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
+
 \item{González-Bustamante, B.
@@
 {\itshape Social Science Computer Review}.
-\\ DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper / Writing sample}.}\vspace{1mm}
+OnlineFirst.
+DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper / Writing sample}.}\vspace{1mm}
 

### 2025-07-09 short/sections/summary.tex
Update summary.tex

@@
 
-\textcolor{black}{In addition to research, I convene the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
+\textcolor{black}{In addition to research, I teach the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
 \vspace{1mm}

### 2025-08-08 short/sections/summary.tex
Update summary.tex

@@
 
-\textcolor{black}{My work bridges the fields of comparative politics, public administration, and computational social science.
+%% \textcolor{black}{My work bridges the fields of comparative politics, public administration, and computational social science.
 I build large-scale text-as-data pipelines, deploy AI and machine learning models, and apply causal inference strategies to gain insights into executive politics and elite behaviour.
@@
 
-\textcolor{black}{My recent peer-reviewed articles have appeared in {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, among others.
+%% \textcolor{black}{My recent peer-reviewed articles have appeared in {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, among others.
 I regularly present at IPSA, ECPR, EPSA and COMPTEXT.
 I am currently working on an NWO-funded project that uses Large Language Models (LLMs) to analyse global investment prospectuses and reveal how governance arrangements shape sustainable finance flows.
+In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers and lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies.”}
+
+\textcolor{black}{My work bridges the fields of comparative politics and computational social science.
+I build large-scale text-as-data pipelines, deploy AI and machine learning models, and apply causal inference strategies.
+My recent peer-reviewed articles have appeared in {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, among others.
+I regularly present at IPSA, ECPR, EPSA and COMPTEXT.}
+
+\textcolor{black}{I am currently working on an NWO-funded project that uses Large Language Models (LLMs) to analyse global investment prospectuses and reveal how governance arrangements shape sustainable finance flows.
 In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers and lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies.”}

### 2025-09-08 short/sections/selected-papers.tex
Update selected-papers.tex

@@
 {\itshape Public Opinion Quarterly}.
-SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v1}{\textcolor{blue}{10.31235/osf.io/37ruy\_v1}}.}\vspace{1mm}
+SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v2}{\textcolor{blue}{10.31235/osf.io/37ruy\_v2}}.}\vspace{1mm}
 
@@
 OnlineFirst.
-DOI: \href{https://doi.org/10.1007/s10506-025-09468-4}{\textcolor{blue}{https://doi.org/10.1007/s10506-025-09468-4}}.
+DOI: \href{https://doi.org/10.1007/s10506-025-09468-4}{\textcolor{blue}{10.1007/s10506-025-09468-4}}.
 OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
@@
 (2025).
-Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets.
+Machine Learning and Political Events: Application of a Semi-supervised Approach to Produce a Dataset on Presidential Cabinets.
 {\itshape Social Science Computer Review}.

### 2025-09-08 spanish/sections/awards.tex
Update awards.tex

@@
 \cvhonor
+{Premio a la Trayectoria Académica Temprana}
+{Mejor trabajo al inicio de la carrera académica y ayuda de viaje para la conferencia BigSurv23.} %% , {\pounds} 525.}
+{Quito, ECU}
+{2023}
+\end{cvhonors}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
 {Premio para las Sesiones Conjuntas de Talleres de ECPR} 
-{Ayuda de viaje para las Sesiones Conjuntas de Talleres del Consorcio Europeo de Investigación Política (ECPR), {\pounds} 1 350.}
+{Ayuda de viaje para las Sesiones Conjuntas de Talleres del Consorcio Europeo de Investigación Política (ECPR).} %% , {\pounds} 1 350.}
 {Toulouse, FRA}
@@
 {Premio de investigación de postgrado y postdoctoral SLAS y beca para conferencia} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS), {\pounds} 1 400.}
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y apoyo financiero para participar en la conferencia anual de la Sociedad de Estudios Latinoamericanos (SLAS).} %% , {\pounds} 1 400.}
 {Bath, GBR}
@@
 {Fondo Muriel Wise de St Hilda's College y beca para viajes y libros} 
-{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros, {\pounds} 2 255.} 
+{Beca de apoyo a la investigación para mi proyecto de DPhil (PhD) y asignaciones para la participación en conferencias y la compra de libros.} %% , {\pounds} 2 255.} 
 {Oxford, GBR}
@@
 {Beca Doctorado en el Extranjero Becas Chile} 
-{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
+{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340).} %% , {\pounds} 160 000.}
 {Oxford, GBR}
@@
 %% {Beca de Viaje LASA} 
-%% {Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), {\pounds} 400}
+%% {Apoyo financiero para participar en el XXXIV Congreso Internacional de la Asociación de Estudios Latinoamericanos (LASA/40071), {\pounds} 400.}
 %% {Nueva York, USA}
@@
 {Beca para investigación de Magíster FONDECYT}
-{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
+{Apoyo financiero para el trabajo de campo de Magíster (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877).} %% , {\pounds} 1 150.}
 {Santiago, CHL}

### 2025-09-08 spanish/sections/experience.tex
Update experience.tex

@@
 \cventry
-{Investigador Post-Doctoral en Ciencias Sociales Computacionales} 
+{Profesor Asociado} 
+{Universidad Diego Portales (UDP)} 
+{Santiago, CHL} 
+{2024 - Hoy}
+{Escuela de Administración Pública, Facultad de Administración y Economía} \vspace{1.5mm}
+
+\cventry
+{Investigador Postdoctoral en Ciencias Sociales Computacionales} 
 {Universidad de Leiden} 
 {La Haya, NLD} 
-{comienza 1 dic. 2023 - 2026}
+{2023 - Hoy}
 {Instituto de Administración Pública, Facultad de Gobernanza y Asuntos Globales} \vspace{1.5mm}
+\end{cventries}
+%% \pagebreak
 
+\cvsection{Experiencia profesional relevante}
+
+\begin{cventries}
 \cventry
@@
 {Santiago, CHL} 
-{2019 - en comisión}
+{2019 - 2023}
 {Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
-\end{cventries}
-\pagebreak
 
-\cvsection{Experiencia profesional relevante}
-
-\begin{cventries}
 \cventry

### 2025-09-08 spanish/sections/languages.tex
Update languages.tex

@@
 {} 
-{\textcolor{black}{italiano (habilidades de lectura elementales), francés (habilidades de lectura elementales)}} \\
+{\textcolor{black}{francés e italiano (habilidades de lectura elementales)}} \\
 
@@
 {Programación \&} 
-{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}
+{\textcolor{black}{Python, R, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}
 
@@
 {software} 
-{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
+{\textcolor{black}{{\scshape HPoP}, Zotero, JabRef, {\LaTeX}, Bib{\TeX}, MS Office, WordPress, Moodle, {\scshape java}, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
 

### 2025-09-08 spanish/sections/papers.tex
Update papers.tex

--- 2023-09-23 spanish/sections/papers.tex
@@
 
-\begin{benumerate}{9}
+\begin{benumerate}{12}
 
 \item{González-Bustamante, B.
-(2022).
-Ministerial stability during presidential approval crises: The moderating effect of ministers' attributes on dismissals in Brazil and Chile.
-{\itshape The British Journal of Politics and International Relations}.
+(2025, {\itshape próximamente}).
+Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval.
+{\itshape Public Opinion Quarterly}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v2}{\textcolor{blue}{10.31235/osf.io/37ruy\_v2}}.}\vspace{1mm}
+
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2025).
+Changing Meaning of the Rule of Law.
+{\itshape Artificial Intelligence and Law}.
 OnlineFirst.
-{\scshape doi:} \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1007/s10506-025-09468-4}{\textcolor{blue}{10.1007/s10506-025-09468-4}}.
+OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2025).
+Machine Learning and Political Events: Application of a Semi-supervised Approach to Produce a Dataset on Presidential Cabinets.
+{\itshape Social Science Computer Review}.
+OnlineFirst.
+DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm}
 
@@
 G., González-Bustamante, B., \& Schleiter, P.
-(2022).
+(2024).
 Cabinet Reshuffles and Parliamentary No-Confidence Motions.
-{\itshape Government and Opposition}.
-FirstView.
-{\scshape doi:} \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
+{\itshape Government and Opposition, 59}(4), 1274--1288.
+DOI: \href{https://doi.org/10.1017/gov.2022.23}{\textcolor{blue}{10.1017/gov.2022.23}}.}\vspace{1mm}
 
 \item{Orchard, X., \& González-Bustamante, B.
-(2022).
+(2024).
 Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019).
-{\itshape The International Journal of Press/Politics}.
-OnlineFirst.
-{\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}
+{\itshape The International Journal of Press/Politics, 29}(1), 100--123.
+DOI: \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+Ministerial stability during presidential approval crises: The moderating effect of ministers' attributes on dismissals in Brazil and Chile.
+{\itshape The British Journal of Politics and International Relations, 25}(4), 655--675.
+DOI: \href{https://doi.org/10.1177/13691481221124850}{\textcolor{blue}{10.1177/13691481221124850}}.}\vspace{1mm}
 
@@
 {\itshape Revista del CLAD Reforma y Democracia}, 81, 105--138.
-{\scshape url:} \\ \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
+URL: \\ \href{https://clad.org/documentacion/revista-clad/articulos-publicados/081-noviembre-2021/}{\textcolor{blue}{https://clad.org}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}.}\vspace{1mm}
 
@@
 {\itshape Bulletin of Latin American Research, 39}(5), 582--597.
-{\scshape doi}: \\ \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
+DOI: \\ \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}
 
@@
 {\itshape Political Research Exchange, 5}(1).
-{\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+DOI: \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}
+
+\item{González-Bustamante.
+B.
+(2022).
+Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
+{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
+DOI: \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
 
@@
 {\itshape Latin American Business Review, 20}(4), 367--387.
-{\scshape doi}: \\ \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
+DOI: \\ \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}
 
@@
 {\itshape Perspectivas de la Comunicación, 11}(1), 291--326.
-{\scshape url:} \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
+URL: \href{https://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{\textcolor{blue}{https://revistas.ufro.cl}}.}\vspace{1mm}
 
@@
 {\itshape Revista de Administra\c{c}\~ao Pública, 50}(1), 59--79.
-{\scshape doi}: \\ \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
+DOI: \\ \href{http://dx.doi.org/10.1590/0034-7612145767}{\textcolor{blue}{10.1590/0034-7612145767}}.} \vspace{1mm}
 
@@
 
-\begin{benumerate}{14}
+\begin{benumerate}{15}
 
-\item{González-Bustamante.
-B.
-(2022).
-Métodos cuantitativos para estudiar a las élites: Aplicaciones prácticas, sesgos y potencialidades.
-{\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44.
-{\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}.
-{\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
+\item{González-Bustamante, B.
+(2024).
+TextClass Benchmark: A Continuous Elo Rating of LLMs in Social Sciences.
+{\itshape Tufte Working Papers}.
+OnlineFirst.
+arXiv: \href{https://doi.org/10.48550/arXiv.2412.00539}{\textcolor{blue}{10.48550/arXiv.2412.00539}}.}\vspace{1mm}
+
+\item{González-Bustamante, B.
+(2023).
+Análisis de Componentes Principales con correlaciones policóricas: Aplicación en consumo de medios.
+{\itshape Tufte Working Papers}.
+OnlineFirst.
+SocArXiv: \href{https://doi.org/10.31235/osf.io/npc9e}{\textcolor{blue}{10.31235/osf.io/npc9e}}.}\vspace{1mm}
 
@@
 21--32.
-{\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
-\\ {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
+URL: \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}.
+\\ SocArXiv: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}.}\vspace{1mm}
 
@@
 {\itshape Comunifé: Revista de Comunicación Social}, 21, 31--39.
-\\ {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}}.}\vspace{1mm}
+DOI: \\ \href{https://doi.org/10.33539/comunife.2021.n21.2580}{\textcolor{blue}{10.33539/comunife.2021.n21.2580}}.}\vspace{1mm} %% {\scshape url:} \href{https://revistas.unife.edu.pe/index.php/comunife/article/view/2580/}{\textcolor{blue}{https://revistas.unife.edu.pe}
 
@@
 {\itshape Política, Revista de Ciencia Política, 54}(1), 19--52.
-{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+URL: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 {\itshape Política, Revista de Ciencia Política, 54}(1), 7--17.
-{\scshape url:} \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
+URL: \\ \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.}\vspace{1mm}
 
@@
 {\itshape Políticas Públicas, 8}(1), 21--35.
-{\scshape url:} \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
+URL: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{\textcolor{blue}{www.revistas.usach.cl}}.} \vspace{1mm}
 
@@
 {\itshape Revista SAAP, 9}(1), 119--141.
-{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+URL: \href{https://www.redalyc.org/articulo.oa?id=387142733006}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 {\itshape Revista de Sociología,} 29, 37--54.
-{\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}
+URL: \\ \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
 
@@
 {\itshape Política, Revista de Ciencia Política, 52}(2), 49--91.
-{\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
+URL: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
 
@@
 {\itshape Intersticios Sociales,} 6, 1--20.
-{\scshape url:} \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
+URL: \href{https://www.redalyc.org/articulo.oa?id=421739499004}{\textcolor{blue}{www.redalyc.org}}.} \vspace{1mm}
 
@@
 {\itshape Política, Revista de Ciencia Política, 51}(1), 119--153.
-{\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}
+URL: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436}}.
 
@@
 {\itshape Más Poder Local,} 12, 32--39.
-{\scshape url:} \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
+URL: \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4013864}{\textcolor{blue}{https://dialnet.unirioja.es}}.} \vspace{1mm} %% {\scshape url:} \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{\textcolor{blue}{www.researchgate.net}}
 

### 2025-09-08 spanish/sections/summary.tex
Update summary.tex

--- 2022-10-17 spanish/sections/summary.tex
@@
 
-Estoy completando mi tesis doctoral en el Departamento de Ciencia Política y Relaciones Internacionales y en St Hilda’s College en la Universidad de Oxford, Reino Unido.
-Antes de comenzar mis estudios doctorales en octubre de 2019, obtuve un Magíster en Ciencia Política (distinción máxima) y una Licenciatura en Ciencias Políticas y Gubernamentales con mención en Gestión Pública (distinción), ambos en la Universidad de Chile.
-Además, me desempeñé como profesor adjunto y docente en la Universidad de Santiago y Universidad de Chile y como consultor del Programa de las Naciones Unidas para el Desarrollo (PNUD).
+\textcolor{black}{Radicado en los Países Bajos, ocupo dos cargos, soy Profesor Asociado en Administración Pública en la Universidad Diego Portales e investigador posdoctoral en Ciencias Sociales Computacionales en el Instituto de Administración Pública de la Facultad de Gobernanza y Asuntos Globales de la Universidad de Leiden, Países Bajos.
+Tengo un doctorado (DPhil/PhD) en Ciencia Política por la Universidad de Oxford y anteriormente obtuve un Magíster en Ciencia Política, título profesional de Administrador Público y una Licenciatura en Ciencias Políticas y Gubernamentales por la Universidad de Chile.}
 
-Mi investigación doctoral es supervisada por la Profesora Petra Schleiter y se centra en las causas y consecuencias de la rotación ministerial en 12 países presidenciales latinoamericanos desde mediados de los años 70 hasta la fecha.
-Mi proyecto integra elementos de la teoría principal-agente para evaluar los incentivos y las estrategias específicas de los actores en los sistemas presidenciales, considerando las características institucionales del régimen.
-En mi proceso de recopilación de datos, apliqué técnicas de reconocimiento óptico de caracteres (OCR), procesamiento del lenguaje natural (NLP) y aprendizaje automático a casi 50 años de archivos de informes de prensa.
-Además, mi estrategia empírica emplea métodos de emparejamiento de puntuación de propensión, modelos semiparamétricos de riesgos competitivos y regresiones de variables instrumentales.
+\textcolor{black}{Mi trabajo abarca los campos de la política comparada, el gobierno y las ciencias sociales computacionales.
+Creo flujos de trabajo para analizar datos textuales a gran escala, implemento modelos de inteligencia artificial y aprendizaje automático y aplico estrategias de inferencia causal.
+Mis artículos recientes revisados por pares han aparecido en {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, entre otras revistas.
+Presento regularmente en las conferencias de IPSA, ECPR, EPSA y COMPTEXT.}
 
-Mi investigación es financiada por la Agencia Nacional de Investigación y Desarrollo (ANID) de Chile, el Fondo Muriel Wise de St Hilda's College y el Premio de Postgrado y Postdoctorado de la Sociedad de Estudios Latinoamericanos (SLAS).
+\textcolor{black}{Actualmente estoy trabajando en un proyecto financiado por la Agencia Holandesa de Investigación que utiliza grandes modelos de lenguaje (LLMs por sus siglas en inglés) para analizar reportes de inversión globales y revelar cómo los acuerdos de gobernanza configuran los flujos financieros sostenibles.
+Paralelamente, colaboro en la Acción COST CA22150 sobre carreras ejecutivas y burocráticas y dirijo el proyecto Enlace-Inserción UDP 2025-2026 “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies''.}
+
+\textcolor{black}{Además de dedicarme a la investigación, imparto la asignatura de pregrado Instituciones de Gobernanza y Desarrollo en el Leiden University College y doy clases de doctorado sobre minería de datos e inteligencia artificial en la Universidad Diego Portales.}
 \vspace{1mm}

### 2025-09-08 spanish/sections/teaching.tex
Update teaching.tex

@@
 \begin{itemize}
-\item{\small Escuela de Negocios, {\bfseries Universidad Mayor}, Santiago, CHL}
+\item[{\scriptsize ■}]{\small Leiden University College, {\bfseries Universidad de Leiden}, La Haya, NLD}
 \begin{itemize}
-\item[$\circ$]{\small Aprendizaje Automático para Políticas Públicas y Economía (taller, Prof. Carla Cisternas), primavera 2021}
+\item[$\circ$]{\small Gobernanza y Desarrollo (curso de pregrado), primavera 2025-2026}
 \end{itemize} 
-\item{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, GBR}
+\end{itemize} 
 \begin{itemize}
-\item[$\circ$]{\small Gobierno Comparado (tutorial de pregrado, Prof. Petra Schleiter), Hilary 2020}
+\item[{\scriptsize ■}]{\small Facultad de Administración y Economía, {\bfseries Universidad Diego Portales}, Santiago, CHL}
+\begin{itemize}
+\item[$\circ$]{\small Introducción a la Inteligencia Artificial (curso de Doctorado), primavera 2025}
+\item[$\circ$]{\small Minería de Datos (curso de Doctorado), primavera 2024-2025}
+\item[$\circ$]{\small Economía Política (curso de Magíster), otoño 2024-2025}
 \end{itemize} 
-\item{\small Facultad de Administración y Economía, {\bfseries Universidad de Santiago}, Santiago, CHL}
+\end{itemize} 
+\begin{itemize}
+\item[{\scriptsize ■}]{\small Escuela de Negocios, {\bfseries Universidad Mayor}, Santiago, CHL}
+\begin{itemize}
+\item[$\circ$]{\small Aprendizaje Automático para Políticas Públicas y Economía (taller), primavera 2021}
+\end{itemize} 
+\item[{\scriptsize ■}]{\small Departamento de Política y Relaciones Internacionales, {\bfseries Universidad de Oxford}, Oxford, GBR}
+\begin{itemize}
+\item[$\circ$]{\small Gobierno Comparado (tutorial de pregrado), Hilary 2020}
+\end{itemize} 
+\item[{\scriptsize ■}]{\small Facultad de Administración y Economía, {\bfseries Universidad de Santiago de Chile}, Santiago, CHL}
 \begin{itemize}
@@
 \end{itemize}
-\item{\small Escuela de Gobierno y Gestión Pública, {\bfseries Universidad de Chile}, Santiago, CHL}
+\item[{\scriptsize ■}]{\small Escuela de Gobierno y Gestión Pública, {\bfseries Universidad de Chile}, Santiago, CHL}
 \begin{itemize}
@@
 \item[$\circ$]{\small Análisis Político (curso de pregrado), otoño 2014}
-\item[$\circ$]{\small Elitismo y Democracia (curso de pregrado, Prof. Alejandro Olivares), primavera 2013-2014}
+\item[$\circ$]{\small Elitismo y Democracia (curso de pregrado), primavera 2013-2014}
 \end{itemize}
@@
 \end{publications}
- \pagebreak
+ %% \pagebreak

### 2025-09-08 spanish/sections/working-papers.tex
Update working-papers.tex

--- 2022-10-17 spanish/sections/working-papers.tex
@@
 
-\cvsection{Proyectos de recopilación de datos}
+%% \cvsection{Proyectos de recopilación de datos}
 
-\begin{publications}
+%% \begin{publications}
 
-\begin{benumerate}{3}
+%% \begin{benumerate}{5}
 
-\item{\small González-Bustamante, B., \& Aguilar, D.
-(2022).
-Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set].
-Versión previa al lanzamiento bajo acceso restringido.
-{\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}
+%% \item{González-Bustamante, B., \& Aguilar, D.
+(2023).
+Data Set on Local Government Indicators in Chile (Version 0.20.15 -- Late Sky).
+Dataset, versión previa al lanzamiento, University of Oxford, Universidad de Santiago de Chile (USACH) y Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.7568387}{\textcolor{blue}{10.5281/zenodo.7568387}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set].
+%% \item{González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Ministers (1990-2014) (Version 3.3.7 -- Soft Dew).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor y Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}
 
-\item{González-Bustamante, B., \& Olivares, A.
-(2022).
-Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set].
+%% \item{González-Bustamante, B., \& Olivares, A.
+(2023).
+Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass).
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor y Training Data Lab.
 {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}
 
-\end{benumerate}
+%% \item{González-Bustamante, B., Olivares, A., Cisternas, C., \& Cuevas, R.
+(2023).
+Chilean Political Science Ranking.
+Dataset, University of Oxford, Universidad de Santiago de Chile (USACH) y Training Data Lab.
+{\scshape doi:} \\ \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}
 
-\end{publications}
-\pagebreak
+%% \item{González-Bustamante, B., Astete, M., \& Orvenes, B.
+(2021).
+Survival of the Senior Civil Servants in the Chilean Executive Branch (Version 1.13.19 -- Bold Lab).
+Dataset, versión previa al lanzamiento bajo acceso restringido, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab.
+{\scshape doi:} \href{https://doi.org/10.5281/zenodo.8115596}{\textcolor{blue}{10.5281/zenodo.8115596}}.}\vspace{1mm}
+
+%% \end{benumerate}
+
+%% \end{publications}
+%% \pagebreak
 
@@
 
-\begin{benumerate}{4}
+\begin{benumerate}{8}
 
-\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B.
+(2025).
+Charting Reproducibility and Performance: LLMs in Multilingual Toxic Speech Detection.
+Paper presented at the LLM Pre-Conference Workshop, European Political Science Association (EPSA), Universidad Carlos III de Madrid, Madrid, Spain, June 25.
+URL: \href{https://talkingtomachines.org/large-language-models-workshop/}{\textcolor{blue}{https://talkingtomachines.org}}.}\vspace{1mm}
+
+\item{González-Bustamante,B.
+(2024).
+Benchmarking LLMs in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data.
+Paper presented at the 8th Monash-Warwick-Zurich Text-as-Data Workshop, September 16-17.
+arXiv: \href{https://doi.org/10.48550/arXiv.2409.09741}{\textcolor{blue}{10.48550/arXiv.2409.09741}}.}\vspace{1mm}
+
+\item{González-Bustamante, B., \& Kantorowicz, J.
+(2024).
+Cross-Lingual Word Embeddings for Unravelling the Rule of Law in European Countries.
+Preprint.
+OSF: \href{https://doi.org/10.31219/osf.io/m65re}{\textcolor{blue}{10.31219/osf.io/m65re}}.}\vspace{1mm}
+
+\item{Kantorowicz, J., \& González-Bustamante, B.
+(2024).
+Exploring the Rule of Law in Academic Discourse: A Comprehensive Bibliometric Analysis.
+Preprint.
+OSF: \href{https://doi.org/10.31219/osf.io/sgf8y}{\textcolor{blue}{10.31219/osf.io/sgf8y}}.}\vspace{1mm}
+
+\item{Maillet, A., González-Bustamante, B., \& Olivares, A.
 (2016).
@@
 {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40.
-{\scshape doi:} \\ \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}
+DOI: \\ \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Olivares, A.
+\item{González-Bustamante, B., \& Olivares, A.
 (2016).
 A rotatividade de subsecretários dos ministérios no Chile (1990-2014).
-{\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil.
+{\itshape Newsletter.
+Observat\'orio de elites pol\'iticas e sociais do Brasil.
 NUSP/UFPR, 3}(5), 1--19.
-{\scshape url:} \\ \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
+URL: \\ \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B., \& Soto, D.
+\item{González-Bustamante, B., \& Soto, D.
 (2016).
 Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave.
-{\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26.
-{\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}
+{\itshape Serie Política, Gestión y Políticas Públicas}, 2, 1--26.
+DOI: \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}
 
-\item{\small González-Bustamante, B.
+\item{González-Bustamante, B.
 (2015).
@@
 {\itshape Revista de Gestión Pública, IV}(1), 143--149.
-{\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}
+DOI: \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}
 

### 2025-10-28 short/sections/summary_associate.tex
Create summary_associate.tex

--- 2025-08-08 short/sections/summary.tex
@@
 
-\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at Leiden University’s Institute of Public Administration, Faculty of Governance and Global Affairs, in the Netherlands.
+\textcolor{black}{I hold dual appointments as an Associate Professor of Public Administration at Universidad Diego Portales and as a Postdoctoral Researcher in Computational Social Science at Leiden University’s Institute of Public Administration, Faculty of Governance and Global Affairs.
 I hold a DPhil (PhD) in Politics from the University of Oxford and previously earned an MA in Political Science and a BA in Public Administration and Government from the Universidad de Chile.}
 
-%% \textcolor{black}{My work bridges the fields of comparative politics, public administration, and computational social science.
-I build large-scale text-as-data pipelines, deploy AI and machine learning models, and apply causal inference strategies to gain insights into executive politics and elite behaviour.
-This agenda centres on cabinet reshuffles, ministerial survival, civil service dynamics, and blame-shifting, while also engaging with broader debates on policy agendas, bureaucratic careers, and digital governance.}
-
-%% \textcolor{black}{My recent peer-reviewed articles have appeared in {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, among others.
-I regularly present at IPSA, ECPR, EPSA and COMPTEXT.
-I am currently working on an NWO-funded project that uses Large Language Models (LLMs) to analyse global investment prospectuses and reveal how governance arrangements shape sustainable finance flows.
-In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers and lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies.”}
-
-\textcolor{black}{My work bridges the fields of comparative politics and computational social science.
+\textcolor{black}{My work bridges the fields of comparative politics, government and computational social science.
 I build large-scale text-as-data pipelines, deploy AI and machine learning models, and apply causal inference strategies.
@@
 \textcolor{black}{I am currently working on an NWO-funded project that uses Large Language Models (LLMs) to analyse global investment prospectuses and reveal how governance arrangements shape sustainable finance flows.
-In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers and lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies.”}
-
-\textcolor{black}{In addition to research, I teach the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
+In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers, lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies,” and am a Research Leader at the Oxford Computational Political Science Group.}
 \vspace{1mm}

### 2025-10-28 short/sections/projects_associate.tex
Create projects_associate.tex

--- 2024-10-08 short/sections/projects.tex
@@
 \cvsection{Relevant Research Projects}
+
+\vspace{1mm}
+
+\begin{cvhonors}
+\cvhonor
+{Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies}
+{Enlace-Inserción Vice-Chancellor Research Office at the Universidad Diego Portales (UDP), {\bfseries PI}, about USD\$4 000. Period: 2025-2026.} 
+{UDP}
+{2025}
+\end{cvhonors}
 
@@
 
-\vspace{1mm}
+%% \vspace{1mm}
 
-\begin{cvhonors}
-\cvhonor
-{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
-{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), {\bfseries PI}, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
-{USACH}
-{2022}
-\end{cvhonors}
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
+%% {Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), {\bfseries PI}, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
+%% {USACH}
+%% {2022}
+%% \end{cvhonors}
+
+%% \vspace{1mm}
+
+%% \begin{cvhonors}
+%% \cvhonor
+%% {Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
+%% {XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), {\bfseries Research Associate} (Ximena Orchard, PI), about USD\$4 000.
+Period: 2019.} %% {\pounds} 3 000
+{%% UAH}
+%% {2019}
+%% \end{cvhonors}
 
 \vspace{1mm}
-
-\begin{cvhonors}
-\cvhonor
-{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
-{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), {\bfseries Research Associate} (Ximena Orchard, PI), about USD\$4 000.
-Period: 2019.} %% {\pounds} 3 000
-{UAH}
-{2019}
-\end{cvhonors}
-
-\vspace{1mm}
+%% \pagebreak
